% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
  \setmainfont[]{Latin Modern Roman}
  \setsansfont[]{Latin Modern Sans}
  \setmonofont[]{Latin Modern Mono}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[a5paper,margin=18mm]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={The Electric Cipher},
  pdfauthor={Francis Dove},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{The Electric Cipher}
\author{Francis Dove}
\date{}

\begin{document}
\maketitle

I moved into the house on Cappuccino at the beginning of June. I was
greeted by two people---a man and a woman---who assured me that the
landlord would not ask any questions if I decided to move into the
house, they had told him I was a ``friend'' and left it at that. I had
known Frank eight months, we had met in the hospital; we weren't
necessarily friends but our company made the experience we had together
bearable.

My room was in the back, an addition hastily slapped onto the rear of
the house to accommodate another bedroom, to create another renter.
Although I hadn't met the landlord, I had a feel for where his
priorities were; immediately I sensed I wouldn't like him very much, if
at all. But as long as I paid my rent and he left me alone, then things
would be fine. There would be no conflict. No reason to get upset. And I
couldn't afford to become upset. I had come to the peninsula to relax
from the stress of the city, where my job had taken its toll on my
nerves; my patience was shot, but at least I had attained enough in
disability grants---a post office box served as an address for the
checks---to support myself for at least six months or longer without
doing any work. When the six months were up, then I could reapply if the
problems were not resolved. I considered what I found myself in a
blessing.

That night Frank, Marian, and I sat on the living room floor; I talked,
they smoked pot. It was a housewarming, a newly kindled friendship
gathering bent on promoting the good in us. I felt warm and secure.

``So what are you going to do now that you have the time?'' Frank asked
me.

``I don't know,'' I told him. ``Maybe do a little writing. I've always
wanted to since I was a kid, and I never had the chance. And since I
seem to have nothing better to do.''

Marian laughed. She sat cross-legged on the floor, close to Frank. If I
hadn't known better, I would have thought she was Frank's girlfriend.
She was nice to look at: brown hair, brown eyes, fair skin, medium
height, thin. She almost looked native American, but I wasn't certain.
If she was sleeping with Frank, I wasn't sure why. He was overweight,
had a bad complexion, and looked as if he needed a shower just after
stepping out of one.

``Sounds like a good idea. More power to you.'' He said.

Marian passed the joint to me. I smirked and handed it to Frank. She
eyed me carefully, perhaps seductively, but I wasn't in the right frame
of mind to make a correct observation.

``You don't smoke?''

``Used to, but now it would only interfere with my medication.''

``Medication for what?'' Frank asked.

``Nothing important.'' I smiled, hoping it would answer the question. It
didn't seem to, so I added: ``Something to help me relax.''

``I see.'' Marian said.

The evening waned. I was tired and didn't feel like being around people
any longer, but I had to be polite about an exit. I didn't want to
disturb the newfound ``good feeling'' we were experiencing.

``Look guys, I'm a little tired, and I still have to rearrange my room.
Thanks.''

They shook their heads and I left them. I passed Frank's room; the door
was open a crack and I saw no furniture inside---not even a bed---only
scattered piles of clothes. I pulled the door shut and looked down the
hall. Frank and Marian were laughing between coughs. I thought to turn
back, sit with them and spend the remainder of the evening conversing;
instead, I walked into my room and shut the door behind me. My room was
a shambles. I stood gaping at the disarray before me---a definite mess.
No sense in trying to arrange anything; I practically had no furniture
either, I had left it all in the last house. All I'd managed to take was
a futon mattress and a stack of plastic milk crates that I could make a
bookshelf out of. I put a couple of books away, stacked some clothes,
unfolded the mattress, and lay down. The room was carpeted and warm; I
would have to get a fan to keep it cool, to at least make it bearable.
It was warm, so warm, almost too warm to sleep, but it was quiet, and
that was a plus. Who knew what was going to happen at this house, but so
far I felt okay with it. The diamond silver and black carpet proved to
be interesting. I let my eyes wander over the pattern, it was the solace
my brain needed to put me to sleep.

* * * * *

``So what are you going to do?'' She asks me.

``I really have no idea.''

I am sitting with her in a coffee shop by the beach; the day is overcast
and dreary, it is perfect irony.

``Are you going to live up to your promises?''

I look at her, tufts of red hair falling into her eyes. She is pretty
while being unattractive. Maybe I'd had a good relationship with her,
maybe we had been in love, maybe could have spent our lives together,
but that's all past now.

``I can't, you know, I need some time to myself.''

``You're flaking out of it, aren't you? Do you know how much that hurts
me? I don't think you do. I have tried and tried with you. I tried to
take care of you as best I could, but it's not enough for you.''

I put my fingers around my coffee cup, the heat pressed into the palms
of my hands.

``My father reserved the hall, and I shelled out nearly \$5000. You said
only two months ago you still wanted to get married, now you've changed
your mind\ldots again.''

``Things have changed, I've had a hard time.'' She never knew what I
went through, how I felt.

She leans over the table and brings her face close to mine.

``I'm going to make you hurt for what you did to me. Really hurt, so you
can feel like I do.''

``Don't listen to her, she doesn't know real pain like you do.'' A voice
whispers quietly, distantly, in my ear. I look in the direction of it
and see a tall, thin man in an olive green suit and tie. He is sitting
at the table next to us. His clean-shaven face is very long and his
complexion dark. He has a frothing latte on the table before him, it
spills over the rim of the glass. His glowing green eyes glance at her
and then fix on me. I turn back to her and smile.

``You don't need her,'' he says. ``She never loved you, she knows she
can't get anybody else.''

He gets up and puts his hand on my shoulder. His lips are close to my
ear.

``I can show you real love.''

* * * * *

I shook myself awake. The room was dark. I cocked my head, all my senses
awake, sensitive---I heard the slightest sounds, felt the faintest
movements. Frank and Marian were in the room next to me. I could hear
them having sex; someone's ass was squeaking on the hardwood floor. At
once I was sickened by the sound, it rang in my head. I placed my hands
over my ears, but it did no good. Their breathing became louder and
louder---Marian was panting and Frank was moaning. Almost as soon as the
noises began, they stopped. I calmed myself and suddenly found what was
going in the next room hilarious. I wished to laugh out loud, but I
regained control. The sounds nearly ceased, became barely audible---I
found I missed their absence. I knelt at the head of the mattress, on a
stack of pillows, and set my ear to the wall so that I might hear.

About an hour later, I managed to get myself back to sleep and woke
again late in the afternoon. The house was empty. I showered, washing
myself of the oily residue on my skin---stale sweat from the dreams I'd
had. I wasn't sure if what I'd heard in my roommates' room was real, it
could've been part of my imagination. Time to focus on reality. I shook
off the haze and popped open a sugary soda from the fridge. I had to go
to the university today to see an old friend who was lecturing there,
Steve Sanderson. He had come to see me while I was in the hospital after
my breakdown in the lab. He told me if I ever needed to talk, to come on
by. I felt it was time to take him up on his offer. I knew I should
probably go to see my therapist too, she had said if I started to have
dreams about Judy, I should make an appointment. But I felt okay,
although a little queasy. I'll survive.

Steve was in his office when I arrived. He greeted me, then offered me a
seat.

``Haven't seen you in a while, Darrin. How have you been?''

``Okay, I guess. Moved into a new place. I'm in Burlingame.''

``I heard. Nice there?''

``Yeah, I suppose. If you like suburbia.''

``Did you want to talk about something? I have a class in twenty minutes
and I need to review my lecture.''

``I just wanted to see an old friend.''

He laughed and tapped his pencil on his desk. ``Here I am, you feel
better?''

I laughed. ``I don't know, had some disturbing dreams last night, can't
make anything out of them.''

``Maybe you should see that psychiatrist, that's what they're paid
for.''

``I don't like those headshrinkers, they play one huge mind game.
Besides, she has this patronizing way of telling me things are all
right. Know what I mean?''

He sat up in his chair. ``No, I don't. You're the crazy one, remember?
Sorry to cut it short but I've got to prepare. They've been cutting
instructors again this year, listing those slated for redundancy, so I
have to outshine my colleagues. It's a good thing you got out when you
did, seems the whole place is succumbing to capitalists who think
education is a business. Well, you've got enough things going on right
now, you don't want to hear about it.''

I looked blankly at him. He sat back in his chair, gritting his teeth.

``Have they been harassing you, the government guys from the lab?''

``No, I haven't seen or heard from them.''

``Good, as long as they don't know where you live. Don't tell Doc or
that bastard Niles. She might relay the information, and he'll
snitch---he's been jostling for a promotion once they get rid of enough
of us.''

``Okay.''

``Sorry, I really have to get ready.''

``Okay. Thanks, Steve.''

He stood up to show me out, we shook hands, and I left his office. He
called to me as I was walking down the hall.

``Give me a call, maybe I can persuade the wife to make dinner.''

I waved to him with my back turned.

I wandered around campus for the better part of two hours. It was
bustling with students rushing in all directions. I was thinking someone
might remember me, but nobody did. It had been too long. I'd only taught
two classes for a few years, spending most of my time in the lab, and I
hadn't been that social, not even with the students. I walked by my old
office in the Physics building, it was still vacant. I didn't have the
mood to drop by the lab, I was certain someone would recognize me. I
did, though, stop by one of my favorite vending machines and purchased a
soda, drinking it rapidly on my way down the hallway.

The library provided some comfort. I read through some foreign
newspapers, sat in a comfortable chair, and thumbed through a Soviet-era
treatise on nonlinear mechanics. A few chapters in, I thought to check
my email but gave up on the idea immediately. My mind couldn't focus on
anything, not even the interesting material in the book. I found that as
soon as I set myself in, I was staring out the window looking at the
unkempt grass that had expansive patches of brown and small piles of
dirt that looked like large anthills. A class streamed out from one of
the buildings. It must've been an elective course, they stood in a
circle and held hands---maybe it was one of the new ``psychological
freedom'' classes the university was touting. I chuckled quietly, so as
not to draw attention to myself; I knew how easily distracted the
undergraduates were here, none of them very motivated. It was
frustrating trying to lecture to them on topics of quantum mechanics or
even the basics of linear algebra. Their attention span was analogous to
that of a dog sniffing out the nearest hedge to urinate on. Maybe that
was why I got sick of it and had to duck out for a while; I needed some
time to myself, to recover, to regain my senses and to find some sort of
norm, if there ever was such a thing. And it's not like the work had
anything to do with what happened to me, more like the inability to pass
between this world and the one which existed in my head.

I slammed the book closed. I was thinking too much again. As I left the
library, I heard a voice calling from behind me. I turned and saw that
it was Niles. Oh shit. I took a deep breath. Niles and I went back to my
earliest days at the university, back when I was doing my postdoc. He
and I both worked in the same laboratory but I knew he was stealing my
work, publishing results as if they were his own. That work caught the
attention of the university heads and they awarded him a prize for it,
of course leaving me completely out of it.

``Darrin, guy, what's happening?''

He offered his hand, I kept mine in my pocket.

``I'm tired, going home.''

``Where are you living now? The peninsula, I hear.''

I stared blankly at him. ``I'm not settled yet, not settled at all.
Actually, I'm thinking about going north or maybe to Europe to pursue my
research.''

``Great to hear you are keeping yourself busy. The work goes well then?
You're still doing it? I mean, in your private time?''

``Not really. But you know how it always persists.''

``Definitely. Hey, you want to grab coffee? I don't have a class for
another hour.''

I frowned and shook my head. ``Really, I'm sorry, but I'm very tired.
Another time, perhaps.'' I turned away from him and managed a few steps
as he continued.

``Donalsed's been asking about you, hasn't heard from you since you left
the hospital. You should let him know how you are.''

``I don't work for him, nor do I care.'' I continued walking in a
quickening pace.

``Hold on,'' he ran to me and grabbed my arm.

``He does really care about you, just like the rest of us do. Look I
heard what happened, with the experiment and the accident. I told
Donalsed it wasn't your fault, I said that I helped you calibrate the
machine.''

``And they didn't fire you?'' I looked at him with a contorted
expression.

``No.~They promoted me. That's how important the work is. Come back to
the university, come back to the lab, come work again.''

I shook his hand from my arm. ``Not ready yet. Not now.'' I stared
walking again.

``It's not so easy when people think you're a genius. They know what you
can do, they know the kind of machines you can build. They know you
understand how to bridge this world with the quantum.''

I started walking faster, almost running.

``Just think about it. I'm here for you, man.''

I didn't look back. When I got to my car, I hastily opened the door and
slumped in the seat. It was just starting to rain. I set the radio to an
oldies station and let the music echo in my head. I whispered to myself
over and over,

I'm no genius. Just a regular guy. I don't know anything...

The rain came and went, then the sun came out. Evening was approaching
and I realized I had spent at least two hours sitting in the car. The
evening fog was rolling in, the temperature dropping; it was getting
cold almost to the point of shivers, but I left the window down anyway.
I couldn't command my body to move, for it might disturb the tranquil
state I was trying to get myself in. Relax, I had to relax, the pressure
was trying to mount me, trying to take over my mind. So they want me
back, huh? Back to the lab. I don't think so. I've seen enough to know I
don't want to set foot inside the place. I had thought to destroy it,
but they had found me out too soon, before I could do any damage; they
said I was hysterical, mumbling incoherent things about some sort of
this and that. They said I had gone through AND come back, unlike others
who had met with a more violent end. No matter what, I'm NOT going back.
I pounded my fist on the steering wheel until a sharp pain stung the
bottom of my hand. Out of the corner of my eye I could see some students
walking by; they were watching me intently, the beady-eyed little
bastards. Don't look over here, nothing to see.

* * * * *

I let a month pass before I decided to call Steve. He had seemed a
little nervous about having me in his office; he wasn't sure what to do
with me or how I might react, of that I was sure. I had to reassure him
that my life was better. I told him I was settling into a new house with
good roommates, the memories of Judy were getting further behind me, and
the work at the lab a soon-to-be lost memory, more of an annoyance than
anything else. Things were going along just fine; I spent most of my
days walking around the neighborhood getting my bearings, occasionally
driving south for a friendly dinner with Marian---she had asked me since
Frank phoned saying he couldn't make it---and reading. No more physics,
no more mathematics, just Dostoyevsky and Kant. I find a lot of truth in
the latter, his thoughts are pure and clear, his language cutting a
clearing through the wilderness of man's moral turpitude. Pure reason,
something I can latch onto. Better than the sheer melodrama that was my
old life.

Steve's wife, Daria, answered the phone. She had been a friend of
Judy's. She was sorry things hadn't worked out between us. I didn't
think she knew the extent of what had happened, although Steve did. She
invited me to dinner the next Saturday, then handed the phone to Steve.
Judging from the hesitation in his voice, I got the impression that the
invitation he had extended to me while at his office was purely cordial
without any intent of it actually happening. Sort of like an extension
of his heart that didn't sit right with his logic. Emotion got the
better of him, as he would say.

``Yeah, Darrin, if you are free to stop by Saturday evening, we'll see
you about...''

He cupped his hand over the receiver and yelled to his wife.

``She says around six-thirty, is that okay?''

``Fine. Are you still in the Marina?''

``Same place.''

``Okay. See you Saturday. Bye.''

I hung up and heard someone come in the front door. I left the kitchen
and met Marian in the living room. She set down her purse on the coffee
table and plopped down on the couch I had bought only a few days before.
Since I had more money than they did, I didn't mind buying furniture.
She smiled at me.

``How was your day?''

``The usual.''

``Work was hell, my boss is such a jerk. He told me yesterday there was
a screw-up and I might be fired over it, said there were these corporate
types coming in to investigate. Turns out there was no screw-up. The
suits were only there to tour the office.''

I shook my head.

``They say he's going to quit or be transferred or something. Hope it's
soon. That was my day.''

I sat on the couch. She snapped the television on.

``I hope this doesn't sound weird, Darrin. If you don't mind me asking,
how old are you?''

``Thirty-six.''

``Frank and I had a bet. I thought you were twenty-seven, he thought you
were forty or older.''

``What a guy. Guess it's because of the white in my hair.''

She gazed keenly at it, as if noticing it for the first time.

``Ahh, that's why.''

``Why what?''

Her attention was drawn to the television. ``Why he thought you were
older than you are.''

Her eyes started to glaze over. I looked to the screen but didn't know
what program it was. She sat up on the edge of the couch and leaned
toward me.

``Do you feel like having a bowl?''

``What? Oh, no, no I don't.''

``You don't mind if I do, do you?''

``No, go ahead.'' She pulled a small box from her purse which contained
a glass pipe. It was turquoise and its edged were smoothly rounded.
Thin, white stripes ran through it making it look glossier than it was.
She reached under the couch and pulled out a bag which contained her
marijuana. Using her long nails, she pinched a chunk of bud and stuffed
it into the pipe. She watched me, as I watched her, lighting the pipe.

``I really love this stuff,'' she said while holding her breath. I don't
know what I'd do without it.''

She exhaled slowly, the musk of smoke tickled my nostrils. Her attention
was back at the television.

``What are we watching?'' She snorted. I turned my eyes to the screen.
``I mean what is that guy doing?'' She lit the pipe again, then ashed it
in a small cup on the coffee table. ``You know\ldots{}'' she said, ``I
can see you are a nice guy.''

The smoke seemed to have an effect on me. I was drifting away. ``Okay.''
I said not taking my eyes off the screen. She packed another bowl.

``Did you hear me?''

I snapped out of it. ``Um, sure, nice,'' drifting back again.

She laughed. Time passed.

``I'm tired of watching TV. I'm going to take a bath.''

``Okay.''

She got up and I heard her slide into the tub some time later. The
program ended and I casually flipped through the channels. I hated TV,
it not only had a way of draining what was left of my brain, but also
suppressing any new thoughts to refill it. I snapped it off and went
into my room, leaving the door open. The new furniture in the room
consisted of a frame for the futon, a real bookshelf, a desk, and a
small wooden filing cabinet. I had few papers to put into the files;
most of the writing I had done prior to my breakdown had
disappeared---Judy had probably thrown it away. I sat at the desk and
gazed at a pad of paper that had a few lines scribbled on it, much of
nothing it was. I wanted to buy a typewriter, an old one, and maybe get
back to the book I was working on before, but a non-fiction book on
quantum physics in the realms of mysticism seemed too trite for me now.
And owning a typewriter would be too intimidating, it would force me to
work---the damned machine staring up at me, keys winking, stark white
blank paper glaring. Better than writing on a computer, though.

``Darrin, could you come here for a minute?''

I get up from my chair. I think to shut the computer down, but I figure
Judy won't need to talk to me too long. She likes it when I walk in on
her while she's bathing or dressing; she says she likes having my eyes
on her, staring at her vulnerability---her breasts floating in the bath,
nipples firm.

``Do you find me attractive?''

``Yes.''

``Do you think I'm sexy here in the tub?''

``Yes.''

``What are you thinking about?''

``Making love to you\ldots my hands around your throat.''

``Darrin...''

I rubbed my eyes. The pen was in my hand; I had drawn a series of skewed
circles on the pad.

``Darrin!''

``Yeah.''

``Could you come here for a minute?''

It was Marian's voice. I shook my head. I had been lost again. That
smoke did a number on me.

``Be right there.''

When I got to the bathroom, she was standing before the mirror, wrapped
in a towel.

``Are you doing anything Saturday night?''

``I'm having dinner at a friend's.''

She combed her hair, peering through the steam on the mirror.

``Anybody I know?''

``No, you wouldn't.''

``Oh, that's too bad. I was hoping we could have another nice dinner
together, like we did on Wednesday. Frank's not going to be around.''

I pulled at my lip. ``Are you guys going out or something? I'm not sure
of the situation between you two. When Frank first mentioned the living
arrangement, he said there was another roommate, but he didn't say it
was a girlfriend. So I don't know.''

She looked at me. ``How did you meet Frank?''

``I met him a couple of months ago, through a friend. Um...''

I stared into the mirror. I couldn't, for the life of me, remember who
the friend was; in fact, I didn't remember meeting Frank at all. The
memory of my life then seemed to be surrounded by an impassable thick
cloud.

``What's wrong?''

``I don't know where or how I met Frank.''

She seemed surprised and changed the subject; she went on about work
again. I massaged my forehead, trying to think. Nothing.

``When did \emph{you} meet Frank?'' I asked her.

``We used to go out, a long time ago.'' She abruptly walked past me into
her room.

``But we don't get along too well, that's why I have a separate room. In
some ways we need each other, but we agreed to go out with others,
although he's not too fond of me doing it.''

I turned and looked into her room. She had left the door open, and by a
mirror on the wall, I could see her dressing. The blank, it was still
there. It was as if the knowledge of Frank had been implanted, because I
couldn't remember the actual experience of having met the man. I felt
very strange and found I was starting to worry.

``That's the way it is,'' she came out of her room patting her head with
the towel. ``If you can't make it Saturday, maybe we can do it another
time.''

``Yeah, maybe\ldots maybe in a few days or so.'' I was starting to get a
headache.

``Don't worry about it.'' She walked to me and kissed me on the cheek. I
touched the spot, it was warm and moist from her saliva.

After lying in bed for nearly three hours, I managed to sleep fairly
well, only one dream I could remember. It was of the man who first
appeared in the coffee shop. He and I were in the lab, on the bottom
level. The walls were made of cinder blocks, they were painted, splashed
with black. The paint had run; it had dried in pools at the bottom of
the wall.

``Come on,'' he said to me. ``I have something to show you.''

I followed him, down a stairway that wound around a corner. The light
was feeble; I could barely see, but I felt as if I knew where I was
going.

``This is something that will shock the hell out of the world.'' He
smiled. ``And fuck 'em if they don't like it. We'll shove it down their
goddamned throats!''

We came into a room that was expansive. There was a single light in the
center the room, illuminating a table. On the table lay a staff mounted
into the top of a stone pyramid. A metal ring, shaped like a zero, was
attached to the top of the staff. There were large generators behind the
table, and an oblong circle was drawn on the floor. I knew what it all
meant. I backed away.

``Take it easy, just one more experiment and we'll be successful.''

``No, no, I\ldots I\ldots I can't.''

His green eyes glowed vibrantly, he stretched his arms out toward me.

``You must...''

I shook myself from my sleep, to find daylight streaming in through my
window. I sat up and the light of the sun caught my eyes. Alive! Alive
again!

I went to the kitchen and put my hand on the phone. I thought of calling
Doc; she had said if the dreams started again, I should call her. I
could handle it. I survived. The dreams, they're vivid phantoms
screaming through my brain, revealing the atrocities of a life gone
un-recollected. I needed help, but not hers; she couldn't understand
what I'd seen, how it had and will affect me and how it will all come to
a climax where no one shall remain.

* * * * *

I arrived at Steve's house a few minutes after six. His wife was all
smiles as she opened the door.

``Hi, Darrin. Come in.''

Their flat looked just as I had last seen it, over a year ago. Nothing
had changed: same furniture, same pictures, same family. Steve and Daria
had been married almost nine years. I felt sorry for them having to live
in the same place all that time, without any hope of ever leaving, but
they were so comfortable in the familiar, with no taste for the
extraordinary. Steve greeted me in the living room.

``Darrin, come with me.'' He grabbed me by my arm and led me into the
hall. ``I invited another guest for dinner, he says he knows you. I
don't think you know him, but he works at the lab.''

I yanked my arm away. ``What?!''

``Take it easy, he's only been there a year. He started right after you
left, so he doesn't know what happened. Besides, he's a friend of mine,
so be nice to him.''

I let out a long, quivering breath. ``Okay, okay.''

``He's really anxious to meet you. I talked to him after I saw you on
campus. I thought since you were going to be here, you wouldn't mind
meeting him.''

``Yeah, I'll deal with it.''

``Splendid.''

He led me into the kitchen. He looked at his wife, who was putting the
finishing touches on dinner.

``Where's Sam?''

``In the bathroom.''

``Have a seat in the living room. Can I offer you anything? Soda?''

``No, thanks.''

I went and sat on the couch. There was a loose string of fabric on the
arm; I tugged at it. There were sudden voices in the kitchen, one I
thought I faintly recognized, neither Steve nor Daria, still familiar,
from somewhere distant, like a voice carried on the wind. Then he came
in.

He was tall, thin, his skin dark and his hair jet black. His eyes were a
deep hazel, almost glowing; his pants were olive, his shirt black,
buttoned to the top. I knew him in an instant. He was the man in the
coffee shop dream and in the lab dream. I stared, frozen, with my eyes
wide and my mouth open. He smirked and gave me a perplexed look.

``Darrin?''

His voice was exactly the same, down to the intonations, pitch, accent,
and pronunciation. I couldn't conjure a word or gesture to acknowledge
him. He walked over and stood next to me.

``I'm Uncler, Sam Uncler.''

He extended his hand, and after a minute or so, I followed. My palms
were wet. After we released, he looked at his hand, then at me.

``A little nervous, are we?''

He sat next to me.

``I've heard a lot about you back at the lab, you're quite a celebrity,
famous I might put it, been following your work. Now I have the ultimate
pleasure of meeting you, the genius behind it all.''

I flashed a facetious grin at him. He pulled out a cigarette and put it
into his mouth.

``Smoke?''

``I quit.''

``Oh,'' he searched his pants and shirt pocket. ``I hate it when that
happens, I lost my lighter. Excuse me.''

He quickly got up and went into the kitchen. He walked over to the
stove---I watched his every move as if anticipating the dreams to
recur---he looked back at me and smiled. He flicked on the gas burner
and bent over it, extending the cigarette over the flame. He looked at
me again. I was still staring. He lifted the corner of his mouth as if
to silently say something.

``Sam!'' Daria yelled.

``Sam, if you needed a light, I have one.'' Steve said.

``I got it. You have an ashtray? I don't want ruin your couch. And I
have your guest to talk to.''

He returned and sat next to me again---this time closer. He had a faint
scent of cologne on him.

``Sanderson's a great guy, all manners and British etiquette, Daria too.
But you can't know two better people. Don't you think so?''

I resumed tugging the loose string on the arm.

``She's making her specialty, Veal Parmesan, my favorite. Nothing like
eating sick young cows. Makes you feel really alive, eating the
misfortunes of those lesser than you. Superior, that's the word I'm
looking for, makes me feel superior.''

``Yeah.''

He was suddenly quiet. I could hear him taking long draws on the
cigarette.

``You don't say much, do you?'' He said without looking at me.

I turned and gave him a surprised look. ``What?''

``Silence, the absence of speech. You seem to have cornered the market
on it.''

Daria dropped something in the kitchen. I looked up to see Steve running
to her. Uncler was smiling, almost sadistically.

``She might need some help...'' I started to get up. He put his hand on
my leg.

``She's a big girl, she can handle it. Besides, that's what the
husband's for. Don't worry about it.''

I sat back down slowly, eyed his hand on me; he retracted it.

``You feeling a little edgy?''

``Not really.'' I looked at the string, but left it alone.

``Seems like it, it's what your profile says.''

I glared hard at him.

``I've read it several times, you know, had to. Donalsed, Niles,
Sanderson-\/-they all say you're dangerous, could go off at any second,
like a powder keg, boom!'' He made the motion with his hands. ``But they
insist despite that you're an absolute genius. To me you just seem a
little edgy, but that's all---uncomfortable around strangers,
anti-social and all that. I can understand. Ah, don't worry about it,
I'm the same, it's the damn work at the lab. Can drive you up the wall,
if you know what I mean, but I think you already do. That's what the
profile says, but my curiosity got the best of me, I had to see for
myself. But you don't strike me as the murderous type, not at all, you
seem perfectly passive sitting in your little corner of the couch
pulling on that damn thread. Perfectly passive.''

I looked blankly at him.

``Yes, your defense mechanism. Pretend you know nothing, good idea, it
works for me, especially as far as the government's concerned, but I'm
not here to talk politics.''

``What are you here to talk about?''

``I think you know.''

Another blank expression. He shook his head.

``You're the man behind the Cipher Experiment, the brain of the
operation---I've spent the last year intently studying your work. I
wanted to meet you sooner, but they wouldn't allow me to see you at the
hospital.''

Another blank expression.

``This is how we're going to play it, huh? Fine, don't say anything if
you don't want to. Hell, you probably don't remember any of it, anyway.
The profile says you're a vegetable up here,'' he tapped the side of his
head with his finger, ``and maybe they're right, who knows? Only you
do.''

He pulled at his lip; the cigarette burned between his fingers, smoke
gently curled away. He took a long drag and snuffed it out in the
ashtray on the end table. His gaze fixed with mine.

I get the distinct impression that you think you know me, but can't
place the face.''

``Maybe.''

``No bullshit. This is the first time I met you. Well, in person anyway,
your reputation precedes you, you ought to be proud.''

``Really.'' I looked at the string again. The temptation was too great;
I started tugging at it---he noticed.

``Look,'' he moved closer, put his hand on my leg again; he brought his
face close to the side of my head. I felt his breath on my neck. ``I
know what happened at the lab.''

I snapped my head around and faced him. ``You don't know anything.'' I
relaxed and turned back to the string. ``Don't know anything at all.''

``Is that what you think? If so, you have grossly underestimated me.''
He eyed my progress at nearly pulling the entire thread out. ``But I do
know one thing for certain, if you tear Sanderson's couch apart, he'll
be upset about it.''

I cracked a smile. Steve walked into the living room.

``Dinner's ready.''

Uncler and I exchanged glances, simultaneously got up, and walked toward
the kitchen. He stopped me.

``Let's try to be friends and we'll go from there, okay?''

I nodded, and sat at the table; a plate had already been prepared for
me. The veal was breaded, a thin tomato sauce covering it, a piece of
cheese swimming in all of it---maybe floating. A bowl of noodles was
beside the plate; they were cooked, but had no sauce. I wasn't sure if I
was supposed to pour the noodles over the plate, or scoop pieces of veal
and soup into the bowl. I decided to wait and see what everybody else
did. Uncler looked at me and smiled; he unfolded the napkin and placed
it in his lap. I did the same, he nodded.

``Sanderson.'' He stood up with a glass of red wine. ``A toast, to
Darrin. May this be the first day to lead to the rest of his life.''

``Here, here.'' Steve and Daria raised their glasses. I had no wine,
only water. I gripped my hand around the plastic cup and lifted it.

``Great.'' Uncler drank deeply from his glass, then sat back down. No
more words or glances were exchanged, and the rest of the meal was taken
in silence.

I arrived home close to eleven; Marian was up watching television. Frank
was nowhere to be found.

``How was your dinner?''

``It was okay. Nice to see friends.''

``I wish I could get out once in a while. Frank never takes me
anywhere.''

``You should ask him to.''

She laughed. ``Yeah, right.''

``By the way, where is he?''

``I don't know, he wasn't here when I came home, probably out with his
white-trash friends. Out drinking beer, belching, farting, you know, all
that male bonding nonsense.''

I laughed and started to walk to my room. I thought of asking her about
Samuel Uncler, but there was no way she could possibly know him. A
nagging feeling told me to ask anyway, but I ignored it.

I got to my door and she yelled down the hall.

``What are you going to do?''

``Settle down and read, I think. Not much else to do. Too early to
sleep.''

There was silence, and I went to my room. The futon was comfortable. The
room was warm from the heat of the day; I threw the window open and lay
down. I had books, a lot of books, most of them unread. They had looked
good in the bookstore; I'd bought them because they seemed interesting.
Maybe someday I would like to read a particular author, and when I did,
I didn't want to have to go through the agony of not having their work
on hand.

I must've dozed off, a knock on my door startled me.

``It's Marian, you awake?''

I looked at the clock. It was well after one.

``Yeah, I'm awake. Come in.''

She threw the door open and knelt on the bed. ``I thought I heard
something downstairs.''

I rubbed my eyes and yawned. ``We don't have a downstairs.''

``Yes, we do. There's a cellar under this room.''

``A cellar?''

``Come on.'' She pulled me off the bed and onto my feet. I followed her
through the kitchen to the patio door in the back. She opened the door a
crack.

``Listen, do you hear that?''

I looked around the yard, to the wooden fence that enclosed the grounds.
There wasn't a sound.

``I don't hear...''

``Shhh...''

There was an indistinguishable sound of something crying. It was coming
from under the wooden stairs below the patio door. Faint scratching
echoed. She grabbed my arm.

``What is it?'' She whimpered.

``It's probably a cat or something. There's a cellar under there?''

``Yeah, lift the stairs.''

I went to a drawer and got a flashlight. Marian shrunk back and sat in a
chair; her voice was quivering from fear.

``Oh, shit...''

There was more crying and scratching, now more fiercely. It sounded like
someone or something was trapped in the cellar. I rifled through another
drawer and pulled out a steak knife. I didn't know what good it would
do, but it gave me a small amount of security.

It was dark outside---no light from the front of the house would
illuminate the back---I flicked the switch for the kitchen light, but it
was burned out.

``Go to my room and turn on the light.''

It did little good, it only cast shadows, since the cellar was around
the corner from my room. Although I stepped as lightly as I could on the
stairs, they creaked from my weight. The crying ceased. I stood before
the stairs and placed my fingers under the edge of them; I looked at
Marian.

``Straight up,'' she whispered and gestured with her hands. I quickly
pulled and the whole unit lifted up, hitting the wall hard and coming to
a rest. The crying began again; it came in soft long cries and short
sobs. My hands were shaking, making the light bob before me. I clutched
the knife tightly.

Setting a foot on the first concrete stair, I started my descent. I had
to duck, and I noticed the stairs curved around to the left.

``Great.'' I couldn't see the cellar without first rounding the narrow
corner. I crept slowly, moving with the pitch of the cries---my
instincts had taken over. I reached the corner and, shining the
flashlight around it, peered into the depths of the cellar. The walls
were painted black; the floor was moist, small patches of fungi growing
out of the cracks. The walls were constructed of cinder blocks. I shined
the light around and noticed it was silent. The room was small, not more
than eight meters square. I couldn't see anything, so I continued down
the remaining three stairs. I was standing on the floor, my footing
unsure; I found I was standing in a patch of fungi, the moisture soaking
my socks. There was a water heater in one corner, a series of pipes
overhead, and junk in another corner. A small, overturned wooden box lay
behind the water heater, a piece of plywood leaning against it.

The light went out.

``Great.''

I shook the flashlight as hard as I could, but it didn't respond. I
looked behind me. I was in pitch-blackness.

``Need a light?''

I freeze. It's a familiar voice---too familiar.

A feeble light glows, increasing until I can see. Uncler is standing in
the center of the room, holding a staff with an oblong-shaped piece of
metal mounted to the top of it. His olive drab suit is electric; his
hazel eyes shine emerald green. He has a wide grin on his face.

``Tired of the world bothering you, Darrin? Tired of them crying to you
when they have problems? Tired of being blamed for everything? Even
tired of getting all the credit?''

He extends his arm out and points to the wall. He turns the staff,
illuminating the black blocks. Judy is chained to them. The handcuffs
and length of chain holding her drip rust. She is struggling to get
away; she is gagged, whimpering long, soft cries and short sobs.

``We did it once a short year ago, nothing's stopping us from doing it
again.''

He grips the staff tighter, and the light from the cipher glows to a
blinding glare; a soft hum emanates. In the corner where I had seen the
water heater, there is a generator; it is rocking violently, pumping out
juice.

``So many places to see, so many people to meet.'' He looks at me and
extends his hand. ``Come with me.''

I shake my head, my mouth open, drool trickling down the front of my
shirt. He focuses on Judy; she is hysterically flailing herself,
desperately trying to get loose from the bonds that hold her to the
wall. Uncler leans the staff towards her; a flash of current comes out
of the generator, and a rod of light shoots through the cipher. It
penetrates Judy, she screams. The sound echoes in my brain.

``Darrin! Darrin!!''

I felt someone shaking me in the darkness of my mind. My back was moist,
my skin saturated. I was too fear-stricken to open my eyes.

``Darrin, can you hear me?!''

The shaking: my head fell back and forth, striking the concrete. Slowly,
slowly, fear dissipated and I wedged my eyes open. I saw Marian staring
down at me.

``What the hell happened? First thing I know is you go around the
corner, then the light goes out, I hear you scuffle with something, then
nothing.''

She lifted me up and sat me on the bottom stair. She turned my face
toward hers; dried foam was glued to my chin, and drool covered the
front of my shirt.

``Oh my God, I didn't know you were epileptic.''

I was regaining my senses, able to sit myself up. She took off her shirt
and patted my face with it; she wiped away the grime, trying to clean me
up.

``Jesus, I had no idea.''

The cry. I heard it again, like a far off echo of Judy screaming---I
could see her body contorting, head twisting into odd shapes, face
deformed, red hair falling out in large clumps. The cry---I heard
it---is seared into my sickened soul.

``What the...''

Marian looked behind her, gripped the flashlight, and shined the beam
into the corner. From behind the water heater, a cat slunk out. It cried
sharply, then mewed softly. It's coat was fire-orange.

``Oh,'' she set the light down and picked up the cat. It purred in her
arms and looked intently at me. It meowed.

``You must be hungry, huh?''

Her attention was focused on the cat. All of a sudden, she realized I
was still incapacitated on the stairs.

``I'm so sorry, are you okay?'' She knelt and looked into my eyes,
searching for something.

``I'll be all right. I told you it was a cat.''

I had her shirt in my hand. She had only her bra on, the cat tucked next
to her small breasts.

``I'll be fine.''

I showered. It was a long one, must have been an hour. The hot water
relaxed my frazzled nerves. I put on my robe, went to the living room,
and sat down; my head ached. Marian went to feed the cat in the kitchen.
She opened a can of tuna; the animal purred loudly between bites.

``Marian.'' I had to call her twice.

``What?''

``Do you have any cigarettes?''

``They're on the table. I thought you didn't smoke.''

``I don't. But I \emph{need} one.''

I inhaled as deeply as I could. The first time I coughed violently; the
second, less so; the third, even less; finally I got the knack of it and
my body stopped reacting. I shut the light off and sat in the dark,
watching the ember from the cigarette glow brightly. It relaxed me. I
heard Marian coming down the hall. She opened the door, closed it, and
sat down next to me; she had put on a bluish, flowered sweater. She lit
a cigarette and we smoked together; I felt at peace and wondered why I
had quit in the first place.

``You okay?''

``That's the third time you asked me. Yes, I'm okay.''

``Just checking. You scared the hell out of me. I had no idea.''

``I don't like to advertise it.''

``Does it happen often? Do you have any medication for it?''

``No.~And I haven't been taking it lately---I find it depresses me too
much, and I already feel too tired.''

``I won't tell Frank. It'll be our little secret.''

I chuckled. ``Thanks.''

``Besides, he doesn't deserve to know. He'd think you were a retard or
something.''

I looked out the window. A car slowed before the house; Marian stared at
it until it took off.

``Probably one of his friends looking to party. Glad you turned out the
light.''

The cigarette tasted good.

She quickly exhaled smoke. ``He's so chicken-shit, he never would have
gone down there.'' She affected a playful tone. ``You're so brave.''

I extinguished the cigarette and leaned back---she followed. She ran her
fingers through my hair---I responded.

``That feels nice.''

She rubbed the back of my neck, leaned over and kissed my ear. ``So
brave.''

I kissed her on the lips, they were soft and warm. She pulled back and
looked at me, trying to figure out why I had done it. She shook her
head, then kissed me, her tongue probing my mouth.

``I have an idea,'' she said between kisses. ``How about a back rub? I
think you could use it.''

``Sounds wonderful.''

I led her to my room. I lay on the futon; she straddled me and worked at
my back. There were many knots, a lot of tension; if she only knew.

I woke late the next morning with a splitting headache and despair in my
heart. I felt as if I'd had dreams during the night---so many, in fact,
they had left my body weak; my hand quivered as I went to pull up the
window shade. It occurred to me that Marian had gone. In my groggy state
I hadn't realized she'd left. I sat against the wall, then I noticed I
was naked---I never slept without clothes. I found myself in a state of
panic, remembering nothing save the back rub. Had I actually screwed my
roommate? This was not a good way to develop platonic relations. Why
couldn't I remember? I tugged at my lip and looked around the room for a
sign as to what might have happened; everything appeared normal,
although a little scattered, as if somebody had torn around.

The clock next to the bed read eleven-thirty. I found two cigarettes and
a small note tied together with a string. I read the note.

``Relief for my rehabilitating roommate.''

I smoked them back to back; if I'd had a whole pack I would've kept
smoking until I had finished it. Doc had warned me that as soon as the
dreams started, I would be experiencing blackouts again; she had said
because of the mild epilepsy and the trauma I had endured at the lab, it
would only encourage repeats in the future. I reached for the phone to
call her. I had to dial three times before I would let the line connect,
and even then I had to force myself to ask for her.

``Darrin, I haven't heard from you. I've been concerned.''

``Seems like a lot of people have.''

``What?''

``Nothing.''

``Steve called and told me he saw you. You had dinner at his house?''

``Yeah, just last night. Word travels fast.''

``He's worried about you. He phoned this morning and said I should have
you come in to see me,'' she laughed. ``I don't mean it like that. I
like it when you keep in touch with me.''

Immediately, I noticed she had that patronizing tone again.

``I don't have your new number, so I can't check up on you.''

``See, I've been busy. I don't have a lot of time.''

``Would you like to come by and talk about it?''

I thought of saying yes, but something held me back. I let the silence
drone on.

``Darrin?''

``Yeah, I'm sorry. Yes, let's make an appointment.''

``I'm free this afternoon, would that be okay?''

``Yes, that'll be fine.''

``At three o'clock?''

``Three. Yes.''

``Let me have your number in case I get held up.''

``I'll see you at three. Good-bye.''

I hung up on her. Something was going on and I knew I was not being
paranoid---a definite plan was in the works. I wandered around the
house, got dressed, had a glass of milk, and sat at the table. I noticed
the stairs to the cellar were still up. I paced to the patio door,
opened it a crack, and gave the stairs a good shove---they crashed onto
the concrete with a resounding thud.

There were two messages on the machine, both were for Marian. I saved
them.

I sat on the couch and turned on the television; nothing much was on.
Over the low volume, I could hear the cat we'd found in the cellar
gently scratching the inside of Marian's door; it mewed softly. I
thought of letting it out and allowing it to run free through the house.
I ignored it and returned to the television.

At three I was at Doc's office. I had to wait for her in a pallid room
adorned with framed lithographs of Austrian landscapes. The secretary
gave me a peculiar glance; I thought to mimic her, but didn't. I wished
to smoke, but had no cigarettes.

Doc walked in at three-thirty. She offered me the couch; I opted for the
chair---it seemed more ironic. She sat behind her desk, opening my file.

``How are you doing, Darrin?''

``Okay.''

``How are you really doing?''

``I had a blackout yesterday.''

``Have you been taking your medication?''

``No.~I find it depresses me.''

``Taking it will do more good than harm. Be sure that you take it.''

``Yeah.'' I stared off into the room.

``Something you need to tell me?''

I rubbed my forehead, a headache was coming on.

``The dreams\ldots they've started again.''

She leaned back in her office chair. ``I knew they let you go too soon.
I told them you hadn't fully recovered.'' She was angry. ``Darrin,'' she
got up and held my hand. ``Would you like to go back to the hospital?''
I looked into her eyes and realized her expression was patronizing, as
if she only cared about my well-being because she was being paid to see
to it. Like a demon that had been awakened, rage built within me. I
mimicked her patronizing gaze and tone.

``You mean the asylum, don't you?''

She let go of my hand. ``Darrin, it's not an asylum.''

``Don't tell me what it's not. They won't let you out. That means it's a
place you stick people who are behaviorally intolerable.''

``I'd like to see you get some help. You seem to still have a lot of
anger. Maybe you would be more comfortable with someone other than
myself.'' She got up and lifted the phone. ``I can give you a referral
to...''

``The hospital? Where they'll give me a lobotomy? I don't think so. Put
the fucking phone down.''

She was surprised and shocked, but didn't heed my warning. ``Would you
get me the number for...''

I grabbed the receiver out of her hand and yanked the phone across her
desk; it slammed on the floor.

``I told you to put it down, but you didn't listen to me! Why?''

``Darrin, take it easy.'' Her voice was quivering from fear.

``Quit patronizing me, dammit! I'm fucking tired of it!'' I was
screaming. I quickly composed myself.

``You know Doc, sometimes when I look at you, you remind me of Judy.'' I
touched the side of her face; she reeled back. ``I loved her, I honestly
did, but she made me so angry. I was forced into it.''

She pinned her back to the wall. She was cornered, her expression that
of an animal caught in a snare; she was petrified. I smiled, tapping my
fingers on the desk.

``Well, I think I'd better be going, got lots of things to do.''

``Darrin, let me help you. Else, I will have to call the police.''

I slammed my fist on the desk.

``Will you shut up, for once!''

There was silence, beautiful silence, even in the outer office. I knew
they had heard me yelling; soon security would be all over this place
and they would force me back into the asylum.

``I'm outta here. Thanks for the clever conversation and the advice,
Doc.''

I made a quiet exit; she stayed in her spot on the wall. The
receptionist was deathly still. I returned her frightened stare with a
Cheshire smile. I was certain the authorities would be coming for me
soon.

The drive home, instead of lasting half an hour, turned into four hours.
The landscape, passing by at freeway speed, was a comfortable blur: the
houses and businesses, the putrid bay, the smog-choked airport, the
square yuppies with their loosened ties and blank expressions, trying to
pretend they had an intense problem getting home because the road was
over-capacitated with commuters. It was their fault, the assholes, they
had chosen their occupations, subsequently applied for jobs, and gotten
them; they had known what they were getting into, but still insisted
they had the right to honk and swerve from lane to lane, each trying to
move the fastest in a beast of their own creation. If I hit any of them,
I didn't give a shit. If the car still ran after an accident, I would
keep on driving, even if I had badly injured someone. All that was
waiting for me was the hospital-\/-no matter what I did. Even if I sat
home all the time and did absolutely nothing, the hospital would still
be waiting. The CD player was on the fritz, the radio was filled with
banal commercials; if I were more paranoid I'd say there was a
conspiracy. I wished I had my own music player. Why is it that when one
station has a commercial, so do all the others? Coincidence? Ah, I don't
know. Maybe I'll go buy one. No sense getting twisted in the problems of
the world; ordinary, ``normal'' people---I hated them. And if they glare
at me because I'm not driving like they are, because I'm not riding
someone's bumper when they cut in front of me, I'll give them the bird.

The house was dark when I arrived home. I had no idea where Marian and
Frank were. I opened all the windows in the house---it was uncanny how
it held the heat in---my room was the worst of all, the tiny window
doing little for air circulation. I opened the door and turned on the
fan in hopes the cat was in Marian's room and wouldn't wander into mine.
I had bought a large pad of paper, some pens, and a ribbon for the
typewriter somewhere in along the drive---where I had realized (perhaps
discovered) I'd driven too far. The mall had been cool, and the people
wrapped up in looking for something to buy, or deciding what they and
their young friends wanted to do. I sat down, flipped open the pad to
the first sheet of paper, placed the pens within reach, and waited for
darkness to settle in.

I liked the night. It is far better than the day. The temperature is
bearable and when it gets into the morning hours, I come alive. That
way, ``normal'' people are asleep and they can't contaminate my
thoughts. The clear sky is a wondrous sight, and when the morning sun
appears over the horizon, it is the most beautiful thing imaginable. The
feeling of staying up all night is indescribable, especially so after
intensive work. I liked writing and drawing, toiling over a creative
design, honing something out of nothing; I know it takes a special sort
of person to do it, and I hoped I had what it takes to achieve a
semblance of greatness-\/-but I really didn't much care if I had ``it''
or not, I had to create in order for my mind to stop nagging me.

I didn't pay attention to what was going on in the house. I had the
radio on and couldn't hear if anybody came in or not. I was far too
involved in what I was doing to be bothered with concerns about
nobodies. I was drawing some interesting pictures. Someone---I don't
remember his name---had tried to teach me in the hospital; through the
lessons I had tried to listen, tried to duplicate his art, but the damn
thing never worked out. I looked at what I had done, flipped a page on
the tablet, and drew again. After trying to draw the same picture three
times and failing all three, I drew another. I lay my head against the
paper; I couldn't get the image in my head onto the tablet, the transfer
from mind to hand wasn't working. Uncler was in my thoughts; I was
thinking about him and realized I had been doing so most of the day. I
found it odd that he had made such an impression on me, usually I didn't
think about anyone so...

The phone was ringing, distant and quiet.

I answered it. The line was silent.

``Hello\ldots hello?''

The slow inhale and exhale of someone smoking a cigarette. A strong
image was chiseled into my brain.

``Uncler?''

``How are you, Darrin?''

``How'd you get this number?''

``Don't worry about it.''

``I see.''

I brought the phone into my room and locked the door. I set the pen to
paper. I started drawing a square room with a high ceiling and a round
table in the center.

``Heard you made a mess of things at Doc's.''

``How do you know?''

``Sanderson.''

``Figures. He'll probably tell everybody.''

``Always has.''

``Do you think Donalsed knows?''

``That's why I'm phoning. Doc had somebody follow you. She's reported
you to the authorities. You're dangerous and they will probably take you
back to the asylum. I don't know when they will pounce on you.''

I almost dropped the phone. ``What am I going to do?''

``I'd say get out of there. And fast.''

I was sweating, nervous. I didn't want to go back to the hospital, or
the lab, no matter what the cost. \emph{Why did he call it an asylum?}

``Where to?''

``Come to my place. They won't think to look here.''

``What? So you can turn me in?''

``Turn you in? That's not my style. But I don't care about all that, I
just want to make sure you're safe. Besides, if Donalsed gets a hold of
you, there's no telling what he'll make you do.''

``Yeah, but . . .''

``Now, get out of there and drive to the city. California Street and
Sixth Avenue. Number 137 Sixth Avenue. Got it?''

``Yeah.''

``Leave now and don't bother packing, you don't have the time.''

``Okay.''

I slammed the phone down and shoved my keys into my pocket. It was then
I noticed I had a smear of black ink on my hand; I wiped it off as well
I could and found I had snapped the pen in half---the ink had spattered
in several large blotches, covering the paper. I heard the far-off
wailing of sirens and figured they were coming for me. On my way out, I
accidentally kicked the cat---stupid animal---got behind the wheel of
the car and drove away as fast I could. Approaching, two police cars and
an ambulance sped past me as I headed for the freeway.

``You're one step ahead of them,'' Uncler said to me as I pulled up. It
was well past midnight when I arrived. He was standing in the doorway of
his building. He opened the garage and directed me to put my car in it.

His apartment was large; it was a flat on the fourth floor, done
entirely in art deco, with heavy black curtains covering the windows. My
attention focused on a blue neon clock, which was mounted on the wall.

``Like anything to drink?''

He was in a casual shirt and khaki pants. His hair was slicked back.

``Um, I think I'll have...''

``I'll get you a shot of whiskey, it'll calm you.''

He left the room for several minutes. I sat on the couch with my hands
clasped and sweaty, trying to think of what I was going to do, where I
was going to go. Maybe I could hide out at my parents' house up north;
it was near the Oregon/Washington border. Donalsed wouldn't think I'd go
that far, then again, he'd probably figure it would be the first place
I'd flee to. I sat back and tried to relax. I was over-analyzing; my
brain was overtaxed with anxiety and there was no way I could have a
single clear thought. Best to have somebody else do the thinking for me.

Uncler came back with two crystal shot glasses and a bottle. He poured
into both glasses and handed me the more generous of the two. He smiled
slyly and swallowed all of his shot in one swift motion. I sipped at
mine---it had been a long time since I'd had anything stronger than soda
to drink.

``All at once and don't suffer over it.'' He lit a cigarette.

I dumped the whiskey into the back of my throat, it burned as it went
down. I coughed, almost heaving it back up. He patted me on the back.

``Pretty good. When was the last time you drank?''

``Can't\ldots remember\ldots when.'' I hacked dryly.

``I understand. Let me pour you another.''

``No, no,'' I waved him off. He put the glass in my hand.

``The second goes down better than the first, believe me.''

I took the whole shot. It didn't taste as bad as the first, but still
bad. He sat next to me.

``That'll help you relax. Look, it's late, why don't you take the bed
and I'll stay on the couch.'' He put his hand on my leg. ``Unless you'd
feel more comfortable out here.''

``I don't think I can sleep, I'm too wound up in what's going on.'' I
attempted to stand and fell back to the couch. I rubbed my eyes. I felt
groggy. I looked at Uncler; his face was like a watercolor, blurring at
the edges. I couldn't focus the skewed lines. He spoke. His voice was a
distant echo.

``Sleep, Darrin. We'll talk in the morning.''

I saw a black pool open at my feet. I dove in headfirst.

* * * * *

I woke. I didn't know what time it was. The apartment was dim, the
curtains were drawn; I lay on the couch, with a blanket covering me. I
was still fully dressed, my shoes on the floor.

``Oh, crap,'' I sat up and tried to shake the remnants of sleep from my
head.

``What was in that drink?'' I tried to stand, sat back down---my legs
refused to support my weight. The neon clock glowed blazing blue on the
wall across from me. I watched the second hand sweep around the red
numerals; I could see the minute hand slowly moving. I concentrated on
it as hard as I could, trying to find some sort of continuity. It was
working; my mind was clearing as each minute passed. Soon I could stand.
The next task was walking. There was a haze in the air, almost like
smoke, it wouldn't go away, even when I tried to fan it with my hand.

``Okay legs, walk.'' One step at a time. I made it to the clock without
stumbling, much. Then back. On the third trip, the smoke dissipated; I
cracked a smile and congratulated myself for having beat it. I tried to
remember how I knew to do what I was doing to get over the effect of the
drug. I assured myself I must've learned it in the hospital; I had faint
memories of doing the same activity while locked in my room---they had
given me dynamite drugs. My long-term memory was coming back; soon I
believed I was starting to recall why I had been put there in the first
place. Hazy details were all I had, and I wasn't sure if they were
correct-\/-maybe it was a plot of a book I had read or something. In
time it would all come crashing back to me.

I felt brave enough to put my shoes on. I noticed it was almost four. I
also noticed the flat had been quiet the whole time I was awake, which
meant Uncler wasn't home. I assumed he was at the lab---probably talking
to Donalsed or Niles. At any rate, I thought it best I make a quick
exit; Uncler had been kind to show hospitality to a desperate man, but
drugging me wasn't exactly a confidence builder---it didn't inspire any
kind of trust. What he had in mind for me was unknown, but I was sure it
wouldn't be, as Doc would say, in my best interest.

I buttoned my shirt, tightened my belt, tied my shoes, and threw on my
jacket. I headed for the door. The phone rang, the second ring yielding
to the answering machine; a droll greeting, a beep, then a voice. My
hand was on the knob.

``Darrin. Sam. Hope you're feeling better today. More relaxed? Good. If
you can hear this, don't bother trying to leave. I have you dead-bolted
in. They can't get to you now. The windows have key locks and if you
perchance to look, you'll notice you're fairly high up, so don't worry.
I'll be there in an hour with dinner. If you're peckish there's some
odds and ends in the fridge. I'll see you.''

A dial tone. I tried the knob; it turned, but the door wouldn't budge,
the deadbolts moved by key only. The door was heavy, no way I could
break it down. I had flashes of the hospital. The circumstances were the
same; better taste in decor, but I was still trapped like an animal. I
decided to sit and wait it out. And he was wrong about the
fridge---nothing but a bottle of water, soda, and some stinking Chinese
take-out.

Time passed. I sat on the couch where I had been sleeping and watched
the neon clock, it's second hand passing the glowing red numerals. It
hypnotized me.

I heard the bolt turn in the door. I didn't bother moving.

``Hope you weren't too bad off, pal.'' He smiled cordially as he slammed
the door behind him and fastened the deadbolts---the key went into his
right pants pocket. He had a paper bag tucked under his arm. ``I hope
you don't mind, I have to protect you. I don't want them changing you.''

``Yeah, okay.'' I smirked and glared at him. It was after six.

``Oh, don't take it too hard.'' He threw his coat on a chair and sat
next to me. He put his arm around me. ``Your profile says you are a big
baby, is that so?''

I said nothing. He smiled and put his face close to my cheek, nuzzling
my ear.

``Look what I've brought for dinner.''

He tore open the bag. This display was all a game to him, I was his
child at Christmas.

``It's from the Chinese place down the street, some chow mien, some
rice. Chicken or beef?''

I remained silent and stared at the clock, watching the second hand
sweep. The brilliant blue neon with tinges of red glared, perhaps
pulsed.

``You really should eat, since I imagine you haven't all day.''

``Beef then.''

He handed me the box.

``I think you have some of these left over in your fridge.''

``Been snooping have we?'' He dipped into the chow mien, the noodles
like worms squirming off the end of his fork. ``A biological experiment,
nothing to worry about. How's yours?''

It was more fun to play with than to eat. ``Okay.''

``Eat, eat. Please.''

``Maybe later.''

He looked at me sternly. ``Eat, you need your strength.''

I dug the fork deeply into the box and took a big bite, rice falling
from my mouth. He leaned back.

``Much better. I also picked up some drinks. Beer.'' He handed me a
bottle. ``Indulge my friend, soon we will have work to do.''

``What kind?''

``I'll explain later.''

I drank deeply from the bottle, almost finishing it. He smiled at me.

``How's the old memory doing?'' He tapped his index finger on the side
of my head.

``Better.'' I was suddenly uncomfortable. On the end table beside me was
a photo of Uncler and, I imagined, his wife and daughter. I hooked my
thumb at it. ``Who are they?''

``Family.''

``Where are they?''

``Gone.'' He said without expression.

``Where?''

``Divorced. She left me. She thought I spent too much time at work. You
should have heard what she said about me in court, that I was crazy. You
and I have more in common than you think.''

``Oh?''

``Everybody says we are crazy, but we believe in ourselves, in our work.
It is our life. She left me after I nearly completed my time
experiments.''

I choked on my food. ``What?! Time dilation experiments...'' I chuckled.
``That's fucking stupid.''

He slowly set his food down and looked into my eyes, scanning from one
to the other. He'd probably heard the line a thousand times before and
had a well-rehearsed response. ``Time is irrelevant in certain quantum
states. Of all people, Darrin, you should know that. All one needs is a
bridge to this universe.''

``A magnetic-resonant field is one such bridge,'' I retorted. ``But you
can never get it to properly synchronize for it to do any good at
dilating the flow of time.''

``That's where you come in. I've read all your publications and managed
to get a copy of your work diary. You achieved synchrony. The only
person I know who has.''

He got up and left the room. I picked at the tasteless remains of the
food and set it down. He strode back in, carrying a bottle and two
glasses of whiskey, his fingers dipped into each. He handed me one. I
thought about the night before, and the drugs he had given me.

``A toast: To failed experiments, may they torment us until we are
forced to succeed\ldots as long as they don't permanently kill us.''

I eyed him carefully. ``Let's exchange glasses.''

His expression was one of perplexity. ``Why?''

``Guest's privilege.''

``Fine.''

We switched glasses and I downed the liquor. He slammed his glass down
on the table, upside down. He left the room again. I relaxed, safe in
knowing that he wouldn't get the best of\ldots oh, no, not again.
Feeling groggy\ldots the world twisting into a haze. This time, it
seemed strangely familiar.

He had his coat in his hand and he threw me mine. ``C'mon, we're taking
a little trip.''

He took me under my arm. I remember going downstairs to the garage.
Getting into a car. The slow acceleration of his take-off. Then, nothing
more.

``Hey. Hey, Jensen. Hey, c'mon, wake up.''

Uncler was slapping my face. My eyes opened onto bright lights. I tried
shutting them again, but he continued to slap me. He set me upright. I
felt the cold prickle of a needle going into my arm---the hospital,
no---when it was withdrawn, the world seemed to clear. A person on each
side lifted me to my feet. They pulled me across the floor, my feet
dragging behind me.

``In a few minutes, you'll be fine,'' Uncler said to me. ``I gave you
something that should help with your memory block, and maybe make you
more social.''

He and another man laughed. The voice was familiar. They set me in a
chair, it was padded and comfortable. I slowly opened my eyes. Something
struck in my memory: the painted black walls; the expansive, smooth
concrete floor; the monolithic generator in one corner; the triangular
box, encrusted with panels of gauges and knobs, on a table in the center
of the room, with an electrode dangling from above. And all the wires. I
had to be at the lab, my instincts wouldn't fail me. It was the odor
that did it, that queer smell; a combination of burnt hair, salt water,
jasmine, and the faint ozone from high-voltage. But I thought they
destroyed everything.

``Strike a chord, old boy?''

I looked in the direction of the voice. It was Niles. His
self-satisfied, oafish grin was filled with teeth. Uncler put his hand
on my shoulder and whispered in my ear.

``We need it to work again. We're so close to a breakthrough. What
aren't we doing right?''

I don't know what you're talking about.''

Niles spoke. ``Want me to rough him up?''

``Leave him alone. Listen, Darrin, you have to remember. I need to know.
What's the secret? I've run the machine using your equations, having
rebuilding it at least seven times over. But I can't get it, I'm not the
genius you are. I know the answer is in that head of yours.''

I rubbed my brow. ``I don't know. I can't think. I don't even know what
this place is or what all this equipment is for.''

``He's lost it, Uncler. They cut all of it out of him. He has no answer
to give.''

``Shut up. Give him another dose.''

The needle in my arm again. I was defenseless. The cool elixir coursed
through my veins. My heart pounded harder, my throat swelled, I
swallowed dryly every second breath. I coughed. Uncler walked off,
returning with a greyish-silver ring. It looked like a zero, an oblong
oval not more than two meters in diameter. He placed it in my hands. I
rubbed my thumbs over it, the metal was cool, synthetic.

``Is that the correct material? It cost a fortune to make it.''

``No.''

Uncler paced before me. He snapped his fingers. ``Niles, set it up and
turn it on.''

Niles snatched the ring out of my hands, put it on a staff and slid the
staff into a channel in the top of the machine. Uncler knelt beside me.

``Watch. This has to help. Focus on the ring. Remember. I've set the
currents to flow asynchronously between the internal and the external
compartments and have cooled the core to near absolute zero. I can see
the distortions around the edges, but that's as far as I can take it.
What is the secret? I have to know. There are so many things we can do
with this, so many lives we could enhance, we could travel
long-distance, so many places so far away we could never reach
conventionally. What are we doing wrong?''

Niles flicked on the high-voltage generator; it uttered a low hum that
gradually became louder. I could feel the current it was generating. The
power cumulated in the dangling electrode. Bluish streams of electricity
jumped to the ring; it glowed with supernatural light.

In the cellar, Uncler with the cipher on a staff. His smile. The whir
was loud, becoming deafening; the hairs on the back of my neck stood on
end. Judy chained to the wall, how she struggles to get free.

* * * * *

The machine was screaming an incoherent and wholly penetrating language.
The pyramid-shaped body seemed to want to spin, to jump dimensions, but
remained still. The pitch pierced my ears; I tried to shield them with
my hands, but I couldn't move.

The light, streaming out of the cipher into Judy, she screams of pain.
The pyramid whirling uncontrollably, lifting itself off the floor; the
cipher remaining to keep the circuit connected. The gateway opens, the
link established; the pyramid near the wall unfolds away from itself.
The doorway, a blinding light emanating; I can see others, they want to
travel into this world. I cannot let them, they wish to destroy, I must
shut it down. Turn off the generator, cut the power, shut it down, too
much, can't turn back, destroy the cipher, knock it out of balance,
disrupt the frequency, close the door, danger, great danger, too late,
too late, shut it down before it's too late.

``SHUT IT DOWN!''

``SHUT IT DOWN!!!!''

I screamed. The words stuck in my throat; my head seemed to open, my
brain finally recovering lost information, retrieving data---it will not
stop---I have seen them, they have seen me, they know me and are coming
for me. I've seen their world, I've traveled to their space. They know I
can open the gate, they are sending out their signal to match ours, they
want me to help them. They need me, so they can come to us, so they can
travel, explore, destroy, devour. Their faces are alien, features
contorted, insect-like. Their expressions are contemptible, their
intentions evil---I can feel it. My mind, it will not stop, they have
entered me, violated my thoughts, contaminated me; I have seen their
universe, stop it, stop them, must stop them, no matter what the cost.
DO SOMETHING!!

Darkness. My feet on the smooth, wet concrete, shuffling slowly toward
what's left of Judy---her body withered like a raisin, her once
beautiful red hair burnt off, the outer layer of her once milky-white
skin gone, the muscles tight around the bones, her face frozen in an
expression of great anguish and fear, her eyes merely sockets. She saw
their world and did not return.

A distant voice calling to me...

``\ldots Darrin\ldots can you hear me? Darrin, it's
Sam\ldots Darrin\ldots{}''

I am being shaken. I open my eyes carefully. My forehead is cool, my
skin saturated with sweat. Phlegm sticks in the back of my throat.

``\ldots Darrin..?''

I answer, a garbled croak exits. My vision slowly focuses\ldots Sam is
looking down upon me like a bug under a glass. His face shows streaks of
worry.

``\ldots Darrin, you okay..?''

I raise my hand and touch his shoulder.

``\ldots Darrin..?''

I shake my head. ``Darrin's not here.''

``Come back. You can't leave just yet. Not without me. I want to travel.
I want to see them and their universe.''

I laugh. My frame quivers. My chest hurts, but I cannot stop. I am
nearly hysterical.

``I nearly lost you.''

He sets me upright. We are back in his apartment. My head aches. He
hands me a shot of whiskey. I refuse.

``Take it, there's nothing in it. Trust me.''

I smirk at him and down the drink. My throat burns.

Time passes.

I am coming to my senses---slowly clearing.

Time passes.

Feeling better. Aspirin and more whiskey. Several cigarettes.

Time passes.

I felt awful. I knew I was a wreck. My shirt was covered with crusted
drool and spots of blood. I ran my finger along my gums; they were
sensitive and bled as I touched them, an iron taste on my tongue. More
whiskey. Sam sat next to me, stroking my matted hair.

``You scared the hell out of me. It was quite a task getting you out of
the laboratory and back here in your state.''

``What did you expect? You knew what would happen.''

``I only had a faint idea. I needed to know for sure.''

``Satisfied?''

``Yeah.''

He whispered something inaudible under his breath and looked away. He
knew I was watching him. He glanced back at me and flashed a Cheshire
grin.

``Why don't you take a shower? Clean up. I'll get you some clothes.''

I stood and held my balance. He led me to the bathroom, set a towel on
the sink, and closed the door. I peeled off my clothes and drew a hot
bath---soaking seemed like a much better idea.

Steam clouded the mirror, filled my lungs. I settled into the water,
rubbing the soap over me.

* * * * *

A sharp pain. Judy holding hands with them, her body charred, their
expressions twisted.

``Ahhh!'' I grabbed the sides of my head and squeezed.

Uncler rushed in and knelt beside the tub. He pulled my hands down and
put my head to his chest.

``It's okay, relax, all gone now. Gone, gone, gone.''

He kissed the top of my head, brought my face to his. He lightly kissed
my forehead, my cheek, my nose, then my lips. I didn't respond. My
expression remained stolid, but it didn't seem to matter much to him; he
continued kissing me---his tongue probing my sensitive mouth, the taste
of bile and iron.

He finished bathing me. The images of Judy and the others, they were
gone. Sam was a great comfort. I was helpless and he was strong; his
energy and desire were overpowering. He massaged my broken body, pushed
away the hurt, and brought feeling back into places that I had thought
were long dead, places Marian had tried to stimulate, but failed. He
seemed to know exactly what to do; a warm feeling started in my stomach,
moved up my chest, down to my loins. I kissed him back, hard. My breaths
were rapid, my desire awakened. A thought tugged at me. I didn't think I
found him attractive. He was so different, despite the sameness of our
sexes, but it didn't pose a hindrance, couldn't stifle the feelings I
had in me.

He dried me and had me stand on the bath mat. He ran his hand down my
back and reached for my penis; my hard-on formed in his hand. He smiled
and took me in his mouth. I lay my head back. My thoughts were
non-existent; a pleasant emptiness enveloped me. My brain was quiet and
for once didn't bother me; desire was all I knew, flaming desire.

He brought me to the point of near orgasm, then stopped; he stood and,
with my fingers, undressed. He was already erect. I wanted to reach out
and touch him, but stopped myself. Although everything that was going on
was completely unfamiliar, I had faint recollections, memories like a
watercolor in the rain. I was doing what I could to open the floodgates
in my brain.

He grasped my hand and guided it over his body. I wrapped my fingers
around his erection; he squeezed his hand around mine. I could feel him
throb, the heat he emanated. I released him and, with my hand in his, he
led me to the bedroom.

He positioned me on all fours facing the headboard; the dark wood was
carved with many intricate designs. I let my eye wander through them,
allowing myself to be lost in the patterns. I was trying to occupy my
mind with simple tasks. I was nervous, unsure of what was to happen,
anticipating, hoping---I was shaking. I felt his finger probing me,
pulling on the tender ring of muscle, stretching it so it could dilate
enough to accommodate him. I massaged myself, pulling on my testicles;
he whispered to me.

``Turn on the table lamp, in the drawer hand me the small bottle you
see.''

I did so. He squeezed out a portion and put his finger back in me. He
tossed the bottle on the floor and brought himself close to me.

``It may hurt at first, I'll go slowly.''

Pain wouldn't bother me---I had known so much, nothing else could
compare. He slowly worked himself inside me. I must've given some
resistance, at first he put only a little in, moving it back and forth
before he slid his entire length in me.

I let out an uncontrolled yelp---a little pain, yes, but I could handle
it. His motions were slow, then he moved more rapidly. I was
masturbating.

Time moves slowly when you are unaware of it, it quickly passes you by.
He pulled himself out.

``Lay on your back, Darrin.''

I did so and he reentered me from the front. I continued to jerk myself
off, my orgasm building quickly within me; I sensed it was happening for
him, too. Only a few minutes after he had entered me, we both came.

* * * * *

I pulled the sheet up around my neck. I was cold. Sam sat up against the
headboard; he was smoking, the cigarette hanging lazily out of his
mouth. I tried to get his attention by staring at him, but his mind was
somewhere else.

``Sam, can I ask you something personal?''

``Shoot.''

``Why did your wife really leave you?''

``I told you: the experiments, the work, the insanity.''

``Was it because of someone like me?''

He looked at me and drew on his cigarette. ``No.''

I stared at the ceiling, I was experiencing an overwhelming sense of
peace. ``I guess they destroyed my mind at the hospital.''

``What do you mean?''

``What do you know about it? The truth, I mean. I need to hear it.''

He exhaled slowly, smoke drifting off. ``I heard they tried to destroy
your mind. Rumor has it you lost it, had a habit of raving about some
`others' from another dimension. Ranting about how they'd violated you
and how you needed to shut them out, so the doctors fixed you. Fixed you
up good. No more `others'. So who were the `others'?''

``What I can scarcely remember is they are from the other place, on the
other side of the gate. I remember their faces, I remember seeing them,
the terrifying feeling of not being in my body, being in an alien one.
But, I don't know any more. Sometimes, I think I see them, or else they
see me, but maybe I'm looking at myself from myself. It's hard to talk
about it.''

``Which place are they from? How did you discover their space?''

``I don't want to talk about it. It has a bad effect on me.''

``You're in the company of friends, Darrin,'' he put his arm around me.
``You can trust me. Now you know me a bit better, I think.''

``I know enough to know you know more than you let on. You know what the
machine in the lab does. You just can't get it calibrated properly. It
opens a gate to another dimension, a whole other world, an entire race
of people. Where they are from relative to use I don't know, but I
imagine they are far, far away from our solar system.''

He looked pensive. ``I first heard about your temporal dilation
hypothesis in one of your publications. It immediately grabbed my
attention. To be honest, I was rather surprised they published it at
all, from the commentary which followed. From that day on, I've been
obsessed with the idea. Then about a year or so ago, I heard about the
experiments you were undertaking at the university, trying to prove your
hypothesis. I mean, really, a machine which allows an object, a person,
to travel such long distances instantaneously, over such a vast expanse
of time and space. It's utterly insane. Only a genius could not only
have thought it up by creating the mathematical context, but to also
build an experiment which demonstrated it! Whoa! I had some connections
at the university and after a year of lobbying, they let me into your
laboratory, giving me a copy of your notebook. Some of the pages were
missing. I assumed in those pages was the secret of the detail, since
the machine never worked simply by turning it on according to the
procedure you outlined. Something vital was missing.''

``Flesh.''

``What?''

``Flesh, live flesh. Life-force is the catalyst that facilitates the
gate.''

``Huh? I've never heard of such a thing.''

``Sure you have. You just won't admit it.''

``What does that mean?''

``What I didn't write in the notebook was a myth I my father had
discovered while doing archaeology in mezzo America. It was he who
discovered a series of pictographs, along with a small codex which
described the use of an apparatus which did something similar. In their
case, to facilitate their `gods' arrival in this world. It was an
amazing find, a fifth codex.''

``You mean like the Mayans? But that dates to the first millennium. They
didn't have any form of electricity, as far as we know.''

``Certainly. But they had the capability to generate vast intensities of
magnetic fields using a smelting process on a unique collection of
materials.''

``You're saying the magnetic field is the key?''

``No, not by itself. But by energy transport in magnetic resonance.''

``Similar to quantum tunneling, then?''

``More akin to signaling, but with large quantities of power, in the
manner of an Einstein-Rosen bridge. See, for it to work, there
\emph{has} to be someone on the other side generating a signal of the
same characteristic pattern but with a rotational vorticity which is
opposite to allow attraction of the polarized resonant fields.''

``A wormhole.''

``That would be the laymen's term for it, yes.''

``Which means there is a collaborator on the other side.''

``Exactly.''

``And you think your father discovered these collaborators, back in the
Mayan times?''

``Yes. Time is only valid for us in our universe. It is the ocean that
we swim in. Across universes, time has less meaning. There are only
resonance points, like addresses, which can be connected. Certain
conditions favor some over others.''

``So that means they are performing this feat of traveling now? Just to
us, it is in the past.''

``Whenever a machine, calibrated properly, exists, that allows the
potential of point-connection and therefore travel.''

``Which implies \emph{they} could be anywhere, even here?''

``Once in our universe, they are subjected to the flow of time like we
are. In order to be in the future---relative to A.D. 450---they would
need another point of connection.''

``Any you posit they are looking to travel here?''

``They already have. But that's where my memory stops. I faintly
remember \emph{seeing} them, \emph{meeting} them, in fact. But it's gone
from me.''

``So let's go back a minute. What's this thing you said about flesh
being the facilitator?''

``Yes. Live flesh. Like people.''

``Live people? Really?''

``Yes, people.''

``That doesn't make any sense at all.''

``Scientifically, no. Mystically, yes. By its design, the cipher can
only operate with someone ready to lose their life.''

``Yeah, but human sacrifice is a cultural thing, it has absolutely no
bearing on scientific exploration.''

``My father discovered glyphs from walls in the Temple of Inscriptions,
in Palenque, and copied them. The codex lie in a chamber just beyond it.
It was written that the machine had originally been kept in Teotihuacan
and rituals performed in a secret chamber in order to travel to the city
of Xibalba. The cipher would be used to try to contact the `others'.
Priests wanting power wanted to travel to the Underworld to accost these
others---the Lords of Death, noted in legends---in order to achieve
immortality. In our language, to exist in a place without time moving
from place to distant place. That is what the cipher is for.''

``You call it \emph{cipher} but the apparatus doing the work looks more
like the number `9'.''

``When connected to the circuit, yes, if you include the connection
leaving it. Which makes sense as Xibalba is divided into nine distinct
levels. Some of these levels were the place where human souls were kept.
One soul was required to travel there to allow a bridge created by the
cipher.''

``So in the legend it is these `Lords of Death' who facilitate travel,
but something else is going on, then.''

``Yes. The myth is one thing but the cipher actually does quite another,
in terms of physics.''

``But I'm confused, then, about the need for human sacrifice to make it
work. In the frame of legend, sure, but how do you reconcile it in terms
of physics?''

``That's where my intellect became lazy. I was desperate to make it
work. So I followed the formula to its exact description.''

``I see. That must be what is contained in the missing pages of your
journal.''

``But what you don't see is that the one who is sacrificed receives
redemption and is the guide for the traveler.''

``That is quite an explanation. I see you are not the genius I made you
out to be.''

``Let me have a cigarette.''

He handed me one and lit it for me.

A long pause ensued. I could tell he was thinking deeply, intellectually
digesting the story I had told him. I had nearly finished smoking when
he sat up.

``So that's it, then. The catalyst is a human victim.''

My heart suddenly leaped. ``You're not thinking of actually continuing
the work, after what I just told you?''

He quickly looked at me, smiling furtively. He stood up. ``No.~No.~In
fact, I'm going to go to the lab tomorrow and destroy it.''

``I'd like to go and...''

``You had better stay here. It's too dangerous. Besides, they are still
looking for you.''

``But\ldots I\ldots{}''

``You've had enough strain. Rest.''

I laughed, the thought seemed immensely funny. What should have been an
inner monologue I expressed verbally: ``I guess being caught between two
dimensions while trying to destroy the cipher takes some time to recover
from.'' A headache was just starting to come on.

``So \emph{that's} what happened to you? You were caught \emph{between}
spaces?''

I looked up at him. ``As far as I can remember, when I tried to stop the
cipher's operating cycle, I did it when my body was already inside the
gate.''

He thought intensely. ``So that means a part of you is still in Xibalba,
in one of those levels, suffering from torture?''

``That could be a proper explanation for my predicament.'' The headache
was intensifying. It made me feel cold. I lay down on the couch.

``Poor guy.'' He leaned over and kissed me on the forehead. ``Sleep.
We'll talk some more later.''

* * * * *

When I woke at some point in time later, he was getting ready to leave.
I kept my eyes closed, pretending to be still asleep. The key he used
for the deadbolts he stored in a drawer next to the door. I saw him set
it in there as he pulled the door shut. I quickly got dressed, ran a
comb through my hair, and left. I let him have a twenty-minute head
start to insure he wouldn't return and catch me. I was quiet as a mouse.
I figured I would arrive at the lab after him and give him at least an
hour to see if he really intended to destroy the machine---if not, then
I would personally do it.

I hit the button for the garage and the door slid up. Luckily, I still
had my car keys. I turned on the radio, the music and static making an
eclectic background. The road blurred by, the sun a steady strobe as I
cruised below an overpass. No dreams the night before, how about that.
In the comfort of Sam they had vanished, but through my insecurity and
vulnerability, he had used me. I wanted to hit myself for having been
stupid enough to tell him everything about the cipher\ldots but even he,
as manipulating as he was, didn't have the stomach to add the final
ingredient.

The roadway folded before my eyes, the lane dots twisting into
disheveled shapes. The putrid smell of exhaust, burnt flesh, and ozone
seared my nostrils; I heard voices, faint voices. I snapped off the
radio, but the voices continued; I perked my ears, trying to listen to
them. The language was alien, but I understood it with perfect clarity.
One voice, then many; I saw the lab, Judy, her soft red hair, her smile,
her beauty---she quickly mutated into the decayed heap I had seen lumped
on the floor. She reaches out for me; she wants me to join her in
Xibalba.

The car swerved; I nudged another car into the center guard. A quick
right onto the off-ramp and I was heading toward the house on
Cappuccino. I parked in the back, trying to hide myself. I needed to
regain control; I was going to get out and walk, although I wanted to
stay in the car and drive off---my actions were not my own. I was a
spectator.

The clock read three. Marian usually came home around five-thirty.

Wait.

I hid in my room, kneeling before my futon; my senses were keen, my ears
tuned to the slightest noise. Activity in the neighboring apartments, I
could see them in my mind through the wall; a car going by on the
street, my mind's eye watched it. Marian, come home.

Waiting. Five-thirty-three.

Many things happened at once. I know it all. But order to make sense, I
must filter the out unimportant details.

Harsh scratching at Marian's door. It was from the inside---the cat. It
was furiously trying to get out. With a grin, I rose. I went to the
door, opened it a crack; the cat's orange-red coat was standing straight
up. It growled, then hissed at me. I knelt with a facade smile. Its
green eyes were electric, teeth bared---small fur ball, you're no match
for me.

It suddenly calmed. It sat and stared at me with wide pupils. As I lay
on the floor and looked into its face, it displayed its teeth and formed
its mouth to simulate speech. A voice came out of it. Nothing surprised
me any longer.

``You stupid bastard, Darrin. You promised to marry me...'' I reeled
back, it was Judy's voice. ``Backed right out of it. Now you send me
there and plan to give an encore.''

I sat with my back to the wall. The cat grinned and paced toward me.

``Comin' for you.''

It leaped for my face. I blocked and it tore into my arm. Drops of blood
fell to the hardwood floor. I shook my arm and the cat sailed across the
room. It ran under the bed.

``Come here you.''

It wailed, as it had in the cellar. I shut the door and window; I pulled
the sheet off the bed. With one hand, I flipped the bed upright. The cat
made a mad dash for the door, but didn't realize I had shut it. Its
claws scratched the floor as it tried to make a quick turn. I threw the
sheet over it and pulled the corners together, cinching it closed---it
was bagged, and struggled violently. I was smiling again, ignoring the
pain in my arm.

``Gonna take care of you.''

I drew water into the bathtub---ice cold---filled it to the rim. I
lowered the bag into it.

``Bye-bye.''

It struggled. Air bubbles rose to the surface. Less and less it fought,
until there was no movement---nothing. I pulled a heavy book out of my
room to hold it under for good measure.

A few minutes later, a car parked in the street in front of the house.
It was Marian. I quickly rushed to her room and straightened it, put a
fresh sheet on the bed, shutting the door. I locked the bathroom door.
Marian was still at her car, digging through it. I had just enough time
to wash my arm, bandage the cuts, put on a long-sleeved shirt, turn on
the television, and situate myself on the couch before she came in. She
looked surprised to see me.

``Darrin, haven't seen you in a while.''

I pretended to be into the TV. ``Been busy.''

She went to her room. I hoped she wouldn't notice anything amiss. She
came back out; she hadn't.

``What have you been up to?''

I snapped off the TV. ``I was thinking, we haven't had dinner out
lately. Let's do it tonight, my treat.''

``I'd love to, but Frank and I already have a date.''

``You know him, he'll flake. Go with me.''

``We've been getting along better, he won't flake.''

``Are you sure?''

``Of course not.''

I stood and grabbed her arms. ``Marian. I need to talk and it would be
better over a meal. Please.''

``Okay, okay, let me leave him a note.'' She scribbled on scrap paper
dug out from her purse and set it on the coffee table. ``I need to go to
the bathroom.''

My eyes darted to the door, then to her. ``Something's wrong with the
toilet, it overflowed. I already called the landlord. Can you hold it?''

``I suppose.''

She walked in front of me and looked back.

``Have you seen Max?''

``Who?''

``The cat you found in the cellar. He wasn't in my room.''

``He's probably wandering around somewhere. I just saw him before you
came in. He seemed all cooped up, so I let him out.''

``Okay, but I'm not sure if he can find his way back.''

``If not, when we come back later, I'll help you look for him.''

``Okay.''

A smile was on my face. Soon the experiment would begin again.

* * * * *

I drove at blinding speed, toward the lab.

``Where are we going?''

``A great Italian place near where I used to work. I've been meaning to
take you there.''

``Kind of far, isn't it?'' She seemed nervous. I wasn't sure why.

``Not at all. We'll be there shortly.''

We were nearing the university. I needed one more excuse to get to the
lab. ``Oh, shit!''

``What? What?''

I looked at her. ``Would you mind terribly if I stop by my office and
pick up some papers? I must finish them tonight, I'm going to see a
client tomorrow.''

``I didn't know you were working again. I thought you were not allowed
to work at all.'' She gazed out the window.

I was suddenly caught by what she said. ``How do you know about that?''

``You must have told me when we met.''

``I could have,'' she seemed more nervous. She must be connected with
Doc, to keep an eye on me. I decided to diffuse the tension. ``Perhaps I
forgot, seems like that is the story of my life these days.''

I laughed, she laughed.

``Are we close?'' She asked.

``Very close.''

``Good, because I'm getting pretty hungry.'' Her voice seemed to be
shaking from nervousness, almost as if she were keeping a secret that,
if found out, would be the death of her. Ironic, I must say. We arrived
at the gate. It had a guard posted, which was usual for the afterhours.
He leaned his head out the window of his cabin.

``Can I help you?''

``I want to get in.''

``Name?''

I was beginning to think this wasn't the best idea, going right into the
laboratory when they were looking for me. But here I was, there was not
turning back.

``Professor Darrin Jensen.''

``Professor Jensen?''

``Phone Dr.~Samuel Uncler, he can vouch for me.''

He looked at Marian, then at me.

``She's okay,'' I snorted.

He smirked. ``I gotta check it out.''

He returned to his cabin and picked up the phone. He nodded several
times. Marian was fidgeting in her seat. Only a few more minutes, relax,
almost there.

``Must be a new guy, I don't recognize him.'' I said snarkly. ``The
rookies are so into following protocol to the letter.''

The guard waved.

``Go on through, Professor Jensen.'' He opened the gate.

The lab was housed a small distance off-campus within a series of
nondescript buildings on the hillside. I followed a winding road to the
very back one.

``Have you ever been here before, Marian?''

``Uh, no. Why do you ask?''

I knew she was lying.

``Well then, I can give you the grand tour.''

I parked the car. We got out and walked a short distance to the
entrance. The main entrance was unlocked and the secretary who usually
manned the post was nowhere to be seen. Strange.

``I used to spend all my time here,'' I waxed lyrical. ``It really
disturbed my family life. I really don't like coming here.''

``But you said you work here?'' She asked. ``You don't like it now?''

``Well, no one \emph{really} likes their job, do they?''

``No,'' she shrugged. ``I suppose not.''

We walked down long hallways and many vast open spaces behind windows to
number 19, my old laboratory. I was expecting to run into Uncler
somewhere along the route. The door was locked. I took my set of keys,
unlocked it, and flung the door open in a dramatic fashion. Uncler
\emph{and} Niles were toying with the machine. Surprised and shocked,
Niles walked over to me.

``Jensen. Hello. Nice to see you again.'' He cast a look at Marian.
``What is SHE doing here?'' She withdrew into herself. Sam walked over,
glaring at both of us.

``Kathy, you're supposed to keep an eye on him. Not let him traipse
around.''

``Kathy? Your name's Kathy?! Who's Marian?''

``Calm down, Darrin.'' Sam put his hand on my shoulder. I shook it off.

``Fuck calm down.'' I said.

``You should have stayed put.''

``Well, I wanted to see if you were good at your word. I see that you
aren't.''

``How can you blame me? Such a fabulous piece of work. My intellect is
not so lazy, I'm going to figure the last steps out.''

``That will take too long.''

``Take it easy, Darrin,'' Niles snorted. ``We are readying a new
calibration. Uncler's had a bit of inspiration.''

``Only because he learnt it from me.''

``We're going to try it momentarily, if you'll allow us to finish.''

``If you insist,'' I went to the workbench in a corner, pulled out two
chairs, set Marian in one and took one for myself. Sam and Niles
continued what they were doing before I interrupted them. When they
seemed satisfied with what they had done with the machine and the
alignment of the cipher, relative to the pyramidal case and surrounding
rings, Niles went over to the high-voltage switches. Sam drew the
Faraday cage around the apparatus and motioned to Niles to turn on the
power. Slowly it ramped up, soon a corona appeared on the cipher
coinciding with a series of smooth, slow arcs between each segment of
the outer rings. Sam motioned for Niles to engage secondary power and
the pyramid started its rotation, slowly at first, then speeding up
until it was only visible as a blur. The third and final power switch
was thrown and the machine lit up, exploding with the noise and smell of
ozone emissions. But it did no more than a perform a fabulous light
show. Sam was becoming frustrated, his patience wearing thin. He yelled
at Niles to ramp it down by reversing the switching sequence. In a few
minutes it was quiet again. He then turned to me, eyeing Marian.

``Okay. I give up. Show me what you did.''

I sat smug in my chair with my arms folded. ``Is that how you ask
nicely?''

``Darrin.''

``I'll need some convincing first, the three of you have been very rude
to me.''

``Darrin, please,'' Marian said. ``Let's go and forget about all this.''

Niles shot a look at me; I glared at Niles and at Uncler. 'Don't listen
to her,'' Niles said. ``This experiment is worth more than anything you
need to do to make it successful.''

``You really don't have the stomach for it, either of you.''

Sam came over to me and knelt beside me, close to my face. ``Please,
Darrin. Show us what you did to make it work.''

The room was deathly still, no one moved, no one breathed. In that
moment, I was happier than I had ever been. No noise, no sounds, the
thoughts in my head quiet and people around me anticipating my next
move. I enjoyed it as long as I could.

``Fix Marian and Niles a drink, Sam.''

He nodded, went to a small refrigerator and came back with two shot
glasses. He filled each with a shot of whiskey he had sauced me with. He
handed each of them one and held the bottle in his hand.

``What about you?'' Niles asked.

``I can't drink, Niles. It doesn't mix with my medication,'' I winked at
Sam.

I watched Niles and Marian drink their glasses and to my surprise, Sam
took a deep drink from the bottle. I was never able to figure out how he
snuck the psychotropic drugs in that manner. Seems I miss the most
important details of a story. Doc probably gave him some guidance.

``I don't feel so good,'' Marian said. ``What was in that drink?'' She
passed out, collapsing into her chair.

Niles stared at me.

``What's the matter, tough guy? Can't handle it?''

``I'll manage.''

He looked to Sam, who nodded. He dragged her out of the chair and draped
her over his shoulder. I dug in a drawer at the table where I was
sitting and found a generous length of non-conductive nylon rope. I
looked toward the machine looking for the iron rings I had installed
just behind it, but didn't see them.

``Have you modified the arrangement?'' I asked. ``I don't see the iron
rings.''

``I removed them,'' Niles said sheepishly.

``Well, put them back!'' I snapped. He went to another table in a corner
of the room and came back with the four iron rings. He placed them in
the wall behind the cipher. Niles and Sam lifted Marian from her chair
and stood her at the intersection of them. Sam and I tied her arms and
legs, suspending her a foot above the floor.

``Just like us, huh? The two of us, willing to do what it takes to see
it through.''

His face seemed sad. ``I'm just following your lead.''

``Get a wooden step to support her weight, Niles. We don't want her body
to touch the floor.''

Niles returned with a platform and put it in place. Uncler had a faint
smile on his face; I returned it.

``Now we shall have success. I promise you.''

I found a hydrometer also in the drawer and checked the humidity of the
room.

``We need to increase the moisture level. Niles, hose her and the wall
behind her down. And close the Faraday cage, we don't want to fry
ourselves.''

I jumped into the chair by the panel and whirled around in it, like a
child in a park. On my third or so revolution, it occurred to me the
settings were \emph{way} out of whack, like novices having set the
positions of the knobs in the hope it was correct. I put them into their
correct positions. Niles shut off the water and went to the high-voltage
switches. Everything was in place.

``Sam, take a hold of the pivot which changes the angular position of
the cipher.''

I was in control of the ignition sequence for the electrode, Uncler was
ready to pivot the cipher at my command. A flick of a switch by Niles
would start the procedure.

``Ready?''

I pointed to Niles and he threw the first switch, turning the generator
on. I watched the gauge on the panel. The amperes rose at a steadily.

``Level it off at eight thousand volts. Then, when I engage the
electrode to the cipher, throw the second switch. Wait for my signal.''

He nodded.

``Sam, on my cue, set the angle at 17 degrees.''

``Got it.''

``For now, set tolerance at 25 degrees, frequency 125 MHz.''

``Got it.''

The generator whined as it built up current. For the first time in quite
a long time, excitement throbbed within me.

The needle on the gauge increased steadily: 6, 7, 7.5, 7.8, 8.0. The
capacitors were charging well. I was proud how she still worked as the
day I made her. The voltage leveled. I turned a knob on the panel and
set the electrode into position.

``Two centimeters above. Niles, throw the second switch.''

Blue streaks of lightning playfully encircled the cipher. The pyramid
started its rotation. I pointed to Uncler, he pivoted the cipher and
stopped it exactly at seventeen degrees. Through all his nonsense and
posturing, this part was the truth, he had followed my notes to a `T'
and had practiced the experiment perhaps dozens of times. He was good,
but not good enough to know how to run the panel.

``About two meters before the cage, that's where you'll be able to see
the gate, boys. It will open like a flash.''

My finger was on the switch, it trembled terribly. One flick would power
up the pulse current through the cipher which was in synchrony with the
magnetic field at the rings. I could see the pattern in my mind. I think
I drew it in my notebook once, it was quite a thing to behold. But
Marian still needed to be connected to the circuit. Once Niles threw the
third and final switch, it would be closed. Once in that state, I would
engage the rotational vorticity of the rings and it would be ready to
open the gate. I looked at Marian, the deceitful little spy; she was
slowly moving back and forth while unconscious, as if in a trance.
Uncler's psychotropics were much better than the ones I had used on
Judy. At this point, she was starting to wake up as the magnetic field
began saturating her body. I watched the level rise, doubling as the
sequence was supposed to be: 0.5 Teslas, 1, 2, 4, 8. It was nearly show
time. Hairs on my neck started to stand, the field was leaking from the
cage, there must be damage to the cage. No time for that now. No time
for anything else.

``Ready, boys?'' I yelled above the whir. ``Niles, throw the third
switch.'' He did and I immediately after turned on the pulse current.
The cipher ebbed with brilliant greyish-white light. The gauge measuring
current climbed quickly to nearly the top of the scale. Suddenly a wave
of force struck out, it nearly knocked me out of my chair.

``Darrin! There!'' Niles pointed at the cipher. It discharged a bolt of
light that contacted Marian. She screamed, painfully, and excruciatingly
but it was barely audible above the electrical noise. The gate, where
was the gate? Waiting: Seconds seemed hours.

A flat light appeared on the floor before the cipher. It rose oddly as a
cube---it didn't do that last time, or am I not remembering correctly?
Yes, that was correct, it was not spherical, but cubic---soon the gate
would be opened. Niles stood gaping while Uncler had stepped back from
his position to get a better view of what was happening from my
viewpoint. Marian's screams had ceased. I made a mental note---these
psychotropics are \emph{much} better than the old.

The cube rose, its shape was still odd, it seemed to be fracturing into
a more complex octahedral form, which I knew could \emph{not} be
correct. A six-sided form represented a stable dimensional link, a clean
resonant transport, any deviation meant an error, which is why it
\emph{could have never} been spherical. There must be a problem with the
flow of current, it was surging. The leak in the cage. I needed to
compensate for it. I adjusted the pulse rise time to clean it up. That
did the trick. The cube continued to rise; at the height of two meters,
I would have to stabilize the cipher's resonance---having to set it
perfectly. Almost there.

``Sam, adjust the pitch to eighteen degrees.'' I noticed he was standing
toward the front of the machine staring at the cube. He's going to mess
up the whole experiment.

``Sam! Eighteen degrees, now!'' He ran back to his positon and set it
thus.

I was still having trouble with the current leakage. The ammeter was
starting to bounce, the cube looked almost liquid. Something was
definitely amiss.

``Sam, nineteen degrees. And do it slowly.''

I adjusted the pulse fall time, but it didn't seem to help. A cloud of
smoke and a buzzing from the panel. The overload warning indicator was
flashing. The ammeter was jumping all over the scale. The cube started
to dissipate. The generator had overheated, smoke enveloped it. The cube
quickly dropped to the floor and disappeared. A sick metallic grinding
sound, and the generator came to a dead stop. The sequence automatically
terminated, system automatically shut down. The light extinguished as if
it were a candle that had just been put out.

Silence. The cipher glowed with a slow pulsing supernatural light.

I slammed my hand on the panel. ``Shit!'' I rubbed my forehead. It had
to be the damage to the cage, the leaking current, there was not enough
containment of the resonant energy, it was like a bowl with a hole too
big to hold water long enough to drink form. I leaned against the panel,
trying to think. Uncler and Niles joined me. The smell of burnt flesh
and ozone hung in the still air.

``The generator's blown, Niles said. We'll need to fix it and probably
add a few more transformers to stabilize its output.''

Uncler nodded. ``I agree. What happened Darrin?''

``There is some damage to the Faraday cage, it's leaking. Which one of
you geniuses fucked it up?''

Niles looked at Marian's burnt body with disgust and opened the cage. A
hinge on the right side lay askew. ``I didn't notice this before. Looks
like the damage is recent.''

I stood from my chair and paced over to Marian's body. Her arms had
separated at the wrists, her body lay in a twisted, blackened,
indefinable heap. She had been too fragile; it was possible that when
she had separated, the circuit had been broken, thereby overloading the
generator. The cage was one thing, but I was certain the adjustments I
had made with the pulses were compensating, by the frequency enforcing
containment. Quite possible. Uncler walked with me. He tapped me on the
shoulder and handed me two tablets in an aluminum wrapper.

``Next time it'll be easier with these.''

I thrust my hand into my pocket. ``So \emph{that's} your secret to
making friends.''

We both had a good laugh. Niles looked on confusedly. I didn't care
about the particulars of the scene before me, especially the dead body,
that was not my problem. That was Uncler's. I was consumed with the
failure at hand. I \emph{really} wanted it to be over.

``I need someone with a stronger frame for the next go.'' I looked to
Uncler then setting my eyes on Niles' stocky build. He was sickly pale,
anxiously looking at the gauges on the panel. ``And replace the nylon
rope with something more robust---leather please, but be sure there is
no conductivity whatsoever.'' I tugged at my lip. My mind was racing a
mile a minute---I was \emph{so} close to finishing. I could feel the old
obsession consuming me as it had before. I should have realized that
continuing this work would be dangerous, but I didn't care. Three years
ago I had \emph{finished} the work, seen their world and they mine. But
I chickened out and tried to short-circuit the whole thing, leaving a
part of myself in their universe, fracturing me. How stupid, to having
partially gone through before deciding to turn back and close the gate
without the proper procedure---I panicked and now a part of me is a part
of them and vice-versa.

Uncler cracked his knuckles. ``What's the plan?''

The problem nagged at me, beating a continuous monotonous rhythm.

``We need to fix the cage and install the new transformers like Niles
said. Somebody has to dispose of the body.'' I paused with a maniacal
spirit. ``And we'll need a new connection in the circuit.''

``Yes, I agree,'' Sam nodded, a blank expression on his face. ``But we
need to clean up around here. He looked around to a set of wooden boxes
in a corner of the room which was used to ship the large transformers
and electric motors the laboratory used.

``We could put the body in one of those boxes and then it would be
easier to dispose of it. In its condition, I don't think anyone would be
able to recognize it \emph{as} a body. Then we could take it to the
chemical waste storage facility in building seven and dissolve it. You
go back to my place, Darrin. Niles and I will take care of the body.''

``What about the next set of experiments? I mean once the cage is
repaired and the transformers installed? We'll need another
participant.''

Sam looked at Niles and eyed him up and down. He stepped back.

``No, not me!'' He exclaimed.

``I know, don't worry,'' Sam said. ``We need three of us to operate the
machine.''

``Definitely no. I want to be \emph{sure} we can keep the connection
solid. We will need an oversized person.'' I immediately thought of
Frank.

``You have any ideas, Darrin?''

``I think I might.''

``Well, don't do anything without discussing it with us first.''

* * * * *

It was almost four in the morning when I arrived home. Yes, Sam told me
to go to his place, but I wasn't in the mood to heed his advice. The
house was dark when I arrived---not a single light was on. Marian's note
was still on the table. No Frank. I fact, I couldn't remember the last
time I had seen him. There would be more waiting, but I could be
patient. Scientific success is a hard-fought battle won by the
accomplishments of genius---soon, very soon.

Time passed. It was nearly dawn. I had stopped checking the clock a long
time before. I was tired, but still obsessed with my plan. If I could
just catch a few hours' sleep, then I would feel better, and perhaps
Frank would be back by morning. I laid down to settle to sleep and
closed my eyes. Instead of peaceful blackness, I saw many brightly
colored lights; they flashed before my eyes like a carousel. I
concentrated on them, trying to form shapes---if I could tire my mind,
then maybe I could sleep. I saw Uncler's face, his expression twisted,
his smile malevolent. I thrust open my eyes. I heard a sound similar to
the hum of the generator powering up to activate the cipher. The sound
changed in pitch and grew louder; I gritted my teeth and held my hands
over my ears. Stop. Stop. Louder and louder, my eardrums felt ready to
burst.

``Leave me alone! I'm doing all I can! Look, I know, I take
responsibility that I planned it badly, but next time I promise it will
be successful.''

I felt as if they were torturing me, at least a part of me. I felt as if
stuck in a room which was constantly humming, vibrating my entire form
which was driving me crazy. The hum steadied, as if to acknowledge my
recognition of it. They were trying to manipulate me and I knew it. The
others, they were keen to see the gate opened, properly this time. Frank
still wasn't home. Anything that could be done without him would render
inefficacy. Still, the hum continued with piercing amplitude.

Relax, cease the noise, control. You are here and not there. They were
trying to drive me out of my mind. They knew how, knew very well, but I
was stronger. I was the one in control. I performed the experiments. I
opened the gate.

``You have to wait, you fucks,'' I laughed loudly. ``Kiss my fucking
ass, I'm the master, and if I decide to scrap the cipher, then you're
fucked.'' Torture me all you want, keep me cold, keep me hot, cut me to
a thousand ribbons, I don't care, \emph{you cannot control me}. I
laughed again, this time at the top of my lungs.

I must've fallen deep asleep sometime after that because I don't
remember anything until I noticed a feeble light in my eyes. I opened
them and the sun was streaming through the dirty little window in my
sordid room, but the scene was wavy, like the heat was turned way, way
up, although I didn't feel it. The phone rang.

``Darrin, what are you doing home?'' It was Sam. ``I told you to go to
my place.''

``What? What are you saying to me?'' The room was starting to shake and
quiver as if bobbing at the end of a tether.

``Well, I've got some bad news, the transformers have to be made and it
will take a week. We're shelving the project until then.''

``What did you say, a week?''

``We need those transformers, right?''

``Yes, and what about the cage?''

``You'll have to wait it out.''

``Why are you so fucking nonchalant about it? A delay is out of the
question. I thought you were as obsessed as I?''

``What gave you that idea? The machine, your theory doesn't work. It's
but melodramatic way to murder people.''

``What? This isn't Uncler. Who is this?''

``You know who. I don't want to see you around the lab. You're insane,
brutally so, fucking bonkers. Don't contact me and don't come by the lab
anymore.''

``Sam..?''

``If you do, you'll be arrested at the gate, charged with first-degree
murder, and thrown back into the loony bin, you fucking psycho.''

``Sam, what the hell is going on?''

The phone went dead. I stared off into the bleakness of the kitchen. The
walls started to melt and the floor switched patterns as if in a
kaleidoscope. I fell to the floor.

* * * * *

In the blackness of the mind you don't have any bearing on reality. This
must be what it's like for people who are in a coma. I heard sounds and
I felt movements. I heard the faint mewing of animals and people rousing
in a theater. I remember seeing the world from above, as if floating,
trees and landscape below. A world without people. My back felt hot, the
back of my legs warming slowly as if mounted on something dangling over
an open flame. While comforting at first, the pain started becoming
unbearable. I could feel my eyelids. I needed to open them.

The sun hit my eyes and I was blinded by it. I raised my arm to shield
myself from the light. My body ached and I couldn't feel my legs, other
than the feeling of hot. I slowly managed to sit myself up and noticed I
was in my own bed. As I realized I must be awake, I rubbed my eyes and
tried to focus my vision. I noticed that I had trashed my room---at
least I \emph{think} it \emph{must have been} me. All the books were
thrown to the floor; the crates serving as a bookshelf lay across one of
my legs, cutting off circulation. With my free leg, I shoved it off the
bed. I managed to get myself to stand and waited for the feeling to
return to my leg, which now felt like pins and needles. I hope it hadn't
been cut off from blood circulation too long, I still needed it to get
around.

It was a colossal task dragging myself to the kitchen. My thoughts were
on the call from Uncler. I was trembling violently from fear, fear that
I wouldn't be able to finish my work and see the cipher to completion. I
didn't want to end up like my father, broken and disheartened,
desperately trying to hold onto life, only to end it by my own hand.

I tripped over the corner of the baseboard and fell to the linoleum. I
reached for the phone cord and pulled it; the receiver fell from the
counter to the floor. I dialed the lab, the number engraved in my
memory. I got Niles.

``Is Uncler there?''

``No.~He went home to get some sleep. We managed to clean everything up
this morning. The transformers are on their way and should be installed
later today. I managed to weld the hinge back onto the cage, so that is
repaired. We should be ready to go by tomorrow. I suggest we meet
then.''

``Where?''

There was a long pause and I heard an audible sigh. ``Here, stupid.''

I rubbed my eyes, my head was full of confusion. ``What day is it?''

``Thursday. If you don't mind, I suggest you come here tomorrow, Friday,
at eleven in the evening. Most of the staff will be away for the weekend
and we'll be able to conduct the experiment without distraction.''

``The experiment?''

``Of course. What else?''

\emph{Something} was going on, at this point I wasn't sure if the
conversation with Uncler took place at all. I couldn't trust my senses,
couldn't trust anything that was going on.

``Listen, Niles, if he comes in, have him call me. I have one more
detail to clear up here, and I'll meet you tomorrow evening with the new
participant.''

``So you have that item taken care of? Uncler said you would.''

``Yes. And by the way, who was that Kathy woman?''

``Never you mind. Goodbye.''

He hung up. I pulled myself to a standing position. During the call, my
leg started to get feeling back in it. Apparently the circulation was
not cut off too long. I walked one step at a time to the bathroom. I
needed a shower, or better yet a bath. When I reached the door, just
before grabbing the knob, I remember the cat I drowned in it. I'll need
to bury it in the yard. More work to do. I grabbed the knob and the door
was unlocked. Strange. I slowly turned the knob and peered around the
door, opening it carefully, as if not to make a sound. The cat was gone.
The water had been drained out of the tub, not even a trace of a smell.
I wondered where my book I used to hold down the cat had gone to. I
checked my arm for the scratches, yes they were there, the wound looking
terrible under the bandage. I showered---no patience for a
bath---disinfected the wound, put on a new bandage. Once I cleaned it,
it didn't seem as bad as when I first saw it. I shut myself in my room
and waited.

It was well after ten that night when I heard a car pulling up. It was
an old car, with loud exhaust. It rumbled in the driveway after being
turned off, the sick sound of dieseling of the engine. The front door
was thrown open. I sat up like a shot and frantically dug through my
pants pockets, searching for the tablets Uncler gave me. I set them
under the futon. I heard Frank mumbling incoherently in the kitchen,
rifling through the refrigerator and placing something in the microwave.
I straightened myself and went out.

``Frank? Hi, haven't seen you in a while.''

``Yeah, you neither. What's up?'' the microwave bell rang and he pulled
out a burrito. It steamed on the plate as he placed it on the kitchen
table. I noticed a beer was sitting beside it. He sat down and began
eating ferociously, as if he hadn't in some time.

``I need to talk to you.''

``Go ahead. Talk.''

``What are you doing tomorrow evening?''

He shoved a third of the burrito into his mouth and talked through his
chewing.

``I was supposed to go to a party, but it was already last night. I
haven't slept at all. You want to come?''

``I was thinking we could do something else.''

``Like what?'' He took a long drink of his beer.

``There's something I want to show you. Then afterwards, we could go for
a drink or something. We haven't hung out in a while, you know?''

``True,'' he belched loudly, smiling in satisfaction. ``That could be
fun. If we get bored, we can go to that party I've been invited to.
There'll be lots of girls, I'm sure you can meet somebody.''

``What about Marian?''

``We don't go out anymore, in fact, I haven't seen her in a week. Have
you?''

I shook my head. ``No, me neither.''

``She's got her own life.'' He finished the remainder of his burrito and
downed the beer. ``I'm tired. I want to go to bed.'' He got up and
stumbled past me. ``Night.''

``Good night, see you tomorrow.''

I heard him in the bathroom and then slam his bedroom door. His heavy
frame came down on the bed, it shrieked in protest. I stood in the
kitchen and sat at the table across from the remnants of food he left at
his place. The light from the single bulb above the table burned my
eyes. What to do until then? I got up from the table, turned out the
light, and went to the living room. I snapped on the TV and sat on the
couch. Got time to kill. I sat for an unknown time starting at the
screen, then noticed the cup on the coffee table. The marijuana, that
should keep me occupied. I reached under the couch and found Marian's
stash, there was a lighter on the coffee table, but no pipe. It was
probably still in her purse, or, maybe in her room. I stood up and went
to her room, passing by Frank's hearing him snore loudly and searched
for it, no luck. I then remembered the tablets Uncler gave me. They were
wrapped in aluminum foil, if there was enough material, I could make a
pipe out of it with a pencil. Innovation and I were no stranger! I went
to my room and took the package from under the futon. I unwrapped the
tablets, dumping them on the bed and unfolded the foil. It was just
about the right length and width to do the job. I took one of my drawing
pencils and made a pipe. I used a mechanical eraser to neatly fold the
edges---it was ready.

Back in the living room I sat packing small amounts of marijuana into
the pipe smoking and smoking as images unfolded on the TV. Soon I didn't
seem to mind the ludicrous stories or the pedantic comedies. I was
laughing, silly at first, then I started to feel better. Good, in fact.
Better than I had felt in years.

Soon the entertainment value of the TV waned. I started flipping the
channels one to the next, nothing was on and I was getting bored. As I
was ready to turn it off, I saw the note Marian left for Frank on the
table. I'd been sitting here for hours and hadn't noticed it. Luckily,
neither had Frank. I snatched it up and read what it said.

`Frank, going to dinner with Darrin. Let's catch up later. Love,
Marian.'

Her handwriting was incredible, neat and cleanly-spaced cursive letters.
A mark of a tidy, highly-intelligent mind. I could never write so well,
my handwriting was so bad, I couldn't even read it, which makes me
wonder how Uncler could have understood \emph{anything} that was
contained in my experimental notes. Maybe he was able to interpret the
meaning from the drawings and pictograms. It was all starting to make
sense how he could know so much about my work, yet know so little. I
neatly folded the note, put it in my pocket, turned off the TV and went
to bed.

It wasn't until breakfast time the next day that I realized I slept like
a baby. No dreams, no nightmares, no voices, no pain, no anguish.
Nothing but pure bliss in blackness and nothingness. It was getting on
toward noon when Frank came out of his room. Saying nothing, he went to
the bathroom and I heard the shower running. He came out dressed in
fresh clothes and went to a cabinet, then to the refrigerator.

``Fuck. I got a wicked hangover. I can't go to work today.''

``I feel pretty good. Found Marian's stash last night. It's dynamite.''

``Tell me about it. She gets \emph{the best}. I cannot figure where she
gets it. I've smoked nothing like it.'' He made himself a bowl of cereal
bringing it and the milk container to the kitchen table across from me
sitting in the same place he had the night before. I had picked up the
mess he had made.

``What time you want to go out tonight?'' He asked.

``Oh, about nine-thirty. The place is about an hour's drive from here.
But I'll need to stop by and pick something up before.''

``If it's far, my car won't make it.''

``We'll take mine.''

``Excellent.'' He finished his cereal and put the empty bowl in the
sink. The milk carton was still at the table. ``You want some coffee?
I'm going to make a pot.''

``That sounds good, perfect in fact.''

We sat together for a bit of time drinking coffee and talking about the
funny chaos that used to go on at the asylum, although Frank insisted
constantly on calling it \emph{the hospital}. As the conversation
started to wane and topics became exhausted, we started to talk about
them from the beginning. I never spoke about what I did, Frank never
knew my work at the university or the laboratory.

``This is great fun, like the old days,'' he chortled. ``Hey, you
wouldn't happen to have any of that weed Marian had, would you? I would
\emph{love} a joint right about now.''

``Certainly, let me go get it.'' I went for the living room and I heard
him getting up from the table and going to his room. When I came back to
the kitchen and sat down, he arrived with some rolling papers and a
lighter. I had my aluminum pipe and the bag of marijuana from under the
couch set on the table before me, next to my empty coffee cup. He
glanced down at it and resumed sitting across from me.

``That's a great idea, but I like rolling my own.'' He opened the bag
and took out a portion, breaking in into smaller bits on the table
before him. I took a portion for myself and did something similar,
except my bits were not as small as his. When he'd finished rolling, we
sat staring at each other, he with the joint, me with the aluminum pipe
stuffed in our mouths each of our hands containing a lighter.

``You ready?'' He quipped. I nodded. We lit our respective smoking
apparatus simultaneously taking a deep drag while watching each other.
It was a ritual from those times, a means to connect. Then we did it
when we were given our pills, now it was a different kind of medication.
When he'd finished inhaling, he took the joint out of his mouth and
inspected it carefully.

``Man, Darrin, I \emph{love} this stuff. I have no idea where she got
it.''

I couldn't imagine either, soon the feeling had me drifting away from
the problems which plagued my mind.

``I could smoke this all day,'' he continued. ``I don't have anywhere to
be today.''

And so it was. We sat in the kitchen and smoked. We went to the living
room and smoked. We even went out to the back yard and I showed him the
cellar where I had found the cat. We laughed and laughed and laughed. We
laughed about our lives, we laughed about the hospital, we laughed about
what set of emotions put us there, we laughed at the television, and we
laughed about nothing. Soon it was getting to be evening. We ordered a
pizza for delivery, then smoked some more. All the while the clock
approaching the time to leave for the laboratory. At seven-thirty I
decided to stop smoking while Frank continued. The bag was getting to be
empty, we probably smoked five grams between us. Soon the clock edged to
nine.

``We have to go soon,'' I noted. Frank nodded.

``Okay, I'll go get on some decent clothes.'' He went to his room and I
did the same. A fresh set of clothes would set everything right, the
last set if I was lucky enough. The day was one of childhood wonder,
emotion, and imagination. This was why I really liked Frank when we
first met. He was so easy-going despite having very intense body issues
because of his size. It didn't seem like he ate that much to cause such
weight, but something biological, or glandular, as he would say. But we
never stayed on topic of what made us crazy enough to be committed, that
would be too much. We just wanted to forget about all the troubles of
the world and enjoy it as if it was our last day.

We left the house at nine forty-five. Frank took his papers and the
remainder of the bag with him. We left a bit late but there would be no
traffic, I hoped. Late Friday night, who would be out? Not many, but an
accident along the way kept us stuck. I was starting to become nervous
and Frank seemed to notice. We stopped talking, he looked out the window
into the darkness and the streetlamps passing one slow one at a time as
we crawled our way to the university. As the traffic started to lighten
up, I suddenly realized a grave mistake: I had left the tablets Uncler
gave me on the futon in my room. My mind started racing to find an
alternative solution.

``This is taking too long,'' Frank said. ``I'm going to roll one up.''

While he was rolling, the solution presented itself. I remembered a
meter's length of thick PVC pipe I had on the floor behind my seat. I
always kept it there in case of problems while driving. I made it a
short time after leaving the asylum, when I was accosted one day while
driving. The experience shook me so much that I would feel better with a
defensive weapon. I never had a chance to use it, though. Frank lit his
joint and took deep drags from it. He handed it to me. I shook my head.

``No.'' The smoke smelled divine, it reignited the feeling I had
earlier, but I had to keep it together, tonight was very important.
``Open the window, though,'' I told him.

Soon Frank was laughing hysterically in the car beside me. The marijuana
had a more intense effect on him than me. I sure would have enjoyed one,
had I not been driving. But I was busy nevertheless, my mind rehearsing
over and over how I would execute plan `B'. We arrived at the gate when
my watch read twelve-thirty. I wasn't sure how it became so late so
fast. The guard eyed me carefully. He knew I had come in with Marian the
night before, but he never saw her leave with me. At least this is what
I was thinking. I smiled broadly.

``Be cool. These people are not cool like you and me.'' Frank nodded
trying to contain himself.

``A little late, isn't it, Professor Jensen?'' I didn't act surprised.

``If you live in ordinary time, I suppose it is. But not for us.'' Frank
started laughing again. The guard looked sternly at him.

``Yeah, sure.''

``Phone Dr.~Uncler again, he can vouch for me, if you don't believe
me.''

``It doesn't matter what I believe. But you need to get a proper entry
card the next time you come in. This will be the last time I do it
without one.''

``Okay.'' I said calmly. He walked back to his cabin, reached for the
phone, then stopped. He raised the gate and waved me on.

``Go on through.''

We drove on the same way I had with Marian, stopping at building
nineteen. Uncler and Niles were outside when I pulled up to park. Sam
threw his cigarette to the ground stuck his head in the window and
looked at Frank across the seat, he was cross and his breath reeked.

``You're late. Who's your friend?''

``I'm Frank,'' he stuck out his hand across me and Uncler shook it.

``Nice to meet you. Darrin, pull around to the back.''

Frank started laughing again. Sam smiled. ``I see those tablets have a
different effect on different people.''

``No,'' I said looking at Frank, then to Sam. ``This is a different
medication altogether.'' The three of us laughed. I drove to the loading
dock at the back of building nineteen. It was pitch dark on this side,
no light was visible on the building. When I killed the engine and
snapped the headlights out, Frank and I sat in complete darkness.

``So who is that?'' Frank asked.

``An old friend from before.''

``He's not going to the party with us, is he? I don't like him.''

My hands gripped the wheel. ``No, Frank. He isn't.''

A door on the loading dock opened. Uncler and Niles stepped through it.
I rehearsed my plan `B' one last time in my head.

``I need to stop in and pick something up. You want to come with me?''

``Yeah, my legs have fallen asleep sitting in this car so long.''

We both got out of the car. I stood by the car door, window down, and
Frank next to me. He raised the remainder of the joint to his mouth and
puffed on it. Sam paced over to us, his body language was that of
irritation of having been made to wait. Niles remained on the dock. I'm
sure they wondered if I would show at all. I probably shouldn't have.

``If you follow me, gentlemen,'' Uncler quipped. Frank puffed one last
time and dropped the remainder to the ground, stepping on it. While he
was looking down, I leaned back in the car where my fingers found the
length of PVC pipe. Frank started walking ahead of me, a few paces. I
removed the pipe from the car taking it firmly in my hand. The only
light was being cast from the half-open door on the dock. When we mount
the stairs, that's when I'll strike.

``What is this place?'' Frank asked.

``A research facility,'' Uncler retorted. I was getting ready to extend
my arm for the strike. Frank turned to look back at me.

``You never said you worked in research?'' I could see in the darkness
he face looked confused. He turned back and continued walking. Uncler
mounted the dock stairs and approached Niles who was looking as confused
as Frank did. He mounted the first stair, I pulled the pipe out from
behind my back and extended my arm for the strike. As his foot reached
the top stair, I brought it down full force on the back of his head. He
yelped.

``Wha..?''

Before he could turn, I hit him again. Harder this time and with a
succession of quick blows. He fell onto the dock. Uncler and Niles came
rushing over. Niles knelt over Frank's unconscious body and Uncler shook
his head.

``That was \emph{your} plan?''

I shrugged my shoulders.

``He's enormous, you think I could have handled his dead weight by
myself?'' I asked.

He eyed his girth. ``No, I suppose not. But it will take the three of us
to lift it and put him in the machine.''

Niles fetched a gurney and a blanket. With an effort more significant
that I had imagined, we lifted Frank onto the gurney and placed the
blanket over him. As we hustled the short distance to the lab, I had an
odd feeling in me. It felt as if my whole being were light, without
weight, like air; I had experienced the feeling once previously, when I
had performed the experiment on Judy. Like before, it was as if I knew I
would be succeeding, and had to prepare for the consequences. My body as
I knew it would not be able to withstand the transition into the other
world. The feeling had been frightening then, and fear gripped me now,
for this time I would not disrupt fate by destroying the machine. I
promised success. For the sake of the others and, I would let the
process come to completion. My head started ringing, the happy effect
the smoke put on me had left me the second I struck the first blow to
Frank. As we walked briskly through the hallway, the ringing became more
intense. I started feeling as if there were a thousand people following
us.

The three of us wheeled Frank into the lab. Everything was ready and in
order: the floors polished smooth, lights dim, panels cleaned, and the
machine prepared. The generator had an extra compartment attached to it
to accommodate the new transformers, and the leather ties had been
installed. I also noticed a video camera near the control panel where I
was to sit. Niles saw me looking at it.

``Donalsed insisted.''

``He knows?''

``He has to be kept informed.''

``About everything? The participants?''

``No, not everything. Not right away, anyway.''

``Hey Sam.''

``Yeah.'' He uncovered Frank and prepared to hoist him up.

``Thanks for the call last night.''

He wrinkled him nose. ``What call?''

``You know.''

``What are you talking about?''

Niles became interested in the conversation. I was starting to feel
hostile.

``Oh, don't give me that shit. You woke me late and said the project was
scrapped.''

His face was blank. ``No, I didn't. That's your brand of crazy
talking.''

``Save it.''

Niles was smirking.

``What the fuck are you looking at?''

``You're cracked, Jensen. Hell, I bet you dreamed it up just like all
the other minutia in your twisted banal life.''

I shot a look at Uncler. He shrugged his shoulders.

``Fuck you, Niles. If Frank doesn't work out, you're next.''

Uncler was tugging at Frank's body, he started moving. He went to the
refrigerator and came back with a vial. He had a syringe, drew a portion
from the vial and injected him in his arm.

``Now if the two of you can help me, that would be great.''

I bit my tongue. Once again, I found my mind in a whirl; this time not
on the experiment, but in the tangled briar patch of my inept
emotions---they had my full attention. I analyzed all the relationships
I'd had in my life---the break-ups primarily---trying to figure out if I
had been in the wrong and, if so, what had brought me to it. I thought
of everybody I had been close to, focusing on my father and Uncler. In
time I noticed that I was performing the experiment as mechanically as
if I were washing the dishes or mowing the yard. I had rehearsed it so
many times in my head, I was ready. Niles didn't look at me as the three
of us set Frank into position. It was a bit of an effort, but Niles was
stronger than he let on. The experiment, I had to concentrate on it; a
monumental task was at hand.

Frank was in place, his head hanging lazily to one side, his shirt
covered with sweat. I sat at the control panel. Uncler, seemingly
pleased with the setup, tilted his head at Frank.

``Where'd you find him?''

``My roommate.''

``Well, at least you didn't have to travel far,'' he quipped
sarcastically.

I looked into his hazel eyes; they were soft and warm, as they had been
that night in his apartment. I could sense my body wanting to repeat the
encounter, but my mind was back. I had full control of all my
faculties---the cipher called, I needed to finish this. I smiled and
patted him on the shoulder. ``Thanks for your consolation. Thanks for
everything.''

He nodded and stared at the cipher. He took his position, as did Niles.
I motioned for the first switch. The slow whir began.

``Remember, level the voltage input at eight thousand.''

``I got it,'' Niles said.

My finger was set just above the switch to power up the pulse current.
My eyes were glued to the gauges: 7, 7.3, 7.8, 8.0---it steadied. It was
definitely smoother this time, Niles did a fine job repairing the damage
to the cage.

``Sam, set the pitch directly at nineteen degrees. Niles, throw the
second switch.''

``Roger,'' they simultaneously chimed.

The magnetic field intensity was rising: 0.5, 1, 2, 4, 5.5, 6.2, 7.1, 8.
I felt no effects of the field at my position. Yes, an excellent repair
job. As the whir became resonant, I felt my head oscillating with it, as
if the energy and I were in synchrony. I suddenly had a vision of my
father. On the night he died, I found a note written by him.

`After I'm gone, burn my notes, destroy the things that lie in my
workshop. You must do this or all will be lost.'

Then he'd calmly gotten into his car and driven off; the wreck was found
the next morning. What always bothered me, what I used to obsess over
what this single question: Why hadn't he destroyed his work himself? I
was never able to answer it. Later I figured it was an indirect way of
telling me to continue. So here I am.

Everything was in perfect placement. I looked at Frank one last time in
his present form. It wouldn't be so bad for him---at least he and Marian
would be together. I wondered if they were in love. She \emph{did} write
`love' on the note for him. I felt the outside of my pocket, the note
was still there. Apparently I hadn't changed my pants, just my shirt.
But if they actually \emph{were} in love, they could endure the eternity
together in the spaces without time. Just like I was going to be with
Judy.

``Niles, throw the third switch.'' He did and my finger engaged the
pulse current. The cipher ebbed with tempered greyish-white light. The
gauge measuring current climbed quickly to nearly the top of the scale.
Starting lambently, the light increased to a blinding wash of white and
grey. Frank was a silent participant---his body convulsing, being thrown
sickly back and forth, like a child's doll. I watched as his face
contorted, his jaw moving to one side, twisting the whole shape of his
head---nose folding over, eyes turning clockwise, hair and skin melting
away, spine being pulled extremely forward, resembling a skewed
T-square. But he kept the circuit connected, and that's what mattered
the most.

The flat light appeared. It rose quickly and, in a matter of moments, it
reached a height of two meters, a perfect cubic form. I quickly checked
the gauges---no surge of the current, frequency at resonance. The
machine was operating perfectly. Niles moved away from the generator,
staring into the steady cube of light, frothing with patterns bristling
within. In his haste, he forgot to make minor adjustments to insure the
current stability. I was able to do it from my panel, but it took all my
attention---I wasn't able to watch what was going on in front of me. I
suddenly realized the camera.

A low, reverberating moan came from the gate. It froze my spine. One
last setting, the pulse current wasn't leveling; instead, it was
fluctuating. The gate was drawing more energy to sustain the opening
than we could produce. The new transformers had helped but it wasn't
quite enough. The whir and the spinning pyramidal body of the machine
emitted a deafening sound. I yelled to Uncler. No response. I knew if I
took my eyes from the gauges, something would go awry; the resonance
could shift and the gate would decay.

I managed to do my best and looked up. Niles was only a few meters from
the cube, Uncler farther back. Their gazes were fixed; they were
mesmerized. I yelled to them. Nothing.

The low moan again. I looked toward the gate; several specks of black
had appeared in its energy pattern. My heart seized; it was them, the
ones I had seen when I'd had my body through the boundary. I felt the
other part of myself coming out with them to rejoin me---to make me
whole again. The need to stop the machine became overwhelming; the need
to adhere my tattered soul was even greater.

Donalsed came rushing in. He stood by Niles and they both gaped
wide-eyed.

The specks grew in size, the moan became clearer. A chorus of voices,
hordes of travelers all speaking at once. There must have been hundred,
if not thousands of them in there. Niles was at the threshold, ready to
put his hand through. A massive grin spread across his face.

``It's beautiful,'' Niles gloated, then noticed Donalsed beside him,
``We've succeeded. We can go anywhere in the universe through this.'' He
put his arm over Donalsed's shoulder.

The moan for a second became laughter, I'd swear to it. Uncler turned
and looked at me, his face stricken with confusion. The laughter echoed,
I felt it coursing my body. The specks were nearly the height of the
cube---ready to exit. The moans became distinct voices; chanting,
calling in their alien language, but I understood them. The link was
established and gate had been opened. The power drain seemed to stop, as
if from the other side, power was being projected in order to stabilize
the link. They were also doing the experiment, from their side, soon
they will be free to enter and destroy what they could of this world. I
swallowed dryly.

``\emph{Destroy? Do you think we want to destroy you?}'' A voice
muttered into my ear.

The panel buzzed, red lights flashed, then it appeared that everything
was malfunctioning at once. The current failed, then recovered. The cube
flickered and the vibrations fluctuated, but the gate seemed to
automatically hold itself. I looked around the lab. I couldn't see Sam
anywhere. Behind me, he was at the main panel, randomly throwing
switches and dials. Niles had his hand through the gate.

``I want to see what's on the other side, let's go!'' I heard Niles say
to Donalsed. I jumped up from my seat and shook Uncler. I was yelling,
shaking him as hard as I could. ``What are you doing?!''

``It's too unstable, it'll suck the whole world into it. Look!''

The lab was a wash of white and grey, as if it was inside the cube. The
gate appeared translucent, by its optics, Uncler could be right.

``What?!'' I exclaimed.'' This was your idea!''

``It's a crack in our reality. We're all in danger!''

A wave of anger filled me, the other part of myself was almost through,
I could see a figure walking in my gait among the black lines and Uncler
was trying to prevent me from being complete. I couldn't let that
happen. I squeezed his shoulder, hearing his collar bone break. He
screamed, pitching his neck to one side. My strength, it was either
magnified hundreds of times over else the energy was disturbing the
molecular cohesion of our bodies. I shoved him away, using a mere gram
of my energy. He slid across the floor and struck a wall. I laughed. Not
this time, you \emph{will} see this through.

``Come, come friends. Let's begin a new chapter between us.'' I stood
before the gate just behind Niles and Donalsed.

A chorus of voices chanted in elated agreement. My senses were
heightened, I could feel the thoughts of the people on my side of the
gate: I felt Niles' gleeful infatuation with the gate turn sour, horror
had taken him. He backed away slowly, looking at the hand that had
crossed the threshold; his skin bubbled, muscles gleamed---he had begun
the transformation. Donalsed seemed less enthusiastic; in an instant I
knew his treacherous soul.

``Enter. Go see what is on the other side. See your true self,'' I said
to the both of them.

Niles smiled, seemingly elated in his horror. Drool dripped from the
corners of his mouth, blood from his hand; both pooled black on the
smooth floor. A figure exited, its stark black silhouette stretched
toward me; a sable hand reached out from the horizon. I stepped past
Niles and took hold of the hand.

``Welcome.''

I pulled on the hand. My first thought was to have the hand pull me in
but instead I found I was pulling at it. My newly granted strength made
it easy. It stopped moving mid-arm. An electric spasm shook me. The cube
was vibrating, its energy pattern sporadically shifting with an
accompanying shift in the voluminous noise. It was Uncler. He was at the
control panel, trying to disturb the pulse current to initiate the
automatic shutdown sequence.

``Stop what you are doing!''

I released the hand. I noticed despite Sam's efforts the cube
automatically corrected itself to his shifting pulse duration, rise and
fall times. We were locked in resonance, the gate could not be shut
down. I regained my grip with the hand.

``Darrin!'' Uncler cried. ``Niles.''

In my focus on the hand, the focus on my missing self, Niles was
readying himself to breach the horizon. The thin black lines in the
pattern of the energy stood at our height and only a few centimeters
before us. I stepped back to one side, and he jumped in. His form
vanished into the cube with no more than a pop.

``What about you,'' I yelled to Donalsed. ``Going through?''

He stared at me, wide-eyed and shook his head in a way that told me no,
although I already knew what he was thinking. I could feel Niles on the
other side, his glee at seeing other worlds and new people; new ideas
and new experiences.

``I think you should,'' I used my free hand to grab Donalsed and I
pushed him through the horizon, his form disappeared through the gate. A
black silhouette was at the horizon, it became imbued with light the
closer it came out. I saw its facial features, it looked human but
different. It seemed to be smiling. I heard its thoughts. They were
scientists just like us, curious about other people in other vast parts
of the universe. They were not a threat, only travelers on a quest for
knowledge, for the truth about this space we call reality. I heard the
form say I had been right, my theory was always right. It was only our
fear that set roadblocks for ourselves so that we could not achieve
anymore than we allowed ourselves to.

``We have to shut the gate! Now!'' Sam yelled.

``No, you have it all wrong. Come over here and see.'' I motioned with
my free arm. I heard him thinking he wasn't going to, he was afraid I'd
push him through like I had Donalsed.

``Darrin, don't. Let go.''

I grinned, it was Cheshire. I felt my face expand to accommodate it. His
fear was welcome to me, he was horrified by the changing molecular
structures, how my body contorted and shifted like the pattern of energy
at the horizon. I fed on it. I \emph{used} to be afraid like that, but I
never will be again.

``I'm sorry, Darrin.''

Uncler went to Niles' station and opened the third switch. He was opting
for manual shutdown. The power on our side was starting to reduce
exponentially, too fast for the others to compensate. The hand starts to
recede again. No, I will \emph{not} be broken, desperate, and disfigured
any longer. The cube is shrinking, reducing in height. I still have a
firm hold. I could hear the thoughts from the other side, I am being
pulled inward.

``\emph{We'll be able to repeat this experiment with your knowledge.
Leave your world and come be with us. Let us show you the wonders of the
universe.}''

I a flash I saw all the people I knew during my lifetime, those good
memories and those bad. I felt ashamed how I treated myself and how I
interpreted myself in relation to this experiment. I am the one,
\emph{true} genius, not because I could understand the problem more
thoroughly than anybody else alive, but because I had the courage to see
it to the end and at the end, had no fear. This is what my father
must've been trying to tell me. It wasn't the work that needed to be
destroyed, it was myself.

``Let go! Darrin! LET FUCKING GO!''

I can hear Uncler yelling. He keeps repeating what he's saying. He
really \emph{is} a good sort, despite what he thinks about himself. But
I see he is not ready for the truth, like I had been. I completely
understand him, but I cannot go along with him anymore. What we had
could have been special, had he not chose to take advantage of me rather
than love me, as he so professed. The same could have been said about
Marian and Judy. Frank, though, was a \emph{true} friend, I could feel
the love from him in the gate. Together in the spaces without time,
eternal and complete. Sorry Sam, I've had enough division, enough
strife, and enough nonsense. In a rapid snapping motion, I am pulled
through the gate, my vision a hot flash of alabaster, then the cool ooze
of onyx.

\end{document}
