% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
  \setmainfont[]{Latin Modern Roman}
  \setsansfont[]{Latin Modern Sans}
  \setmonofont[]{Latin Modern Mono}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[a5paper,margin=18mm]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Testimony of a Loved One},
  pdfauthor={Francis Dove},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Testimony of a Loved One}
\author{Francis Dove}
\date{}

\begin{document}
\maketitle

\section{Testimony of a Loved One}\label{testimony-of-a-loved-one}

This place is ennobled with pith and despair; I have found myself
consumed by it. I hadn't been here long when I came to realize this,
perhaps it has been the season of rains that has eroded my better self.
Or maybe it was the pallid, disdainful looks on passersby that caused my
mind to think of strange, odd pieces of philosophy and reason. Whatever
had happened, I had come to a point in my life that things were starting
to change.

Nothing could quell the sinking of my nature, not even writing which had
always helped me to cleanse my thoughts. I was in a different place at
an indifferent time in the world, there was no place for thought or
expression, just an acrid sense of slipping away amongst the tourists
and permanent population. I could have put myself on high and held
comfort in the notion that I was somehow above it all, but this in
itself only contributed to my falling away.

In the decade before, I had been a fan of planning my life, it took me
ten years to realize what I wanted to do with my career and even now as
I am carrying out this task, it seems more trite as each day passes. How
has the world at the dawn of the 21st Century used knowledge like the
one I espouse? All bombs and wars on philosophies. There is no middle
ground, only a balance between extremes.

I have always fancied myself as a writer; in the times between short
stories and novellas, I have found myself miserable for having not done
enough to contribute to the world. So, I shifted my focus to science,
physics primarily, and for a time it filled the void with equations and
interesting problems for my mind to solve. The solutions I devised
didn't necessarily agree with the repose of the intellectual foundation
and I quickly found myself a pariah in my own culture. I published
several papers on my results but they have been largely ignored by the
annuals. I do not bear any malice regarding my fate but find myself
wondering my place and position here. I realize I know something
profound, something that could alter the very nature of space and time
but I dare not construct the machine. I had built a prototype once and
it did exactly as I had predicted but the consequences I dare not
publish; it's enough to be ignored but quite another to be considered a
hack---venturing from a point of no return back to reality is something
quite impossible. So I have been careful with my methodology and pointed
with my words. Nevertheless, I still cannot shake the ennui that is
slowly engulfing me.

I arrived in Europe about two years ago. I began with a stay in Paris
for half a year and eventually wandered to the east. Since that time, I
have lived in Amsterdam, Minsk, Kiev, Vilnius, Budapest, and Moravia
before finding myself in Prague. The premise for these journeys was that
I was looking for a suitable graduate school to undertake my Doctorate
in Physics. But I wasn't really looking for a school, I was looking for
a new home. I feel as if I have been rejected by my people and my
culture---perhaps this isn't exactly true. When I think about it, I
think that I don't want to have my work being used in the systematic
killing of wide swaths of peoples I would never get to know. My work
should try to rise above the putrid wars and if not offer a solution or
alternative, then force the change on the global society by proxy. I
don't feel that it is my place to perform such a feat, but can feel it
in the small spaces of time where it slowly drives me crazy.

The only pleasing times in my life are when I dream. It is in dreams
that I get the sense of my position relative to my work and desire; it
is also the place where my subconscious tries to make sense of the
waking world. Sometimes dreams protrude in this way. Sometimes they show
me what direction to take and less often what decisions to make. I have
been thinking about one in particular.

I am standing in a circle of men. They are wearing snappy, pressed
uniforms of tan ribboned with green; beyond them I can see the darkening
room become smaller, the walls pulling in until they stop just beyond
the circle. This action is followed by an eerie scraping noise carrying
an enormous mass. The room shakes. As my eyes return to the men, I
notice all but one are wearing hoods with blindfolds stitched in them.
The hoods, green in color and striped in a solid white band, fit just on
the crown of the skull and the blindfolds are made from small pieces of
grey fabric fitting just over each eye. The unhooded man presents me
with a small red velvet case,

``We want to present you this,'' he begins slowly. ``As a token of our
appreciation.''

He places the case in my hand and I notice it is relatively heavy. Not
really heavy but weighty as if something of compacted metal is resting
within. I start to open the case and as I look to the man, he is pulling
the hood over his eyes. The case lid creaks as I try to fold it open and
inside a crudely made medallion peeks out at me, gleaming greyly in the
dim light of the now small room. I squint to read the inscription on the
rough surface but can only make out `\emph{kde je dale}?' (where is the
way?). The medallion seems to get heavier in my hand and soon I am
trying to hold it with both hands. The men stand motionless in the
small, squat room; a loose piece of fabric is blowing in an invisible
wind on the wall just behind the one facing to my front. Soon the case
is too heavy to hold and I drop it on the floor. The medallion jumps out
and shatters on the floor. A wind tears though the room and the walls
blow back away from the circle. The men stay fixed, each facing in to
me, motionless as the wind turns from breeze to gale. They are fixed,
unmoving, able to neither see nor affect the world only I am
participating in. The case is broken, its lid unhinged, the medallion in
shards, the pieces now orbiting the circle of men, dragging across the
floor in a sickening thump. I hear voices on the wind.

``\emph{Kde je dale, kde je nassim..}?''

For a moment a source of light appears in the stretched darkness. It is
one star, then another, then a bright one far off, then two very bright
ones very near. Around the two bodies a series of five planets orbit.
One of them is blue and has water on its surface. The scene focuses
tightly on the planet and it has taken the place of the blindfolded man
just before me. I see it is rather small, two moons and a debris field
surrounding it. The debris field is made of the shards from the broken
medallion, some objects still carry the writing but it is twisted,
convoluted, unutterable. I quit the shards and look closely at the
planet, it has continents and stone cities and breathable air. If I
squinted, I could see large movements of population across its surface.
But I can't see it that well, it is pulling away from me and the wind is
dying down, the room is becoming dark and the men are disappearing into
the fabric of space where the planetary system resides. The walls are
returning to their first position and I feel as if I'm about to wake...

The world is black and black, a vast uncharted landscape devoid of light
or objects. I can feel its oiliness over my skin and the smell of putrid
diesel in my nose. There is a feeble green light emanating from some
unknown source; it is flashing as regular as a ticking clock. My
emotions are calm, as the still waters on the small planet. I am the
source and the fruit of all labors. I am the architect staring at a
blank piece of engineering paper, what I etch will stand for a thousand
years. I am history and I am not exactly a piece of it; I flow between
history and space and time. I am the ancient people who populate all the
planets in the galaxy and I am no one. I am tangible and I am a wraith.
The blackness is fading, the green light vanishing into some unseen
horizon.

I am standing in a ruined flat in an unkempt part of town. Dust and
debris, bits of concrete, plaster, and decay cling to the corners and
lay out in large unbroken sheets across the floor. The room is empty
save a small rickety table and a computer. I am at my laptop watching
myself typing furiously at the keyboard. Torrents of letters, sentences,
and paragraphs assault the screen. A swirl of smoke is rising from the
top of my head, my hair is white and long and standing on end. I try to
see what I am writing, to at least catch a glimpse of the title. My eyes
strain to read the words, I believe they are in English but I cannot be
certain.

\emph{Annuals in Physics, The Glide-Stream of Space-Time and the Journey
to its Far Reaches}

What about the first sentence, can I read that? I must move closer to
the screen. But I find that I cannot move closer, there is an invisible,
almost magnetic force that is repulsing me from approaching. The force
is coming from the other me at the computer.

``In times such as these, man must consider the what is beyond the
limits of his science\ldots what we know today is what was known two
thousand years ago\ldots we cannot escape our fate unless we look
somewhere completely different\ldots where is there new excitement that
holds high promise\ldots not here, not anywhere near here\ldots but in
the depths of space and time where our thoughts must inevitably coalesce
with matter\ldots the mind is the boundary dweller, the machine the
bridge leaving this world commencing an era of discovery not dared
dreamt before\ldots this design I proffer exists beyond the limit of
what is known to that which is unknown and unforeseen\ldots beyond time
is what awaits us...''

I am fairly close to myself now, I am pushing with all my might against
the repulsive force. As if sensing my presence, I at the computer turn
to look at myself. He smiles wryly and winks knowingly.

``If you only knew what I know, then you'd have something to worry
about.''

But I am not me, he is somebody else. Me, yes, but a shade something
different. He doesn't even really look like me but I sense we are the
same. Perhaps from a different time or a different set of circumstances,
but nevertheless, we are identical. He stands staring at me.

``You know what the answer is, you have always known. Why must you not
see it?''

``I have no idea what you are talking about,'' I croak feebly.

``Don't give me that. You have read my work and you have founded my
work. Without you I could not have done what I've planned to do and what
I'm going to do.''

The computer moans, its fan beating rhythmic, incomprehensible phrases.

``You have brought life where there once was none,'' he continues while
patting the computer which is now beginning a slow crescendo to a wail.
``You have seen the future.''

The computer is wailing loudly now and is slowly assembling a tune from
the random utterances. It is regular and systematic, organized. He
smiles at me, his eyes a dark brown, almost black like the fabric of
space but without pinpoints of light. I can feel the vastness behind his
gaze.

``Look to the mirror and find the answer, my friend. And we'll both be
better for it.''

I quickly thrust my eyes open to the wail of the alarm. I must have
forgotten to turn it off from the week before when I had a teaching job.

While traveling through Europe, I have filled my waking hours by
performing research projects I feel test the limits of my intelligence
and imagination. If, according to the Greeks, everything has been done
there must be some interesting work in the small spaces in between.
After a few weeks in Prague, a paper was nagging in my brain. I ignored
the impulse and instead filled my time by hanging out by the river and
in subterranean pubs in Vinohrady. But my neglect was to manifest
revenge in the form of piercing headaches and I found that I had to
write the paper.

\emph{Thoughts and Reflections of a Man Caught Between Himself and the
World he has Created}

Between the past and the future lies what is undone. Despite the
obviousness of the statement, it remains, in terms of physics, that this
is all that there is---there is no more. Time is the only vehicle of
change. It is an inescapable conclusion that will be reached in any
discussion. But what is time, this phenomenon we experience so linearly?

Einstein in the early 20th Century said that time was relative. In his
paper on the Twin Paradox, he noted that the flow of time is dependent
upon the point of view of the observer. In his argument, one twin sets
out on a voyage into space at the speed of light. He travels a set
distance, ten light-years out and ten light-years back. When the twin
returns to Earth, he discovers that many centuries have passed and his
twin has long perished. Minkowski, Einstein's professor, agreed with him
and, as a consequence, was the first to devise the higher order of
geometry necessary to understand the paradox. Greeted with great
skepticism at the time, their contention relies on the premise that the
observer is participating in the omnipresent flow of time upon a
space-time manifold. Wigner, more specifically, speaks of a
spatial-temporal manifold where time is a property of the system just as
the spatial coordinates are. What if, for the sake of a tangible
argument, the observer could remove himself temporarily from the
manifold and freely extrapolate positions in space independent of time
and in time independent of space? What if he could retain this
theoretical removal from the manifold and manipulate its properties? How
could such a thing be accomplished? In the paradigm of language this may
be hard to devise. But conceptually it is not unreasonable to assume
that a machine could aid such a feat. It has been written in antiquity
that Buddhist monks could remove themselves from time and see the future
and visit the past. Now this distinction is interesting. They \emph{see}
the future and \emph{visit} the past. Assuming there are no errors in
translation, this means that the past is fixed and the future is not
since it is dependent upon the past.

A scientist of recent fame in the late 20th Century named Samuel Uncler
constructed a device called \emph{The Cipher} which was reputed to
remove a person from his temporal trappings allowing him to navigate
time and space. He argued his machine was based on earlier
archaeological evidence of other machines. The story goes something like
this.

Around 1935, a team of archaeologists from Britain accidentally
discovered a temple while exploring some ruins in Tunisia. The temple
was relatively unremarkable and fit the time when it was constructed,
about 2100BC. In one of the chambers deep inside the temple was a door
embossed with a seal of the pharaoh, Markidu, warning the contents of
the room should not be disturbed on his order, under penalty of
execution. Breaking the seal and pulling back the large, stone door, an
elongated room spread out before them. In the center of the room lay
artifacts not from the time of Markidu's reign, save a scroll in situ.
The scroll spoke that the artifacts were found in the lands to the North
on a military conquest by an unnamed officer.

It was reported by one of the archaeologists, Arthur Johansen, that the
artifacts were constructed out of a type of metal not known to the time
and not known to current science. There were 40 polished rings---three 4
centimeters in diameter, fifteen 12 centimeters in diameter, and
twenty-five between 14 and 16 centimeters in diameter, graduated in
scale. Also, there were six metallic tubes and a strange metallic sphere
that flaked large sections off if scraped with a tool. It was noted that
the sphere absorbed light and glowed brilliantly when brought in from
exposure to bright sunlight into the dark chambers. There were three
bands across the surface of the sphere as if it were mounted in the set
of the smaller rings. Johansen made a drawing of what the machine might
have looked like if it were to be reassembled.

Shortly after discovering the artifacts, the British military was called
to the site and the contents of the chamber were taken to University
College London for study by government scientists. Johansen's report was
classified and the artifacts disappeared from sight. It was rumored they
were shipped clandestinely a few years later to the University of
California for further study. At the time the laboratory was working on
the research related to the first atomic bomb, and was reputed to have
the most modern equipment to study the metallic properties of the
artifacts. A leaked memo dated 25 March 1938 noted that the metallic
objects were crystalline in structure and could not have been naturally
occurring. It was concluded it must have been synthesized and
recommended that a query into the work the Nazi scientists should be
considered. That if they had constructed the artifacts they could build
weapons of great power. Shortly after the memo, or so the story goes,
the artifacts were shipped to an undisclosed location and quietly
buried.

Dr.~Uncler found Johansen's report while rooting through the archives of
the British Museum. He also found the 1938 memo on a fragment of
microfiche. In 1990, he published a paper \emph{Means of Travel in the
Ancient Stellar World} where he detailed the ancient machine and what
its theoretical purpose might have been. There was no script reported on
the artifacts but nevertheless argued that they comprised a machine that
could create a pocket of independent, or in his words, null space-time
where an individual or collection of individuals could use the pocket to
move within the entirety of time and space. He said that such a machine
would allow the traveler to travel in time or in space independently,
but not both. He exampled that the machine could be directed to open a
pocket where the distance say between here in Prague and Cydonia Mensae
on Mars would be only a few meters instead of 75 million kilometers.
Alternately, a pocket could be opened at a single point, say again in
Prague, to a point in the past of hundreds to thousands to millions of
years before. He did not detail if the future could be navigated in such
a fashion and I would expect that such a feat is truly impossible since
there is no real point for the machine to resonate with. Uncler noted
that there is logic and a formed higher geometry to the space-time
manifold which defines specific properties. It is the higher geometric
system that allows a series of differentiated metrics whose complexity
increases with time. He argued that a lower complexity metric of
sufficient order can be specifically identified where the traveler could
determine where or when he wanted to go. He called this process `time
dilation', in that time is not truly manipulated but dilated, opened up
and made passive upon the manifold. In late 1992, Dr.~Uncler constructed
a prototype \emph{Cipher} that was tested at a laboratory on the campus
of the University of California. Although I suspected the work was
classified and not be able to glean much information, I had the unique
opportunity to conduct a phone interview with one of his associates and
reputed Cipher project manager, Dr.~Steven Sanderson. Dr.~Sanderson,
although vague in his answers to my questions, detailed that Uncler had
conducted three unsuccessful tests and two successful tests with two
unnamed colleagues. I asked him if he could provide any details about
Uncler's Cipher but he passed over my request with `Sorry, it's
classified.' He directed me to Uncler's last publication regarding the
machine; an article in the October 1993 issue of \emph{Physics Today}
from which the information for this article was obtained. There were few
details about the machine itself, instead, the article framed Uncler's
argument of a dynamic, controllable, space-time continuum. After this
article, there is no further mention of Dr.~Samuel Uncler except for
critical reviews of said article where he is lambasted and ridiculed for
his theories. Not even Carl Sagan would come to his rescue.

I searched the public records for Samuel Uncler to determine what may
have happened to him. I performed this research on the new grid
internet, a powerful version beyond the old internet of just a few years
ago. I discovered he was born in Chicago in 1965, went to the University
of Chicago where he got his undergraduate degree in Theoretical Physics
in 1986. He then studied at University of California, where he received
his doctorate in High-Energy Physics in 1991. He was last employed by
the University from 1990 to 1993. There is no mention if he was
transferred or fired or if he resigned his commission at the government
facility. I had filed a request under the Freedom of Information Act for
employment and assignment records but so far there is no word. I then
turned my attention to marriage and death certificates. Apparently,
Dr.~Uncler was married in 1987 to Jenine Goddard and had a daughter,
Emilia in 1988. He was divorced in 1990 and there is no record of
another marriage. Also, there is no record of death. Dr.~Uncler held a
passport that was not renewed after its expiration in 2002.

Between the past and the future lies what is undone. As with the tenet
of physics, this is all there is regarding Dr.~Samuel Uncler. If it
begins with the Greeks and the Roman conception of time and space, it
seems to end with Uncler in the only recorded time dilation experiment.
Did he create a pocket whereby a person could travel to the far reaches
of space and time? What has happened to him these past fifteen years?
Was he reassigned to a classified project and his identity erased in a
cloak-and-dagger Cold War style coup? Did he successfully travel to a
far point in space where I am the twin in Einstein's paradox waiting
until old age for his return? Or did he perish in one of his experiments
and his death not recorded because of the nature of his demise? Many
questions but few answers. It remains for time to uncover these
mysteries...

That's about as far as I have gotten with the paper. I had originally
conceived of this paper while dining at Tartino's on Fisherman's Wharf
in San Francisco some ten years earlier but never pursued it. I thought
I had forgotten the work until very recently. I was riding on the tram
during what was supposed to be the summer. Instead of hot, sunny days, I
was greeted with cold and rain. In my lingering depression and finding
myself staring at the scenery passing by, the paper ebbed back into my
thoughts and soon I found I was becoming obsessed with finishing it. I
immediately went home and started writing in earnest; I should have been
teaching a private lesson with a client named Daniela but I quickly
canceled it. If I go on like this, I won't have any money at all. But
right at this moment it doesn't matter. Besides, it seems my client is
looking for more than just English lessons and being recently divorced,
I wasn't looking for a new relationship in this foreign land. There were
too many answers to questions in contrasting languages.

It is a Wednesday like any other here, the city calls to me. In the
deafening roar of silence, the past and the present mingle like two
lovers recently estranged. I have the urge to wander the streets, to
walk upon the same cobbles Goethe had and see myself as a twisted,
post-modern Faust---sans tragedy. Today the sky is a deep grey, there is
no distinction of clouds stretching to the horizon. Rain pummels the
roofs of yawning buildings where the tourists take refuge and me, well,
I stare blindly into the monochrome watercolor.

\end{document}
