% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
  \setmainfont[]{Latin Modern Roman}
  \setsansfont[]{Latin Modern Sans}
  \setmonofont[]{Latin Modern Mono}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[a5paper,margin=18mm]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Life in the Real},
  pdfauthor={Francis Dove},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Life in the Real}
\author{Francis Dove}
\date{}

\begin{document}
\maketitle

\section{Life in the Real or the Transformation of a ``Normal'' Person
Through the Void of an Enigmatic
Existence}\label{life-in-the-real-or-the-transformation-of-a-normal-person-through-the-void-of-an-enigmatic-existence}

The DAY has passed.

It rolled in and over me, tearing my mind apart and jostling my
benevolent body as a rag doll in a child's hands, leaving me with a head
full of fog and a quivering composure. She sat next to me, and after
giving me a look of seduction, sex and apathy, asked for the fifth time
if she could drive. I repeated what I had been saying on every click of
a mile, on every hour of the night.

``No.''

I had really only known her six hours---it seemed like longer, perhaps
twelve, but then again I had been on the road near four hours; time
viewed from behind the wheel can sometimes become distorted, sort of
like driving through a long tunnel black as pitch---with blinders
attached. She might have been my last girlfriend, a friend's girlfriend,
a shared girlfriend, a woman pressing a lawsuit for my ill behavior, or
a woman I didn't even know.

I wish to say I am not the kind of man who consciously chooses to
immerse himself in self-credible or ``occult-based'' thoughts. I'd
rather have no part of it. In fact, I like to think as little as
possible, what with the world the way it is, if one is inclined to think
about it, he would eventually drive himself crazy. So, in the interests
of staying on my side of the fence, of not keeping myself shut off from
the world, my friends, family and whatever, I find it best not to
ponder---no matter what the circumstances. Though friends say to be an
artist, a writer, you have to ponder, I'll stay out in the light of life
instead of shutting myself out---like most artists seem to do. And if I
have to compromise, I'll refuse the art, the ability, and the madness.

I was, however, never certain of the prospects of life, never certain of
my position and my place, and powerless to act on my inhibitions.

Earlier in the evening, before I agreed to drive her to San Ramon, we
had some drinks, a little food, heavily caffeinated sugarless sodas and
generous amounts of concentrated powdered stimulants. My mind was keen,
my body was jelly; she grinned from ear to ear and talked of her life in
long phrases, the words turned sentences jammed themselves into my ears.

Earlier than that, before the arduous, godforsaken journey began, I met
her at a sleazy pool hall---a place where all the lazers, losers,
no-lifes, stoners, slammers and tweakers gathered---it might have been
pure comedy if I hadn't realized fifteen minutes into our stay that I
knew somebody there. I wanted to laugh but only hacked dryly which
sounded more forced than accidental. She seemed amused.

Even earlier than that, I had my ear filled by another friend.
Apparently he was in the midst of an emergency; a desperate, personal
crisis was at hand. The world had fallen in, the pressure on his brain
was critical, the stress would kill him at any moment. It was at times
like this he chose to channel the crux of his annoyances onto the path
of least resistance, to someone else, someone who was close and an easy
target. And I was the chosen target this day. I had told him a couple of
nights ago, as we were having beers, that if he needed anything, I would
be glad to help him out just because we were friends, because I valued
his company. He decided to cash in on the proposed favor. But as I heard
his girlfriend in the background pleading with him to take her to San
Ramon---a small, fairly pleasant town in the hills above the Bay Area, a
distance well over a hundred miles---I had caught myself thinking twice
about having made the promise in the first place, this favor was beyond
the call, stretched beyond its limits. A ``normal'' person
wouldn't\ldots but I was a man of my word, one to live up to my
responsibilities and to let friends down as infrequently as possible. I
had to figure the time involved getting to San Ramon, one literally had
no idea after considering all the variables of traffic, construction and
weather that lay in the stretch between the valley and there. After
offering me all the pleasantries, and setting up me as the officially
sponsored ride, the officiator of good faith that he was requested if I
could fulfill the task. I smirked and tried to back out of it--if there
was any way to, I had to find it without letting him down. I told him I
already gave at the office.

``Hey, this is important,'' he thinly pleaded.

I was sure it was, she was near tears, sniveling and whining. She was
probably on her knees, which made for an interesting mental picture. I
remembered it used to work on him, years ago. Now he was bored and tired
of her--now he was immune.

I wished I had been so brazen, and not caught myself in a trap of my own
design.

``Come over and we'll talk about it,'' he said. And why not? I was a
patronizing guy in need of a good shafting--no lube of course. He was
really going to go forward with it, and throw my promise into my face,
if it came to that. Every part of me screamed not to go, but being a
mediocre writer and adventurer, this could be fodder for creativity. If
I only had known.

When I arrived, I came to realize it was a fine performance, one that
required tens of minutes of rehearsing; she stood so close to me I
picked up a mixed scent of perfume, sweat and fresh, stagnant sex on
her. It made me think of my parents' waterbed, my ex-girlfriend Lisa,
her sister, several rolls of film, a box of condoms, a jar of honey, my
cat Sam and two meters of twine. Lisa and her sister said it was kinky,
I thought it was weird.

``Please,'' she whimpered, ``I need to go see my son, it's been
months.''

I watched her shuffle over to the fireplace and stick her face close to
the fire. ``I'm so stressed,'' she said at last. ``My mother's going to
take him away from me and I'll have no one in the world---no one at
all.''

That must've meant her boyfriend didn't count; he glared at her, mouthed
`not my kid', made obscene masturbating gestures and went off to the
kitchen. After the sound of him rifling frantically through cabinets
echoed through the house, he came back with a lone, helpless Ho-Ho and
messily devoured it. His blank face was smeared with cream filling.

I gazed at the fire seeing the flames lick the blackened bricks. I
pictured myself as a brick, the girl as the fire, and my friend as the
mortar holding me in place. My good-natured, naive urge to help people
being defaced by the flames. I wished I never saw the fireplace, or the
girl, or my friend. I only had one prevailing thought...I wished I
listened to myself and still lived in obscurity in the city, without
friends, without colleagues, and without problems.

And before all that happened, I was resting quietly in my room, the
walls a wash of tan and white, the ceiling a glimmer of specks, the
insides of my eyes a kaleidoscope. My stomach wrenched, my appetite
non-existent, insomnia overtaking, the cause of which unrenowned to me.
When the phone rang, every fiber of my being chorused I not answer, that
it would be certain death, the gun with a single bullet in the chamber
aimed at my head. I smiled and opened my eyes, gazing at the phone, the
receiver nearly jumping out of its cradle into my hand.

The clap of fire, the projectile lodged in the fall wall after passing
through unshielded flesh. An aroma of gunpowder hung heavy in the air.

\textbf{II}

The highway leaped out before me, crouching into curves, tucking itself
under bridges; sodium lamps screamed orange streaks casting eerie
shadows on her expressionless face.

I used to toy with the idea I was losing my mind, but I had given it up
years ago, after seeing what an emotionless bastard I had become---I had
no choice but to. I hated myself. And almost died at my own hands. I had
put all that negativity away, far away, where I could never find it. I
blocked everything, and denied everything; slowly I had become a better
person, more human. And now the muck was being stirred, feelings dredged
up from the bottom of the black pool I was so afraid of. The old glove
of assimilation into the void, was upon me. But why toy? Why even worry
about it? Why fight it? Just admit to the fact I had lost it. Why spend
so much energy prolonging the inevitable? I mean, here I was, exactly
where I didn't want to be, with her, in my car, on the road, to a
destination of great unimportance. I had lost the capacity for rational,
reasonable thoughts indicative of self-preservation. I must have been
out of my noodle. I had broken a branch in the hierarchy of the Tree of
Life and fallen a great distance---all fingers pointed, all eyes stared,
all faces laughed---I had to be insane.

``What are you thinking?'' She asked callously.

``Oh, nothing.'' I said and pulled the car hard into a curve, hoping the
ditch would find me.

``Sure?''

``Well, no, that's a lie. But if you must know, I'm pondering...driving,
flying, crawling, leaning; swallowing, spitting, chewing, licking;
twisting, turning, spinning, whirling...Lisa, Bethany, Lyle and Oreos;
breasts, buttocks, hemorrhoids and vices; a friend, an enemy, his wife
and my car; life, death, lust and the Japanese\ldots Dinah, Hiela, Maria
and herpes; sex, fucking, love and inconveniences; high, low, never and
a memory lapse; amphetamines, depressants, a bore and what I need right
now.'' In my mind I had said it all, and without rehearsal. But my lips
would have no part of it. If I let her know anything about me, then, she
could manipulate her brilliant discoveries. She would incessantly keep
her wandering eyes fixed upon me, looking for more worldly information
in a vain attempt to familiarize herself with my psyche. And I was
having a difficult time as it was remaining enigmatic, it was all I
could do to keep from sliding completely into the seat.

...She sits next to me, her eyes on the road, her eyes on me\ldots I'm
finding it difficult to discern my erratic high from reality, I can't
distinguish which is fact, which is fiction, and which is pure illusion.
I look at her, her eyes meet mine. I follow the curves of her body:
long, tangled brown hair, thin eyebrows, large hazel eyes, small nose
and lips: her chin, her neck, her shoulders and breasts, her waist,
hips, pussy, and legs...I fantasize\ldots I see a movie of us having sex
together\ldots{}

But the sight of my friend pumping steadily into her awakes me,
discarded shimmering silver Ho-Ho wrappers litter his bedroom floor.

\ldots Later:

Near eleven, my thoughts slow, I shut the car off in a parking lot. She
laid rails and I became the 10:53 Express, leaning to check my
reflection. She decided on swallowing rather than breathing and winced
as it went down. I wished to smile but found I couldn't, the phantom
grin permanently wiped from my face. At 5:30 she was cute, at 7:00 she
was adorable, at 9:15 she was naked, breasts perking out, her fingers
probing between her legs; at 9:16 I purposely slammed my head into the
door glass. At 10:00 she was irritating, at 10:20 I wanted to strike
her, at 10:40 I wanted to choke her, at 10:45 I wanted to kill her and
at 10:54, I loved her.

The sway of emotions, the turpitude of my thoughts and fantasies, didn't
surprise me as much as the erection in my pants. I looked down at myself
and was perplexed at what I saw---this odd bulge---it couldn't have been
for her, I wasn't even attracted to her. She was plain, banal,
dispassionate, and patronizing. It must have been from running on high
octane, on pure reaction, on instinct, on fear.

``I like your hair,'' she said solemnly, trying to strike up a
conversation. Not much had been said in the last hour. I had gotten used
to the purr of the motor, the slipstream of the wind, the growling of
the road pounding into my head. I had worked myself into a daze; a
scenario: after a great cataclysm, after total annihilation of the earth
and its components, I was the only soul left in the world, damned to pay
for the sins of a wanton life by (endlessly) driving to a non-existent
destination. And she was a figment of my imagination, the only company I
could muster in the plight of my (doom, situation). And I was fond of
talking to my imagination, believing it could manifest itself outside of
my head. And apparently it had. So, with a complete blank on my face and
a constant monotone in my voice, I nodded and replied with a proper,

``Thanks.''

``That's a nice ring too. Can I see it?'' The projection asked. I held
my hand to its face, the gold caught the glint of the night.

\begin{quote}
``A gift?'' \textgreater{} \textgreater{} ``Yes.'' \textgreater{}
\textgreater{} ``Nice.'' \textgreater{} \textgreater{} ``Thanks.''
\textgreater{} \textgreater{} ``From who?'' \textgreater{}
\textgreater{} ``A friend.'' \textgreater{} \textgreater{}
``Girlfriend?'' \textgreater{} \textgreater{} ``I can't say.''
\textgreater{} \textgreater{} ``Can't or won't?'' \textgreater{}
\textgreater{} ``I really have no idea.''
\end{quote}

Silence. The banter waned. My imagination was staring to lose
cohesion---to lose its imagination. I was desperately disappointed. The
drive was endless.

In San Ramon:

Into town, up hills and down hills, around curves, dips, and
inconsistent pavement surfaces. I was impatient and had been for the
better part of sixty miles. Her directions were a maze of pernicious
angles, disorganized and skewed, related to me in a tone that included
questions she asked of herself: where the hell was she taking us, it's
late and maybe her mother's asleep, what street was that, are we in the
right town, she wanted to make it up to me on the way back, and she was
lost.

I was thinking of what my friend told me before I left with her.

``Expect her to say, `I'll make it up to you'. If she does (and she
probably will), be sure you cash in before you drop her off---or else
you'll see nothing of her promise. Oh, yeah, most importantly, play on
her a little, she'll kick down, promise or not.''

``Nah,'' I said. ``She's YOUR girlfriend.''

``She not MY girlfriend, just my Ho.''

Like whore, harlot, skank, sleaze, Ho, or prostitute; like Ho-Hos, like
the way the cream filling was lodged into the corners of his mouth. I,
like the crumpled silver wrapper peeking out of the fingers of his
clenched fist, screaming to be let free.

``But, you know, she has the tightest pussy. Even after pumping out a
kid. You've got to find out.''

Sighing heavily, I turned my back on him wondering why he had so little
respect, so much anger, hatred and malice toward the small female. If I
hadn't learned it then, I was to find out very soon. The had been trap
baited and the prey snared; all that remained to be done---skin and
devour the poor beast.

The truth was becoming painfully obvious. No sense denying it any
longer. I wanted to\ldots ahh\ldots I wanted to...to...to...I want
to...my erection throbbed. It wouldn't go away. Hopefully she won't take
notice. But, as precaution, I should have brought condoms.

But I didn't and that's good, it'll insure I remain unaffected by her,
never mind all that. At any moment, I'll calm down. Let it be said, I
have absolutely no intention to fuck her.

Could probably buy condoms at the liquor store we just passed, they
always have a good supply of them.

``Not now or never,'' I whispered to myself.

Pretty cheap too.

I have better taste than that and I'm broke, besides HE had sex with
her, Mr.~Single-Speed with Reverse going out. And she LIKED it, she
wanted it, and probably ANTICIPATED it. No way I could share the same
space with HIM, I shudder at the thought, at the pictures in my brain.
If I could only make myself physically sick, that would convince her I
wanted nothing to do with her.

Although she's not bad to look at, even if her hair is a fright.

STOP IT!!

I sighed and felt a sudden silence in my mind, the facilities causing
calamity in me shut down; quaint, piquant, aloof, nice. Even my
imaginary girlfriend riding shotgun was silent, still. I breathed a sigh
of relief. I thought back to my relaxing insomnia in my room at home and
took reverie in the moment of retrospect. Calm. Peace. Passivity. The
first time since...

Fluorescent ones only \$1.69 for a three pack\ldots{}

``There it is!'' She screamed, bouncing up and down while pointing out
the window as if she were fourteen and looking into the monkey house
watching the primates inspect their genitals. ``Park here.''

I pulled to the curb.

``Not here, down there. Somebody else parks there.''

I bet they do.

``Now, here's the story.'' She turned and gave me details on what I was
supposed to know and what I didn't know. This sort of thing is usually
labeled deception but too many hours and too many miles had passed, I
couldn't care less. Too much information had been input. Too many
reactions. Too much stress, anticipation and anxiety. Shutdown had
commenced.

But somehow, somehow I managed enough thoughtfulness to help her out of
the car and to the front door; my noble reward a stumble over a hose the
father of the child had left lying on the sidewalk.

Tripe details of our visit to her mother's and the eye-wrenching,
tear-jerking reunion of her and her son are hereby omitted. Save the
father was nowhere to be found. And the mother was about as agreeable as
a cat about to take a bath. Oh, yeah, everybody---except the two
year-old---was on some sort of drug or another.

Okay, one sentence, fourteen words. An impression of the whole ordeal:

The only item I learned was that I should have less respect for her.

\textbf{III}

While driving, a lifetime could have expired.

Sometime during the small hours of the morning, on the trip back to the
valley, she started speaking. I wasn't sure if I had heard right, I was
lost in the vacuous expanse that was once my mind.

\begin{quote}
She asked about love. \textgreater{} \textgreater{} I told her what I
thought about it. \textgreater{} \textgreater{} She asked me how serious
I get with a woman. \textgreater{} \textgreater{} I told her what I
thought. \textgreater{} \textgreater{} She asked if I ever fell in love
would it always be. \textgreater{} \textgreater{} I told her what I
thought. \textgreater{} \textgreater{} Was it deep? Was it passionate?
Was it obsessive? \textgreater{} \textgreater{} She knew the answer.
\end{quote}

She paused, as if she were afraid of her next question; the silence a
prickled cushion making even me nervous.

``Would you think about being in a relationship with me?''

I smiled and nodded but gave no response. I could've lied, could have
spent the time fabricating a wonderful, poetic line as my friend
inevitably had, but I knew my eyes wouldn't be able to pull it off.

\textbf{IV}

It was daylight, the sun was lazily beaming through the clouds; I
stopped before a house she wanted to be let off at. I was exhausted and
had to get home, back to my room where I could be alone and think and
meditate--my manners were nowhere to be found. She made motions like she
wanted me to walk her to the door, as if I should attempt to cash in on
that promise. I thought to but it remained as such, my body would not
move.

``Well, I...'' she started to say.

``Goodbye.'' I sat, my eyes staring out the windshield. Her face in a
pathetic pout, a disdainful frown, a devastating disappointment. Certain
to cause great change in her, she would alter her ways so that she might
be with me, to get herself up to my standards---right. That is a laugh,
a joke, a spit into the face of human, a kick in the ass to the
continuity and ability of life to sustain and replicate itself.
Ironically, I had no standards and fell for just about everything that
became available to me. But not this one, not in any lifetime. I knew
too much about her although we had not spoken. I knew the ins and outs
of her although we had not touched. I knew the fabric of her being
without compromise, without prejudice, and without objectivity. She
faded away, her face as indistinguishable as the highway in the fog I
had just traversed. The door slammed and I put the accelerator to the
floor, not once looking behind me.

The DAY has passed.

Seconds to minutes to hours gone

A day never to have known

What hopes, what desires

Time being a thief.

Tis the NIGHT now.

Time to reflect, time to solace

My aching head and body

Time to find a quick resolve

That offers immediate pleasure.

My friend phoned and asked if I had indeed fucked her. I didn't answer
him, not even wishing to speak to him, limiting myself to only thinking
about it. Wondering absolutely nothing, wishing for naught; time spent
viewing things in a less productive light.

I sat back and thought long and hard about what I had done and what I
had allowed to happen to me. Let it be known, I had the absolute control
of a deaf-mute over my environment. I had set me up and thrown myself to
the whims of random chance, not my friend, not the guy who I thought
should catch hell for setting the events in motion. In my own recently
acquired fucked up way, I had cleverly masked my emotions, my desires,
and my perceptions--all in the journey to some sort of enlightenment the
Buddhists call nirvana. I had created a screwy cast of characters and
analogous relations to better answer the questions of why: why I had
kidded myself, why I had become disturbed, perhaps obsessed with present
and past events, and why the whole affair had such a profound effect on
me. The girl served as the curious side of me, my erection as my
limitations, the stimulants my way of altering reality and the
Ho-Hos\ldots well, I'm still not sure where those things fit into this
whole mess. Do I blame myself? Do I pity myself? Do I hate myself? Do I
think this changed me? No, no, uncertain, and maybe for the good but
more for the bad.

But. . .

Glad the DAY is gone.

The adventure a wash

Clear memory now a peek through dirty glass. . .

No regrets. Not now or never. I wish to hide away, to be with myself, to
impregnate my creativity, to birth a new me, and to disappear. Perhaps
to a place unknown to even me. That's about it, I guess. Oh, yeah, to be
more selfish, that would be nice, and to obsess even more on
introspective thoughts. The comforts of which are invaluable and without
horizon.

\end{document}
