% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
  \setmainfont[]{Latin Modern Roman}
  \setsansfont[]{Latin Modern Sans}
  \setmonofont[]{Latin Modern Mono}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[a5paper,margin=18mm]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={The Flashback},
  pdfauthor={Francis Dove},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{The Flashback}
\author{Francis Dove}
\date{}

\begin{document}
\maketitle

On this day in California, it was long and hot, much unlike the cold
climate of the Midwest I knew so well. The heat was unbearable. I had
been sweating; stagnant water reeked on me. She was ahead of me, in the
distance, her brown hair and black eyes hypnotizing me. She was a native
of the state; I was not. She was pure and innocent with love in her
heart; I was blackened, a soul of ash, empty, abandoned, ready to strike
and sate my desires. I should be dead; a part of me is, but the rest has
yet to catch up, an irony to end all ironies---it is a fate I have
learned to accept.

It was early in the new year when I first met Valerie. She struck up a
conversation and I mostly listened. I didn't mind so much; she seemed to
have a lot to say, and I liked to keep my life a mystery. She rambled on
about her job: how it was such an intolerable place to work, the
annoying customers, the demanding boss, etcetera. We both worked in a
bank; it was a branch of Sanwa and the only one in Oakdale, a town stuck
in the expanse of the San Joaquin valley. She was a loan officer and I a
teller. I didn't particularly like the job, but I supposed it supported
me and it was the only place I could tolerate.

We were standing outside near an old drive-up window. It was late in the
afternoon and finally starting to cool off.

``Did you see the way he looked at me?''

``Who?''

``The old man who came over to my desk, about one o'clock.''

I smiled and lit a cigarette. ``No.''

``He just stared at me, like he didn't know where he was or what he
wanted. He said some really strange things. Something like `fire
destroys but water consumes'\ldots something like that.''

``Could be he was hot and wanted a glass of water, maybe it was his way
of asking.'' I laughed.

She hit my arm. ``Not funny. He really scared me.''

I deeply inhaled the smoke. ``Oh. I'm sorry.''

She waved her hand, fanning air on her neck. ``It's so strange to have
such weather in February, it's usually not this hot until summer.''

I took a long drag on the cig and exhaled it slowly, watching the smoke
curl away. ``Indians call it early summer, season of the flames. A time
of drought.''

She smirked and fidgeted with her dress. ``Sounds interesting. So do you
like working here?''

``Yeah.''

She paced, smiling. It was quiet between us; I smiled back. She nodded
and took a quick glance at her watch. ``I'd better go in, break's
over.''

I watched her walk away. I looked up at the sun and flicked the spent
cigarette at it. I wished for it to be cooler, snow perhaps, something
different. That was one of the problems with living in California---no
change of seasons. It was so unlike Illinois where we used to live, my
parents and I and the occasional housekeeper. In February, the
temperature would be near ten below---snow up to the porch, caps on the
pines, the lake frozen over, the old steam heater on the far wall
uttering a steady hiss, the windows fogged. It was such a pleasant time.
I wished it could have gone on forever, but as things go, something
always comes along to adulterate it. I couldn't remember, but whatever
it was, it changed me forever. An accident perhaps, the careless
housekeeper, so much like the others, she never did know how to light
the oven or the boiler when the pilot went out. It was fate, I suppose.
I heard tragedy makes one's character strong, maybe it's true. It gives
one the insurmountable strength to carry on, to possibly one day have
relationships with others.

I met up with Valerie again later in the month. She looked better; she
had dyed her hair, put on her make-up differently, wore thin frame
glasses instead of the cola bottle type, and dressed better, wearing
more flowing dresses instead of fluorescent shorts with sharply
contrasted, plain, button-down shirts. I must admit, I had never really
taken much notice nor much cared for her, but now there was something
awakened that drew me to her. Perhaps it was the touch of rouge on her
cheeks that lit up her face, or maybe it was the pleated skirts. Her
renewed energy stirred something deep within me. I had no explanation
for it. After work, I walked her to her car.

``I tell you, I didn't think I'd make it through this week. It was so
hectic and the boss, he's so damn impatient,'' she tugged at her now
darker brown hair and gazed at me with her black eyes. ``I don't know
how much longer I'm going to work there, I'll probably get fired soon
since I haven't been balancing lately. I'm supposed to be a loan
officer, not a teller, I'm not supposed to be helping those customers.
That's more your job.''

I laughed and looked off into the distance. The sun was just beginning
to set. It was a little cooler that day, as it had been for the last few
days, but it still felt too hot for me. She opened the door, put the key
into the ignition and turned on the radio. `Chicago' by Graham Nash came
on.

``Don't worry about it, Valerie, everybody makes mistakes.''

The song echoed through the car\ldots{}`won't you please come to
Chicago, we can make a better day'\ldots I stood and listened. Her mouth
moved as if she were speaking, but I didn't hear the words; I was back
in Illinois where I first heard the song, where my fantasies frequently
converged with reality. I saw the fields of snow stretched all about me,
reaching, clambering over the entire land. I was a surveyor, an
archaeologist gazing at the spectral white, trying to find a hint of
civilization---if I could only grasp a remnant of life. Just to know I
wasn't alone in the barren world would be a comfort. No sound, nothing.
Something reached out and shook me.

``Are you okay? I thought I lost you for a minute.''

``Yeah. I'm okay. I was marveling at the sunset.''

She turned and looked. ``Uh huh.'' I rubbed my brow as if anticipating a
headache.

``Maybe I've lived here too long, but all I see in the sunset is the
smog.''

``Like the sky is on fire.''

``I suppose.''

``It's beautiful, isn't it?''

I pulled out a cigarette and lit it. She looked at me with her black
eyes, her deep black eyes. So clear they could have been tiny lakes, so
similar to the one behind my parents' house.

``Do you have any family?'' She asked.

``No, they're all,'' I looked again to the sky. ``Gone. Dead I mean.''

``I'm sorry, I shouldn't have asked.''

``Don't be, there's no reason to.'' I smiled at her.

``Well, let's go get a drink or something, instead of talking out in
this heat.''

I inhaled smoke. ``Sounds like a good idea.''

We got into her car and she drove downtown, which consisted mainly of
paltry one and two-story buildings coated in beige, sometimes an
occasional light brown or faded blue. I figured the buildings were
painted to match the colors of the surrounding hills, sort of a blend-in
effect. I thought it was quaint; she wondered why I paid so much
attention to the little things, why I cared so much for details.

``I guess ever since I was a kid, I wanted to be an artist and do
something spectacular with reds and yellows.''

``Did you ever?''

``All the attempts resulted in failure.''

``You're too hard on yourself, I think.''

``No, my parents were.''

And she left it at that.

We stopped at a bar. It was early and the crowd was light. We could
converse without having to shout. But as we settled down for cold beers
and she opened her mouth to speak, I didn't feel like talking. I felt
like listening, letting her stories wash away mine. Maybe that was why
people I have run across, like Valerie, always preferred to have drinks
with me-\/-they could spew their life stories without having to feel as
though they were putting somebody out. I sat back and relaxed, drinking
one beer then another. In the middle of one of her sentences, a glare
from her glasses reflected into my eyes. In the blinding instant, I
could see the landscape of Illinois, snow-covered and flat, the air
chilly, a light breeze hanging in the air. A glint of light sparkled in
the snow, it looked as if something was partially buried in it. I left
the table to see what it was. I knelt before the object and tried to dig
it out. The snow was cold on my hands; it gave me a start. I closed my
eyes only for a moment, almost a blink, and the landscape was gone. I
found myself outside in the parking lot, tugging at the locked door
handle of her car. I stood for a time trying to shake off the sick
feelings, then turned back to the bar. As the table came into sight, I
saw myself sitting there, looking closely at her. I glared at the figure
that had imposed itself as me and quickly sat in its place. Valerie was
within inches of my face. I slowly leaned back in my chair.

``What? Is something wrong?''

``No, no.''

``So,'' she smiled slyly. ``What are you thinking about?''

``Not much.'' Which was a lie.

``Oh,'' she said in a disappointed tone and gazed off into the depths of
the bar. People were filing in and I found myself wondering what she had
been talking about, exactly who she had been talking to. Who knows what
may have been said, no telling how long I had been gone. It was quiet at
our table while the noise steadily increased around us. She turned back
to me.

``You're not saying anything. You sure nothing's wrong?''

``Not at all. What makes you think that?''

``A minute ago, you were very talkative, we were having a good time. And
now you clam up.''

She figited with her glass, tracing her finger along the rim. I stared
blankly at the bar.

I heard a distant voice whisper in my ear, cool and calm; the
pronunciation was hard, almost English.

---Talk to her.

``I'm sorry. I hope I didn't put you off. I get so easily distracted by
people sometimes. I get so wrapped up in watching them. I try to see
into their souls, I'm curious what they're thinking about. I do it at
work, too. In fact, the other day, I had a run-in with a customer, I
mean this guy called me an idiot after I got stuck on the computer. It
wasn't my fault, the damn thing. So you know what I did?''

``No...''

``I told him to screw himself.''

``And you still have your job?''

``As far as I know. But I did apologize to the boss. Shouldn't have done
it, but I said I was sorry.''

``I had no idea...''

``There's a lot of things you don't know about me.''

``I bet. When did this thing at the bank happen?''

``A couple of days ago.''

``What day?''

``I think it was Tuesday.''

``I was working then. I didn't see anything.''

``You should have. It was pretty dramatic.''

``Hmm\ldots wait, it could have been Wednesday. I called in sick.''

``Yes, Wednesday. That must have been when it happened.''

``Funny. All the action goes on when I'm not there, and nobody tells me
about it.''

The voice whispered again.

---Why don't you go to the bathroom?

At first I resisted, trying to ignore it, but as the voice reverberated
in my head, echoing within the recesses of my mind, I found its request
undeniable.

I only wanted to stay in the john a short while. I was anxious to get
back to the table, to say the things I had been thinking since sitting
with her. I wanted to tell her what I truly thought of her, to talk as
though I had known her for a long time. I felt as if I were becoming
accustomed to her. I splashed water on my face, toweled it dry with
paper, and left the crumpled mess by the sink. As the door closed behind
me, I noticed that I was again already at the table. This time I was
leaning across, kissing her. I stared at the figure; it broke from her
and looked at me. It said something to her, then got up and strode
toward me. The eyes of the stranger studied me carefully; his arm
reached out for me, fingers clutching.

``To the bathroom.'' I was pulled in. he door closed. I stood facing
myself, but it wasn't myself, it was someone who had taken over me. We
were physically identical in every way, but he spoke differently, with
an English accent. His speech was heavily pronounced.

``Look, don't be an ass. Let me handle things from here on in. I promise
I'll let you participate later, in fact, I won't even bother you. You
need help and you're damn lucky I'm here. You're going to ruin
everything, so I want you to shut up. Understand?''

``I, I said shut up.'' He smiled, looked in the mirror, and straightened
his tie. ``You don't know the first thing about women. I like the stupid
story you told her. It was an obvious lie, I hope you know. She knew it.
Yes, she did. I can't trust you to do anything. I'm taking over, as I've
had to before. I'll handle her, then you can do the rest.''

I shook my head. He didn't cast a reflection in the mirror. He turned to
me and grinned.

``Don't worry, friend,'' he put his arm around me. ``I'll make things
right, as always.'' He seized me, drawing me to him as if to embrace. I
looked in the mirror, wet my hands, picked up the used towel, and patted
my face. I fixed my hair and straightened my tie.

``Much better.''

I turned to leave. She sat watching me as I made my way back to the
table. Her eyes stared, wide and searching, following me as I sat down.
We sat not saying anything, just staring at each other. I did as
instructed. I became lost in the pools that were her eyes. I saw the
black lake behind my parents' house, a lake whose water was so dark, so
murky, I could never see beneath its surface. I often wanted, while
growing up, to jump into the lake and immerse myself in the black water.
I'd stand on the bank and gaze down at its mirrored surface, seeing
myself peering into it, watching as my features changed with the ripples
in the water. And there were nights when the waxing moon was high in the
sky, when my whole body didn't look right. I appeared contorted-\/-my
head warped, listing heavily to one side, shoulder lifted, one arm
twisted behind me in a sickening fashion, a low moan coming deep from
within me. I wished to turn from the lake in fright, or maybe kick at
the water to make the shape change, but I did neither. I was too
fascinated, too wrapped up in the horror of the sight. I let the images
immerse themselves in my brain.

---Jump in. It looks inviting, doesn't it?

Yes. I smiled at Valerie and we left the bar.

Nights were long. My parents continually warned me, sometimes with
physical punishments, to stay clear of the black lake. One day my father
hoped he could get enough money together to fill it in. They would lock
me in my room to be sure I was kept away from it. But from my window, I
could always see it. I'd gaze out, watching as the trees seemed to part
just so I might catch a glimpse of it. I knew I was a part of the lake
and the lake was a part of me. We shared an existence completely
dependent on each other. I was born here, in this house, knowing only
the land, my parents and the life we lived in this countryside. I
belonged to every part of the landscape.

The room was dark and hot. I could hear a chorus of voices whispering. I
opened my eyes. Valerie sat on the edge of the bed, her eyes fixed with
mine, her clothes falling to the floor, shirt removed, bra
unhooking---her body was tight. She felt warm, comforting against the
cold of my skin. Her hand caressed me, slowly moving up and down my leg.
Her mouth pressed to mine-\/-the taste of alcohol, the smell of stale
cigarettes. The heat was building within me, heat like the sun's;
shaking, quivering, anticipating. I ran my hands over the length of her
back, pressing into her spine; she tensed, then relaxed, tense, relax.
Her breath quickened. I could feel the heat that emanated from between
her legs as she ground herself into my thigh; I wanted her, more than I
had ever wanted anybody before. She was different, new, in control---I
was anxious to know what she was like, how I would feel sharing her. She
smiled a wide smile, teeth gleaming; she mounted me, her hand sliding as
she put me inside her. Waves flooded my body. Only the long walks on the
shores of the lake could compare to the ecstasy I felt---only a dip into
the lake itself could surpass it. I was completely out of myself; I
could smell the heat of passion and the pleasant cool scent of the
pines. In her lips, I could taste the black, stagnant water of the lake.
As our excitement heightened, I became lost between the two worlds. I
tried to regain control, but lost my grip. The energy of our lovemaking
escalated. I was poised inside, ready to snap, ready to sate my desires.

In a final burst, I was cast far from myself, the emotions springing me
away.

I was standing before the house I grew up in. Its weathered facade
glared vacantly down on me. In the feeble light of the moon, I could see
its charred outline. In the distance, water lapped sickly against a
putrid shore. A hand rested on my shoulder. Valerie nuzzled my ear; we
locked our hands together. We walked beside the remains of the house,
toward the direction of the lake. We laughed, we talked and kissed; I
was in love. Our walk meant more to me than anything else she could have
done for me. I was no longer cursed to wander this place alone. Pines
stretched themselves above us, sweet dew dripping from the needles,
giving the impression of rain. As we cleared the house, the lake came
into view. Valerie stopped. She said she had gotten something in her
shoe. She balanced on one leg, searching for the object. The familiar,
accented low voice whispered in my ear.

---You know you have to give her to me. It's as we've always done. We
share everything.

I spoke softly, so Valerie couldn't hear.

``But I love her. I can't do it.''

---All the better. I will love her too. But love or hate, you cannot
deny me.

``Why?''

---We share, we coexist. No more talk. You must put her into the lake.

She got up and we embraced. She felt so good to my pallid body, so kind
and warm, she smelled sweet from the dew. But I knew I couldn't deny
myself. If I did, I would die\ldots{}

---Or at the very least, wish for death.

With my parents it had been so simple---I hated them. Throwing them into
the lake had been an easy matter. Easy, but not painless for them. My
father had screamed as his body was dissolved, inch by inch, flesh to
muscle to bone. His screams sometimes still echo through the pines. I
didn't want her to go through the pain, the suffering. She wasn't
deserving like my father was. I hated him. I love her.

We were before the lake.

---You know what you have to do.

I resisted. I didn't want to send her. I didn't want to share her. I
wished to keep her for myself, that's what I want. In my reflection in
the water, I saw the figure disguised as me. She is in his arms. He is
lifting her, ready to throw her in.

``No!!!'' I snarled. ``\emph{I} will do it!''

I held her tightly, kissing her one last time. She smiled softly; all I
felt was love. I couldn't let her suffer alone. We both went into the
lake, our shapes dissolving into the water.

The world is a dark, shapeless void; I walked, alone, hands searching in
the blackness. I felt moist, moss-covered walls hewn out of live rock. I
negotiated my way slowly, desperately searching for an exit. My breath
became heavy, my anxiety increasing. I stopped; my feet started to sink
into the mucus-saturated ground. I broke free and ran into the darkness,
unmindful of what I might encounter. Not far ahead, a dim light
emanated. I kept running, running toward an end. Through a baroque
archway and I was in a room. It was the basement of my parents' house.
The light came from a flame---the boiler. I ascended the stairs.

Out the front window I saw an object glistening in the snow. Quietly, I
pulled open the front door. I paced out and knelt before the object; my
hands dug through the snow, my cold fingers wrapped around a polished
brass candlestick. I looked up, thinking it possibly could have been
thrown from one of the upper-story windows. I picked it up and a jolt
went through me. I smiled sadistically, for I knew in an instant the
nightmare was just beginning.

I searched the house for any living being. Upon finding the family dogs,
I bludgeoned them, their silly gleeful expressions still fixed to their
faces. The cat eluded me, but the taciturn housekeeper wasn't so
fortunate. I planted the candlestick into her skull, then tore open her
throat. She fell without so much as a breath. I heard rustling upstairs.
I found my father in his office. He was sitting in his chair. His speech
was thick, heavily accented, just the way the voices always sound.

``I knew I should have filled the lake in. But it's fate that this day
has come. As it will eventually come to you.''

I rushed him. Blood, warm and comforting, sprayed on my face. He fell to
the floor, twitched once or twice, then was still. I set the
blood-drenched candlestick down and dragged his body to the lake. A
long, smeared stream of crimson trailed behind us. As he splashed into
the lake, his eyes shot open. He let out a scream so terrifying and
painful, I had to shield my ears. I watched him dissolve, as though his
body were in acid, piece by piece. The shrieking cry echoed through the
pines. His skeleton floated momentarily, then was devoured by the lake.

I returned to the house to retrieve the housekeeper. I saw my mother
coming out of the front, apparently following the trail of blood I had
laid. She ran back into the house, locking the door behind her. I stood
back from the door and smiled. She, in her hysteria, ran upstairs to her
bedroom, grabbed a suitcase, and pointlessly started throwing clothes
into it. I watched as the black figure paced closer to her. She went to
the dresser by the window; I saw her looking down at me. Her expression
was comically twisted and fear-stricken. The figure moved closer, its
hands only inches away. I turned away and pulled my jacket tighter
around me; the frigid chill was biting. A crash of glass caused me to
turn toward the sound. There in the fresh snow lay her tangled body, the
housekeeper next to her. A slight steam from the melting snow rose from
around their bodies. I felt strong, indescribably strong.

---We share everything. Do not forget.

One at a time, I dragged them to the lake and threw them in. As they
sank into the water, I saw an image of the basement. The pilot was out,
gas filled the room. The black figure now disguised as me had a box of
matches in its hand. He extracted one\ldots flint touched
striker\ldots a spark\ldots I was thrown; my body struck a pine tree.
The pain was excruciating. The flames hissed, then silence.

I felt warm and wet---as if sweating in the blazing sun, as if touched
by fire. I am lying down, the noise of the flames has ceased. All is
quiet.

I opened my eyes and caught a glimpse of a ceiling. A faint light
emanated from behind me. The bed was soft and warm. I tried to move; my
arm rested against something solid. I managed to get up and sit on the
edge. I put my face in my hands and tasted iron---the iron found in
blood.

She was sprawled out on the bed beside me. A dull brass candlestick
protruded from her back---she appeared as if she were some child's
wind-up toy. The scene appeared amusing, although I didn't have any
heart left.

Cold laughter echoed from an open window. I rushed toward it. The air
was warm. Through the glass, I saw in the distance the black lake with
its sad pines crouched around it. I saw the figure disguised as me
climbing out of the lake, drenched and blackened. Valerie was screaming.
She was dissolving; many hands were on her. She was pulled under---a
gurgling sound and air bubbles rising to the surface sickened me. I
smiled at myself, teeth gleaming.

\end{document}
