% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
  \setmainfont[]{Latin Modern Roman}
  \setsansfont[]{Latin Modern Sans}
  \setmonofont[]{Latin Modern Mono}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[a5paper,margin=18mm]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={The Itch},
  pdfauthor={Francis Dove},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{The Itch}
\author{Francis Dove}
\date{}

\begin{document}
\maketitle

Steven Lovan Cord, after greeting the last invited guests to his
retirement party and refusing to accept a continuing role as an adviser
to the Company, fell into a heap before Mrs.~Donalsed on the floor.
Boagaphish, Cord's grey and black tabby, whose attention had been on a
balloon string wafting up and down, watched with awe and curiosity at
Cord's convulsions. Near the scene, Mrs.~Donalsed's looks of trepidation
shot through the gathering crowd. Never had she felt more a mix of fear,
loathing, and horror than when she heard the details of the news when
her husband, who had been director at a University laboratory, died in a
mysterious accident there. Boagaphish, cutting a swath between many sets
of towering thin and thick legs covered in pressed black and blue
cloths, stood over Mr.~Cord's face.

Gazing intently at his wincing expressions, she sniffed his cheek
angularly. Such a curiosity it was seeing him like this lying on the
floor. Most of the time she found him engrossed in reading a newspaper
or reports for the Company while sitting by the fire in the den. Other
times she would find him in bed reading a book. She would hop on the bed
and lie next to him, snuggling just at his side, purring intently.
Between turning the pages in his book, he would lay his hand just next
to her and stroke her.

Jacobs, the servant, pushed his way through the crowd and knelt down
beside him.

``Mr.~Cord, can you hear me?'' Cord had stopped convulsing, and
Boagaphish could hear his breathing becoming more rhythmic. She mewed
softly.

Jacobs, who had arrived five years ago, was the head servant of a staff
of six. He was entrusted by Cord to his personal effects and had the
most Herculean task of watching over the CEO of the most valuable
technological company in the world. He delivered reports, answered the
telephone, and showed in streams of people in suits and briefcases and
organized Cord\textquotesingle s strewn documents while he was away.
Soon, however, he would be taking his new role as caretaker of the man
who ran the company that built the true A.I.

``Go on, cat, go away!'' Jacobs swatted at Boagaphish. She meowed
accusingly and sauntered to the door to the hallway stairs, pausing to
look back at Jacobs talking into a mobile phone. Others in the group
pulled out their phones, and the scene became a wailing chant.
Boagaphish decided she was hungry. She made her way along the wall, down
the stairs, and to the kitchen.

Jacobs used to be nice to Boagaphish, a day far in the past, it seemed
to her. It was winter, and snow covered the grounds of the estate; a
time when she did not go outside. She bored quickly of ducking into open
cabinets, racing up stairs, or peering into holes. She liked to sit in
the window and watch the few birds there were resting in the swaying
barren trees. When Jacobs was in the room with her, he would talk to
her, pick her up, and pet her. She once found his caresses meaningful.
He would feed her, making sure her water was fresh and cold and dumping
out her stale food. But since Cord had started to change, everything was
different. When Cord was restless and intensely emotional, Jacobs was
distressed. At times Cord would be calm and witty, but the next moment
he would yell throughout the house in incomprehensible rants.

This had gone on only for the past several years, ever since Cord
relented that he had become an old man. After his retirement and
relinquishment of his power, his mood shifted into shades of darkness.
Boagaphish seemed to understand, his mind was atrophying and he was
drifting away from life. He was forgetting his theories, his equations,
his adaptive programs, and his passion. His life's work realized in
himself, had given him long life far beyond what he had anticipated. He
was aged and tired. The notion of Boagaphish, who used to be of great
comfort, slowly became an irritation, a reminder of what he had done to
himself. It didn't matter, he was forgetting everything save her.

A few morsels lay in her dish and she quickly ate them. She licked her
face, washing an eye with her paw, then paced down the hallway to Cord's
room. As she approached, she could hear the flurry of activity in the
room. She peered around the door and slid into the room to a corner
where she could watch. Cord was lying on the bed, his hands placed over
his chest, his eyes were fixed to a point on the ceiling as if he were
watching a dance of invisible black shadowed creatures. His eyes moved
to and fro, his lips pursed in a muted smile. For now he seemed at peace
and the conversation in the room dwindled. The guests had been escorted
out, and the servants sent to clean up. Jacobs set a blanket over Cord
and left the room.

Boagaphish walked to the bed and jumped to it in a smooth, gliding
motion. She tucked herself under Cord's arm where she could watch his
expression. His face didn't flinch, and he didn't move. Only his eyes
closed, as did hers. In her dream she saw Cord as a young man. In the
beginning there were only the two of them. They were in the tiny flat in
the old city. Cord's room was filled with equipment, computers, various
sorts of hardware, and devices. In a closet hung wires, wires she loved
to play with while lying on her back. If there was one striking detail
about the past she knew much about, it was wires. She twisted herself up
in them, chewed on them, and chased them around the flat. Sometimes she
dreamed of wires.

Her dreams drifted to pleasant times and pleasant things, to long
pastures with tall grasses adorned with yellow flowers and butterflies
and insects which she could endlessly stalk, chase, and pounce upon. The
butterflies would always get away. Then, after such an exertion, she
could lie down in the grass with sweet smells in her nose. She would
sleep peacefully and dream. Her dreams were like a series of photographs
devoid of any emotion, as if she were at the window thinking of herself
outside. Had she been in the pasture or the garden? She didn't know. But
memories are an emotional volley never linear; she only knew what she
knew, her feelings the substance of her life. She knew nothing else. In
her dream a strange sensation came over her. It started as a tickle in
her side, like a small jolt of electricity, and soon moved down her leg.
It was as if an insect was crawling into her fur and biting the skin
underneath.

Cord stirred, Boagaphish awoke. He moaned softly, and she purred trying
to comfort him, snuggling in a little tighter. His arm moved from his
chest to her back where he stroked her gingerly. She could feel his
emotions, his shifting state from calm to fear. His caress became weak
and distracted. The end was coming.

``Mr.~Cord, can you hear me?''

Cord opened his eyes, they focused on Jacobs.

``Yes...''

``How are you feeling?''

Cord coughed and sighed. ``As if the end is finally coming.''

Cord hacked dryly. His side where Boagaphish lay was contracting
violently.

``The itch...it's getting worse.''

``Let me get your medication.''

``It's too late for that.''

``It can at least make you feel better.''

Cord clawed at his side and his leg.

``It's getting worse, sir. I'm getting the medication.''

Jacobs left the room and Cord turned his head to look at Boagaphish. The
strange sensation from the dream came over her. It began in her hind
side and moved down her leg. She gnashed at the spot. She frantically
tried to quell it. Cord placed his hand on her head and stroked her fur.
The itch slowly subsided.

``My lovely Boagaphish,'' Cord croaked.

She sat up and peered into his eyes. His skin was deathly pale, his eyes
the look of shattered crystal. Once his eyes gleamed brightly, now he
was only a remnant of what he once was. She could hear his breathing,
the heaving of his chest was slow and erratic. She could feel what was
going to happen, her sense told her Cord was going to die. She hung her
head and mewed softly. Cord managed his arm up and stroked her ears. She
purred.

``I'm sorry to have done this to you.''

He slid his hand down her back to her side where his fingers probed the
itch. She turned her head around and gnashed into the place. She gnashed
again, but it wouldn't stop. She raised her leg to scratch but the
sensation wouldn't go away. She was possessed trying to put a stop to
it. She had to sooth herself, to stop the itch. Nothing she did, no
matter how hard she tried, would put it to rest. She saw her leg as a
blinding swipe, moving so quickly it appeared as a blur. She was
pressing her claws deeper and deeper into herself to no avail. Soon, fur
was coming off in large clumps, stripped away to the tender skin but the
itch wouldn't subside. She bit into her leg tearing into the flesh,
pulling away layer after layer of skin until she discovered a curious
sight within. Metal, she saw metal, like the shiny material she had
remembered seeing in the old flat. It was now in her leg. Multi-colored
pieces of string were wrapped around it, they were hard and when she bit
into it, she got a shock. She did not understand but feared what she was
seeing. Although the pain and shock gradually decreased, she continued
to tear into herself.

He began slowly. ``I should have let you die,'' he said in a low tone.
``I have been at his game too long. And I see you have, too.'' He
stroked her as he had in the dark past, perhaps he could comfort her and
express his love for her before it was too late.

``An unfortunate side effect to living past your time. I feel the itch
too. It is a sign that death is coming. I am no longer afraid of death,
I have used my feigned intelligence to extend my life by replacing my
dying organs with artificial ones. Now no one can tell which part of me
is human and which is machine. The real Boagaphish died half a century
ago. I consumed myself in replicating her and a year later you were
born. The necessary evils of such work, perhaps I should not have become
a Cyberneticist. The programs, the devices, the wires that run through
you run through me.''

She stopped scratching and suddenly looked at Cord.

``If only you could understand me. But you can't, can you? I can't stand
it any longer, the itch has taken over my entire body. I am powerless to
stop it. If I could\ldots but Jacobs won't let me. It's not his fault,
he's just doing as he's told by the Company. Don't hate him for it.''

He continued to caress her. The itch that had risen to such intensity
abruptly subsided. They lay together as the room became dark. His
breathing became slow and less deliberate, his body twitched and his
face winced. Her gaze never left Cord's eyes and as the last glimmers of
brightness left him, she closed her eyes and dreamt of wires.

***********************************

\end{document}
