% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
  \setmainfont[]{Latin Modern Roman}
  \setsansfont[]{Latin Modern Sans}
  \setmonofont[]{Latin Modern Mono}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[a5paper,margin=18mm]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Prelude},
  pdfauthor={Francis Dove},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Prelude}
\author{Francis Dove}
\date{}

\begin{document}
\maketitle

\section{Prelude}\label{prelude}

What qualifies a vision? What makes it what it is? What could possibly
be its composition? Is a vision of something, what one gleans from it,
the same content as a dream? Such questions are difficult by design, yet
comparatively easy in a sphere of rational thought. As for me, I do not
have the answers. It could be because I do not spend my time dwelling on
such topics. I just accept the dreams for what they are, enjoy the
feelings, no matter how odd they may be. I cannot help, though,
wondering where these \emph{mind pictures} originate. Maybe it is just
transference of distinct images, collected in day living, from the
subconscious to the conscious and visa-versa. It is a fact that your
brain has already made a decision by the time you are conscious of it.
So do the visions, the dreams, the images come from within or without?

I do not know what to think or believe, but I do know that I am
continually haunted by demons of the night. When a topic such as this
affixed itself in my mind, I was not quite sure what I should write, but
I felt that I should try to communicate that part of me that is seldom
discussed. So here goes.

My visions on that night of October were, to say the least, nightmares.
So vivid and full of color were they that upon my waking, I felt that I
was still beyond the wall of sleep. I wish I could illustrate my images
fully, but I have trouble describing them, since they are clear in my
mind but not so when I put them on paper.

I will begin by prefacing that this vision was quite perplexing, which,
in turn, makes translation difficult. A good portion of it was spoken in
Latin. I took a course at University in it so I could read ancient
texts. So I will admit I would be \emph{conscious} of hearing it,
although not to its explicit meaning. I hope I can convey this vision in
a clear diction and format. I do not want any meaning, implied or
otherwise, to be lost. I feel I have covered everything needed to
understand what I am about to reveal.

It was almost nightfall and I appeared in front of a house of some
kind\ldots a large structure hewn out of grey stone that was
unrecognized by me. Four tiers towered above, reaching to the sky, yet
the others had fallen from the weathering of the passing of time. Dark,
cavernous windows glared down at me, withholding the blackness within.
Magnificent gargoyles hunched on the roofline did no more than to stare
at me with their gritty eyes. All was in an advanced state of disarray.
There were loose bits of carved stone lying sporadically on the paved
surface. Paving that once was neatly divided into octagonal shapes now
scarred with deep crevices lead to the depths of the earth. I knew the
place, as if I had lived there in a previous life, but, of course, this
is all in my mind.

I made my way across the littered courtyard and inspected the rest of
the grounds. It was forested with numerous large gnarled oak trees. The
trees were quite dead as their barks were peeling and their large,
droopy branches cried out for a saving grace that was not present in
this forsaken landscape. As I moved close to one, I witnessed something
I will not easily forget. For not only was the wood of this tree
twisted, but there also were human faces, faces embedded into the
composition of the tree. They expressed much pain and suffering as I
have not seen before. As I stared at the images, I could almost see
their anguished faces moving and changing shape. Then, all of them
looked at me in unison. Their jaws fell open and they uttered low,
excruciating moans. Moans of such a magnitude that the dusty sound
rattled the bones in my ears and pricked the hairs upon my neck. I
jumped back from the tree so as not to be drawn into it.

A sharp wind then whisked its way through my hair. A cold wind, carrying
with it the moans, as well as the smell of the life that had been
before. An odor so pungent that I tore myself away from the tree and
paced back to the front of the grey stone building. As I stood there
facing the enormous structure, what I thought was a voice called from
its interior. A hard, dry, crackled voice that I indeed recognized from
my own past. I dare not say what the voice was or what it resembled,
since writing about it makes me feel uncomfortable, and I could lose my
train of thought in doing so. The voice beckoned me to enter the house.
I kicked up the sand at my feet and ventured slowly to the mammoth
entrance.

As I moved closer, I peered through the open doors. Blackness belched
its musty breath at me and enveloped my senses. I was now inside the
house, black and foreboding, but not by my own locomotion. It was as
dark as the deepest abyss. I felt along the grainy walls and found a
candle sitting on its stand by a window. It lit itself, by a means I
know not of, and I followed the voice to a small chapel. I walked down
the aisle, past rows of overturned pews, to the altar. All I had was the
lone candle to cut my way through the almost complete darkness. I
managed to avoid stumbling over most of the larger debris, but I had
that nagging feeling that I knew where everything was. As if I had been
paraded down this eerie hall in some earlier time. I could extinguish
the candle and still find my way, that's how well I knew where I was.
But my sanity wouldn't allow me to. As my eyes focused on the marble
altar, thunder began raging outside and bolts of lightning illuminated
most of the pith in which I stood.

The sound of that familiar voice still echoed within the hall, and I
noticed that it was not emanating from the altar, but instead from its
side. It directed me to it. This is the point where I fail to describe
fully what I heard since the voice was speaking phrases in Latin, which
I understood at the time, but upon waking I found that the words had
dissipated. Although my walking was slow, I quickly arrived at the
source of the voice. It was then that I do remember exactly what was
said. The same phrase was repeated endlessly, over and over, insuring my
memorization. I was standing only a few meters from a large, polished,
black onyx sarcophagus. I stood next to it; hundreds of decayed flowers
and thirty or so exhausted candles littered its surface and the granite
floor it rested upon. I set my candle in one of the copper stands that
encircled the tomb and placed my hands on the smooth lid of the chamber.
The voice was issuing from its interior. That voice that had dug its way
through my entire mind and body was now calling to me; it repeated again
and again,

``Requiem aeternam dona eis, Domine.''

By now I was at a loss what to do next. Terror had long been ingrained
in me since my entrance into the black house. I peered at the
inscriptions carved into the surface of the lid. They shot through me
like the lightning that was riveting its way across the frozen sky
outside. I lifted the mighty lid and fearfully observed its contents.
The leathery face that gazed back at me with its glassy eyes and
yellowed teeth made me scream. I was still; I couldn't move. The face
just looked at me, and as it opened its mouth to smile, its decayed skin
cracked and split. I dropped the lid and ran screaming through the dark
house. I never heard my screams, they were silent.

I tripped several times over the stony debris. I overturned several
things and billowed up great amounts of dust, but I made my way out,
only to be greeted by a group of people I realized I had known, but they
are dead. Archaic laughter expulsed from the grey stone house as I stood
face to face with a barrage of animated bodies in various states of
decay. Their gleaming white bones shone through their dripping,
mud-stained flesh; they smiled wide, paralyzing smiles. I turned to run,
but was surrounded, for the giant wooden doors of the church had now
become the iron gates of the white marble mausoleum. Laughter continued
from its interior, and I turned and faced the horde. Their eyes gaped as
they lunged themselves at me and tore at my flesh.

I abruptly awoke in a cold sweat. I prayed that when I opened my eyes
that I would be in my own room. Luckily, I did arise in my own dwelling.
As I collected my senses, I reviewed what I had just experienced. I
grabbed the notebook that was close to my bed, and as I wrote out what I
felt, I realized what was in that shimmering onyx coffin, and terror
struck me once again. For what I saw in the depths of that dark vault,
what I heard as that voice rang through the long deserted halls of the
structure, and what I read on the top of that lid all had something in
common. What they revealed to me was something that I never wanted to
come to terms with, they did everything for one single purpose. They
foreshadowed my own passing to the realm occupied by death.

The scene changes, first at a slow pace, then rapidly becomes filled
with light. I've seen one kind of ending, one way to deal with my place
in the world. Now, another vision, another memory, one more fitting, and
one I would find myself more likely to believe in.

Back in the days when I was younger, my patents used to take my younger
sister, my brother, and me on long drives from where we lived to visit
family. Sometimes on these long trips, we would camp at grounds a few
kilometers from the highway. I remembered eating baloney sandwiches
noticing how the bread would become drier more rapidly than when at
home. The campgrounds were sylvan with areas of isolation where a
child's imagination could take hold and find itself filled with lucid
fantasies. After several summer trips, the multifaceted experiences
coalesced in a dream.

I was back at one of the campgrounds a substantial distance from the
highway. I was alone and the trees seemed to emanate an unspoken
monologue as they swayed in an invisible wind. Moving away from the
campground deeper into the forest, I heard a faint mewing in the
distance. It was broken and desperate, its cries echoing. I thought to
call to my parents to draw their attention to it, but remembered I was
alone. A wave of fear gripped me, but it dissipated as quickly as it
rose. Instead of being afraid, I possessed courage with a distinct
purpose. I navigated the unknown terrain drawn onward by the sound. As I
got closer, I recognized it could have been a small animal, perhaps a
cat, which sounded as if in trouble.

As I passed over a rise and into a small sunken area of the forest, the
mew rose to a fevered pitch. It was definitely a cat, I was sure of it.
I quickened my pace, the trees wavered above me, the grasses pushed me
forward, and soon I would be on top of the sound. On the approaching
horizon, a large, old tree, its trunk thick and gnarled, drew my
attention. As my eyes focused, the sound emanated near it. I started to
run. Branches became tendrils, pointing feverishly toward the sound; the
forest was alive with cries and bristling overhead. I arrived at the
gnarled tree, put my hands on it, and looked for the sound; it was close
and just on the other side of it. I spun around and found the source of
the sound. At its foot was a newborn kitten, small and frail. In the
moment that I gazed at the creature and the scene, its oddity swelled in
me like a rising tide.

The kitten was flailing to release itself from the shell of an egg, blue
and lustrous with black spots; it was a golden white, and its hind legs
crammed into the shell. I thought who would do such a thing to such a
tiny animal. Then I noticed there were two other unhatched eggs, the
three of them packed into makeshift nest cradled into the tall grass at
the base of the tree. Some creature had made the nest but seemed to have
abandoned it. I knelt down and picked up the kitten. Gingerly, I removed
the shell from its hind and cradled the small creature. The mewing
ceased, and it purred in my arms, nuzzling in the corner of my elbow. It
had definitely come from the egg, I was certain of this because mucus
clung thickly to its pallid fur. Nevertheless, how could a cat come from
an egg? Even at my age, I knew mammals birthed live young, not like
birds who propagate with hard-shelled eggs, so there was something
fundamentally wrong with what I was experiencing. As these thoughts
raced through my mind, the trees rustled overhead, their branches
drooping all around me, the wind picked up. The branches of the gnarled
tree surrounded me and the dream ended. I woke and sat up in my bed. I
was sweating profusely. My heart was beating nervously in my chest. With
the dream fresh in my brain, I hastily scribbled what details I could
remember. A cat hatched from an egg. What was this? As I was finishing
my written detail of the dream, a single word drifted though my
head\ldots{}

\emph{Boagaphish}.

Boagaphish? What is a Boagaphish? It sounded nonsensical and impugn but
I knew Boagaphish was the name of the small, strange creature that
hatched from the egg I had cradled in my arm. I could still feel the
sensation of wetness from saliva of the cat on the inside of my elbow,
which as I habitually brushed at, a jolt of electricity ran though my
body causing me to shudder. I had experienced something profound, I
thought, and although I did not understand and could not even conceive
of how to understand it, I knew it represented something terribly
important. Although I had misplaced the importance of the imagery for a
number of years, I could not ever expunge it from my emotions or from my
memory.

\end{document}
